### 2020-03-10 manuscript/paper.tex
Initial set of files for paper.

\documentclass[preprint,12pt]{elsarticle}

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[utf8]{inputenc}

% For the TODOs
\usepackage{xcolor}
\usepackage{xargs}
\usepackage[colorinlistoftodos,textsize=footnotesize]{todonotes}
\usepackage{lineno}

%% Our macros
\input{macros.tex}

\journal{}

\begin{document}

\begin{frontmatter}

  \title{Comparison of SPH schemes for solid mechanics}
  \author[IITB]{A Dinesh\corrcoef{cor1}}
  \ead{adepu.dinesh.a@gmail.com}
  \author[IITB]{Prabhu Ramachandran}
  \ead{prabhu@aero.iitb.ac.in}
\address[IITB]{Department of Aerospace Engineering, Indian Institute of
  Technology Bombay, Powai, Mumbai 400076}

\cortext[cor1]{Corresponding author}

\begin{abstract}
  XXX
  \end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
{XXX}, {XXX}, {XXX}

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

% \linenumbers

\section{Introduction}
\label{sec:intro}

\section{The SPH method}
\label{sec:sph}

\section{Results and discussion}
\label{sec:results}

\section{Conclusions}
\label{sec:conclusions}

\section*{References}
\bibliographystyle{model6-num-names}
\bibliography{references}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% fill-column: 78
%%% End:

### 2020-08-01 manuscript/paper.tex
2d rigid body algorithm implemented. Memory pointer issues. Not working

@@
 \usepackage[utf8]{inputenc}
+\usepackage{cleveref}
 
@@
 \usepackage[colorinlistoftodos,textsize=footnotesize]{todonotes}
+\newcommand{\todoin}{\todo[inline]}
+% from here: https://tex.stackexchange.com/questions/9796/how-to-add-todo-notes
+\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
+\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
+\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
+
+%Boldtype for greek symbols
+\newcommand{\teng}[1]{\ensuremath{\boldsymbol{#1}}}
+\newcommand{\ten}[1]{\ensuremath{\mathbf{#1}}}
+
 \usepackage{lineno}
-
-%% Our macros
-\input{macros.tex}
 
@@
 
-  \title{Comparison of SPH schemes for solid mechanics}
-  \author[IITB]{A Dinesh\corrcoef{cor1}}
+  \title{Fluid structure interaction and rigid fluid coupling in SPH}
+  \author[IITB]{A Dinesh\corref{cor1}}
   \ead{adepu.dinesh.a@gmail.com}
@@
 \begin{abstract}
-  XXX
 \end{abstract}
@@
 
+\section{2D Rigid body dynamics}
+\label{sec:rb-2d}
+
+\subsection{Center of mass, Linear momentum of a rigid body}
+\label{sec:center-mass}
+
+Let $N$ be an inertial frame in which a body $B$ is situated and is
+discretized into finite number of points. The center of mass is defined as \cite{rao2006dynamics}
+
+\begin{equation}
+  \label{eq:center-of-mass}
+  \ten{r}_{cm} = \frac{\sum_i m_i \; \ten{r}_i}{M}
+\end{equation}
+
+\noindent where $\ten{r}$ is the position vector of the point $i$ with mass
+$m_i$ in inertial frame $N$ and $M$ is the total mass of the rigid body under
+consideration.
+
+The linear momentum of the rigid body in the inertial frame is
+
+\begin{equation}
+  \label{eq:lin-mom-of-rigid-body}
+  \ten{G} = \sum_i m_i \; \ten{v}_i
+\end{equation}
+
+\begin{equation}
+  \label{eq:center-of-mass-velocity}
+  \ten{v}_{cm} = \frac{\sum_i m_i \; \ten{v}_i}{M}
+\end{equation}
+
+\noindent where $\ten{v}$ is the velocity vector of the point mass $i$ as
+observed in the inertial frame. Similarly the acceleration of the center of
+mass is
+
+\begin{equation}
+  \label{eq:acceleration-of-rigid-body}
+  \ten{a}_{cm} = \frac{\sum_i m_i \; \ten{a}_i}{M}
+\end{equation}
+
 \section{Results and discussion}

### 2020-08-01 code/rigid_body_2d.py

@@ -1,0 +1,326 @@
+import numpy as np
+
+from pysph.sph.scheme import add_bool_argument
+
+from pysph.sph.equation import Equation
+from pysph.sph.scheme import Scheme
+from pysph.sph.scheme import add_bool_argument
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.integrator import EPECIntegrator
+from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline)
+from textwrap import dedent
+from compyle.api import declare
+
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator_step import IntegratorStep
+
+# from pysph.sph.rigid_body import (BodyForce)
+
+from pysph.base.kernels import (CubicSpline, WendlandQuintic,
+                                QuinticSpline, WendlandQuinticC4,
+                                Gaussian, SuperGaussian)
+
+
+def set_total_mass(pa):
+    # left limit of body i
+    for i in range(max(pa.body_id) + 1):
+        fltr = np.where(pa.body_id == i)
+        pa.total_mass[i] = np.sum(pa.m[fltr])
+        assert pa.total_mass[i] > 0., "Total mass has to be greater than zero"
+
+
+def set_center_of_mass(pa):
+    # loop over all the bodies
+    for i in range(max(pa.body_id) + 1):
+        fltr = np.where(pa.body_id == i)
+        pa.xcm[3 * i] = np.sum(pa.m[fltr] * pa.x[fltr]) / pa.total_mass[i]
+        pa.xcm[3 * i + 1] = np.sum(pa.m[fltr] * pa.y[fltr]) / pa.total_mass[i]
+        pa.xcm[3 * i + 2] = np.sum(pa.m[fltr] * pa.z[fltr]) / pa.total_mass[i]
+
+
+def set_moment_of_inertia_izz(pa):
+    for i in range(max(pa.body_id) + 1):
+        fltr = np.where(pa.body_id == i)
+        izz = np.sum(pa.m[fltr] * ((pa.x[fltr] - pa.xcm[3 * i])**2. +
+                                   (pa.y[fltr] - pa.xcm[3 * i+1])**2.))
+        pa.izz[i] = izz
+
+
+class BodyForce(Equation):
+    def __init__(self, dest, sources, gx=0.0, gy=0.0, gz=0.0):
+        self.gx = gx
[…]

### 2020-08-16 code/dam_break_elastic_gate.py
Add fsi and rfc code. Add basic examples.

@@ -1,0 +1,286 @@
+import numpy as np
+
+from pysph.examples import dam_break_2d as DB
+from pysph.tools.geometry import get_2d_tank, get_2d_block
+from pysph.base.utils import get_particle_array
+
+from pysph.examples import cavity as LDC
+from pysph.sph.equation import Equation, Group
+# from fluids import ETVFScheme
+# from solid_mech import ComputeAuHatETVF
+
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.scheme import SchemeChooser
+from pysph.tools.geometry import rotate
+
+# from boundary_particles import (add_boundary_identification_properties,
+#                                 get_boundary_identification_etvf_equations)
+from fluid_structure_coupling import FSIScheme
+
+
+def get_fixed_beam(beam_length, beam_height, beam_inside_height,
+                   boundary_height, boundary_layers_left, boundary_layers_right,
+                   spacing):
+    # create a block first
+    xb, yb = get_2d_block(dx=spacing,
+                          length=beam_length,
+                          height=beam_height + beam_inside_height)
+
+    # create a (support) block with required number of layers on the left
+    xs1, ys1 = get_2d_block(dx=spacing,
+                            length=(boundary_layers_left - 1.) * spacing,
+                            height=boundary_height)
+    xs1 += np.min(xb) - np.max(xs1) - spacing
+    ys1 += np.max(yb) - np.min(ys1) + spacing
+
+    # create a (support) block with required number of layers
+    xs2, ys2 = get_2d_block(dx=spacing,
+                            length=(boundary_layers_right - 1) * spacing,
+                            height=boundary_height)
+    xs2 += np.max(xb) - np.min(xs2) + spacing
+    ys2 += np.max(yb) - np.min(ys2) + spacing
+
+    # create the support block on top of the beam
+    xs3, ys3 = get_2d_block(dx=spacing,
+                            length=beam_length,
+                            height=boundary_height - beam_inside_height)
+    ys3 += np.max(yb) - np.min(ys3) + spacing
+
+    # adjust the side supports
+    ys1 -= beam_inside_height
+    ys2 -= beam_inside_height
+
+    xs = np.concatenate([xs1, xs2, xs3])
[…]

### 2020-08-16 code/fluid_structure_coupling.py

@@ -1,0 +1,739 @@
+import numpy as np
+
+from pysph.sph.scheme import Scheme
+from pysph.sph.equation import Equation
+from pysph.sph.scheme import add_bool_argument
+from pysph.sph.integrator_step import IntegratorStep
+from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
+                                        get_shear_modulus)
+
+from pysph.base.kernels import QuinticSpline
+
+class AdamiBoundaryConditionExtrapolate(Equation):
+    """
+    Taken from
+
+    [1] A numerical study on ice failure process and ice-ship interactions by
+    Smoothed Particle Hydrodynamics
+    [2] Adami 2012 boundary conditions paper.
+    [3] LOQUAT: an open-source GPU-accelerated SPH solver for geotechnical modeling
+
+    """
+    def initialize(self, d_idx, d_p, d_wij, d_s00, d_s01, d_s02, d_s11, d_s12,
+                   d_s22):
+        d_s00[d_idx] = 0.0
+        d_s01[d_idx] = 0.0
+        d_s02[d_idx] = 0.0
+        d_s11[d_idx] = 0.0
+        d_s12[d_idx] = 0.0
+        d_s22[d_idx] = 0.0
+        d_p[d_idx] = 0.0
+        d_wij[d_idx] = 0.0
+
+    def loop(self, d_idx, d_wij, d_p, d_s00, d_s01, d_s02, d_s11, d_s12, d_s22,
+             s_idx, s_s00, s_s01, s_s02, s_s11, s_s12, s_s22, s_p, WIJ):
+        d_s00[d_idx] += s_s00[s_idx] * WIJ
+        d_s01[d_idx] += s_s01[s_idx] * WIJ
+        d_s02[d_idx] += s_s02[s_idx] * WIJ
+        d_s11[d_idx] += s_s11[s_idx] * WIJ
+        d_s12[d_idx] += s_s12[s_idx] * WIJ
+        d_s22[d_idx] += s_s22[s_idx] * WIJ
+
+        d_p[d_idx] += s_p[s_idx] * WIJ
+
+        # denominator of Eq. (27)
+        d_wij[d_idx] += WIJ
+
+    def post_loop(self, d_wij, d_idx, d_s00, d_s01, d_s02, d_s11, d_s12, d_s22,
+                  d_p):
[…]

### 2020-08-16 code/fsi_case_1.py

@@ -1,0 +1,295 @@
+"""Dam break solved with DTSPH.
+
+python dam_break_2d.py --openmp --integrator gtvf --no-internal-flow --pst sun2019 --no-set-solid-vel-project-uhat --no-set-uhat-solid-vel-to-u --no-vol-evol-solid --no-edac-solid --surf-p-zero -d dam_break_2d_etvf_integrator_gtvf_pst_sun2019_output --pfreq 1 --detailed-output
+
+
+"""
+import numpy as np
+
+from pysph.examples import dam_break_2d as DB
+from pysph.tools.geometry import get_2d_tank, get_2d_block
+from pysph.base.utils import get_particle_array
+
+from pysph.examples import cavity as LDC
+from pysph.sph.equation import Equation, Group
+# from fluids import ETVFScheme
+# from solid_mech import ComputeAuHatETVF
+
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.scheme import SchemeChooser
+from pysph.tools.geometry import rotate
+
+# from boundary_particles import (add_boundary_identification_properties,
+#                                 get_boundary_identification_etvf_equations)
+from fluid_structure_coupling import FSIScheme
+
+
+def get_fixed_beam(beam_length, beam_height, beam_inside_length,
+                   boundary_layers, spacing):
+    """
+ |||=============
+ |||=============
+ |||===================================================================|
+ |||===================================================================|Beam height
+ |||===================================================================|
+ |||=============
+ |||=============
+   <------------><---------------------------------------------------->
+      Beam inside                   Beam length
+      length
+    """
+    import matplotlib.pyplot as plt
+    # create a block first
+    xb, yb = get_2d_block(dx=spacing,
+                          length=beam_length + beam_inside_length,
+                          height=beam_height)
+
+    # create a (support) block with required number of layers
+    xs1, ys1 = get_2d_block(dx=spacing,
+                            length=beam_inside_length,
+                            height=boundary_layers * spacing)
+    xs1 += np.min(xb) - np.min(xs1)
+    ys1 += np.min(yb) - np.max(ys1) - spacing
+
+    # create a (support) block with required number of layers
+    xs2, ys2 = get_2d_block(dx=spacing,
+                            length=beam_inside_length,
[…]

### 2020-08-16 code/rb_case_1.py

@@ -28,7 +28,7 @@ class Case0(Application):
         self.dim = 2
 
         self.dt = 1e-3
-        self.tf = 1.18 * 1e-2
+        self.tf = 0.1
 
     def create_scheme(self):
         rb2d = RigidBody2DScheme(rigid_bodies=['body'], boundaries=None, dim=2)

### 2020-08-16 code/rfc_case_1.py

@@ -1,0 +1,81 @@
+"""A cube translating and rotating freely without the influence of gravity.
+This is used to test the rigid body dynamics equations.
+"""
+
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+from geometry import hydrostatic_tank_2d
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary, create_fluid, create_sphere)
+
+
+class RigidFluidCoupling(Application):
+    def initialize(self):
+        self.fluid_length = 1.0
+        self.fluid_height = 1.0
+        self.fluid_density = 1000.0
+        self.fluid_spacing = 0.1
+
+        self.tank_height = 1.5
+        self.tank_layers = 3
+        self.tank_spacing = 0.1
+
+        self.hdx = 1.3
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
+        self.gy = -9.81
+
+    def create_particles(self):
+        xf, yf, xt, yt = hydrostatic_tank_2d(self.fluid_length,
+                                             self.fluid_height,
+                                             self.tank_height, self.tank_layers,
+                                             self.fluid_spacing,
+                                             self.fluid_spacing)
+
+        m = self.fluid_density * self.fluid_spacing**2.
+
+        fluid = get_particle_array_wcsph(x=xf, y=yf, m=m, h=self.h,
+                                         rho=self.fluid_density)
+
+        tank = get_particle_array_wcsph(x=xt, y=yt, m=m, m_fluid=m, h=self.h,
+                                        rho=self.fluid_density)
+
+        self.scheme.setup_properties([fluid, tank])
+
+        return [fluid, tank]
+
+    def create_scheme(self):
[…]

### 2020-08-16 code/rigid_body_2d.py

@@ -30,7 +30,6 @@ from rigid_body_common import (
 from numpy import sin, cos
 
 
-
 class LeapFrogRigidBody2DStep(IntegratorStep):
     """
     This step has to be used when Leap frog integrator is used

### 2020-08-16 code/rigid_body_common.py

@@ -94,7 +94,9 @@ def set_body_frame_position_vectors(pa):
             pa.dz0[j] = pa.z[j] - cm_i[2]
 
 
-
+def set_body_frame_normal_vectors(pa):
+    """Save the normal vectors w.r.t body frame"""
+    pa.normal0[:] = pa.normal[:]
 
 
 class BodyForce(Equation):

### 2020-08-16 code/rigid_fluid_coupling.py

@@ -1,0 +1,625 @@
+import numpy as np
+
+from pysph.sph.scheme import add_bool_argument
+
+from pysph.sph.equation import Equation
+from pysph.sph.scheme import Scheme
+from pysph.sph.scheme import add_bool_argument
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.integrator import EPECIntegrator
+from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline)
+from textwrap import dedent
+from compyle.api import declare
+
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator_step import IntegratorStep
+
+# from pysph.sph.rigid_body import (BodyForce)
+
+from pysph.base.kernels import (CubicSpline, WendlandQuintic,
+                                QuinticSpline, WendlandQuinticC4,
+                                Gaussian, SuperGaussian)
+
+from rigid_body_common import (
+    set_total_mass, set_center_of_mass,
+    set_body_frame_position_vectors,
+    set_body_frame_normal_vectors,
+    set_moment_of_inertia_and_its_inverse,
+    BodyForce,
+    SumUpExternalForces,
+    normalize_R_orientation)
+
+# compute the boundary particles
+from boundary_particles import (get_boundary_identification_etvf_equations,
+                                add_boundary_identification_properties)
+from numpy import sin, cos
+
+
+class ContinuityEquation(Equation):
+    def initialize(self, d_idx, d_arho):
+        d_arho[d_idx] = 0.0
+
+    def loop(self, d_idx, s_idx, d_arho, s_m, s_vol, d_rho, VIJ, DWIJ):
+        vijdotdwij = VIJ[0] * DWIJ[0] + VIJ[1] * DWIJ[1] + VIJ[2] * DWIJ[2]
+        d_arho[d_idx] += d_rho[d_idx] * vijdotdwij * s_vol[d_idx]
+
+class SetVolumeFromDensityBoundary(Equation):
+    def post_loop(self, d_idx, d_rho, d_vol, d_m_fluid):
[…]

### 2020-08-16 code/rings.py

@@ -1,0 +1,216 @@
+"""Dam break solved with DTSPH.
+
+python dam_break_2d.py --openmp --integrator gtvf --no-internal-flow --pst sun2019 --no-set-solid-vel-project-uhat --no-set-uhat-solid-vel-to-u --no-vol-evol-solid --no-edac-solid --surf-p-zero -d dam_break_2d_etvf_integrator_gtvf_pst_sun2019_output --pfreq 1 --detailed-output
+
+
+"""
+import numpy as np
+
+from pysph.examples import dam_break_2d as DB
+from pysph.tools.geometry import get_2d_tank, get_2d_block
+from pysph.base.utils import get_particle_array
+
+from pysph.examples import cavity as LDC
+from pysph.sph.equation import Equation, Group
+# from fluids import ETVFScheme
+# from solid_mech import ComputeAuHatETVF
+
+from pysph.sph.solid_mech.basic import (get_particle_array_elastic_dynamics,
+                                        ElasticSolidsScheme)
+from pysph.base.kernels import CubicSpline
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.scheme import SchemeChooser
+from pysph.tools.geometry import rotate
+
+# from boundary_particles import (add_boundary_identification_properties,
+#                                 get_boundary_identification_etvf_equations)
+from fluid_structure_coupling import FSIScheme
+
+
+def get_fixed_beam(beam_length, beam_height, beam_inside_length,
+                   boundary_layers, spacing):
+    """
+ |||=============
+ |||=============
+ |||===================================================================|
+ |||===================================================================|Beam height
+ |||===================================================================|
+ |||=============
+ |||=============
+   <------------><---------------------------------------------------->
+      Beam inside                   Beam length
+      length
+    """
+    import matplotlib.pyplot as plt
+    # create a block first
+    xb, yb = get_2d_block(dx=spacing,
+                          length=beam_length + beam_inside_length,
+                          height=beam_height)
+
+    # create a (support) block with required number of layers
+    xs1, ys1 = get_2d_block(dx=spacing,
+                            length=beam_inside_length,
+                            height=boundary_layers * spacing)
[…]

### 2020-08-16 manuscript/paper.tex
Add fsi and rfc code. Add basic examples.
Add benchmark information to be done in future.

@@
 
+\section{Rigid body interaction}
+\label{sec:rigid-body-inter}
+
+As in
+
 \section{Results and discussion}
 \label{sec:results}
+
+\subsection{Cylinder column collapse under the action of gravity}
+\label{sec:cylinder-column-collapse}
+
+This benchmark is to test the contact law between the rigid bodies.
+
+\subsection{Regular waves interaction with a freely floating box}
+\label{sec:cylinder-column-collapse}
+
+This benchmark is used to test the interaction between fluid and rigid bodies
+aka rigid-fluid coupling. Please refer section 3.1 of \cite{dominguez2019sph}
+for further details.
+
+\subsection{Symmetric water entry of a light wedge (2D)}
+\label{sec:Symmetric-water-entry}
+
+This benchmark is also to test the interaction between fluid and rigid bodies
+aka rigid-fluid coupling. Please refer section 3.4 of
+\cite{amicarelli2015smoothed} for further details.
+
+\subsection{Asymmetric water entry of a light wedge (2D)}
+\label{sec:Asymmetric-water-entry}
+
+This benchmark is also to test the interaction between fluid and rigid bodies
+aka rigid-fluid coupling. Please refer section 3.4 of
+\cite{amicarelli2015smoothed} for further details.
+
+\subsection{Dam break with body transport (3D)}
+\label{sec:dam-break-body}
+
+This benchmark is to test both rigid fluid coupling as well as the rigid body
+interaction. See section 3.6 of \cite{amicarelli2015smoothed} for further
+details.
+
+\subsection{Demonstrative test case: multiple body transport (3D)}
+\label{sec:demonstrative-test-case}
+
+This benchmark is to test both rigid fluid coupling as well as the rigid body
+interaction. See section 3.7 of \cite{amicarelli2015smoothed} for further
+details.
+
+\subsection{Elastic bar hanging under gravity}
+\label{sec:elastic-bar-hanging}
+
+Currently this is a sub problem of elastic dam break. In that problem we are
+simulating gate with out considering the gravity. By considering the gravity
+we get float division error. It will be interesting to see why such thing is
+happening only in the case with gravity and solving such is fun.
+
+\subsection{Dam break with elastic gate}
+\label{sec:dam-break-elastic-gate}
+
+This is to test fluid structure interaction.
+
+\subsection{Water impact onto a forefront elastic plate}
+\label{sec:water-impact-forefront}
+
+In this example the elastic plate is placed at the end. Which gets
+impacted due to the moving fluid. Further information can be found at
+section 3.2 of \cite{liu2013numerical}
 

### 2020-08-16 code/fluid_structure_coupling.py
Fix fluids part in rigid fluid coupling.

@@ -1,739 +1,0 @@
-import numpy as np
-
-from pysph.sph.scheme import Scheme
-from pysph.sph.equation import Equation
-from pysph.sph.scheme import add_bool_argument
-from pysph.sph.integrator_step import IntegratorStep
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-
-from pysph.base.kernels import QuinticSpline
-
-class AdamiBoundaryConditionExtrapolate(Equation):
-    """
-    Taken from
-
-    [1] A numerical study on ice failure process and ice-ship interactions by
-    Smoothed Particle Hydrodynamics
-    [2] Adami 2012 boundary conditions paper.
-    [3] LOQUAT: an open-source GPU-accelerated SPH solver for geotechnical modeling
-
-    """
-    def initialize(self, d_idx, d_p, d_wij, d_s00, d_s01, d_s02, d_s11, d_s12,
-                   d_s22):
-        d_s00[d_idx] = 0.0
-        d_s01[d_idx] = 0.0
-        d_s02[d_idx] = 0.0
-        d_s11[d_idx] = 0.0
-        d_s12[d_idx] = 0.0
-        d_s22[d_idx] = 0.0
-        d_p[d_idx] = 0.0
-        d_wij[d_idx] = 0.0
-
-    def loop(self, d_idx, d_wij, d_p, d_s00, d_s01, d_s02, d_s11, d_s12, d_s22,
-             s_idx, s_s00, s_s01, s_s02, s_s11, s_s12, s_s22, s_p, WIJ):
-        d_s00[d_idx] += s_s00[s_idx] * WIJ
-        d_s01[d_idx] += s_s01[s_idx] * WIJ
-        d_s02[d_idx] += s_s02[s_idx] * WIJ
-        d_s11[d_idx] += s_s11[s_idx] * WIJ
-        d_s12[d_idx] += s_s12[s_idx] * WIJ
-        d_s22[d_idx] += s_s22[s_idx] * WIJ
-
-        d_p[d_idx] += s_p[s_idx] * WIJ
-
-        # denominator of Eq. (27)
-        d_wij[d_idx] += WIJ
-
-    def post_loop(self, d_wij, d_idx, d_s00, d_s01, d_s02, d_s11, d_s12, d_s22,
-                  d_p):
[…]

### 2020-08-16 code/fsi_case_1.py

@@ -24,7 +24,7 @@ from pysph.tools.geometry import rotate
 
 # from boundary_particles import (add_boundary_identification_properties,
 #                                 get_boundary_identification_etvf_equations)
-from fluid_structure_coupling import FSIScheme
+from fluid_structure_interaction import FSIScheme
 
 
 def get_fixed_beam(beam_length, beam_height, beam_inside_length,

### 2020-08-16 code/rfc_case_1.py

@@ -49,11 +49,11 @@ class RigidFluidCoupling(Application):
 
         m = self.fluid_density * self.fluid_spacing**2.
 
-        fluid = get_particle_array_wcsph(x=xf, y=yf, m=m, h=self.h,
-                                         rho=self.fluid_density)
+        fluid = get_particle_array(x=xf, y=yf, m=m, h=self.h,
+                                   rho=self.fluid_density, name="fluid")
 
-        tank = get_particle_array_wcsph(x=xt, y=yt, m=m, m_fluid=m, h=self.h,
-                                        rho=self.fluid_density)
+        tank = get_particle_array(x=xt, y=yt, m=m, m_fluid=m, h=self.h,
+                                  rho=self.fluid_density, name="tank")
 
         self.scheme.setup_properties([fluid, tank])
 

### 2020-08-16 code/rigid_fluid_coupling.py

@@ -17,18 +17,15 @@ from pysph.sph.integrator_step import IntegratorStep
 
 # from pysph.sph.rigid_body import (BodyForce)
 
-from pysph.base.kernels import (CubicSpline, WendlandQuintic,
-                                QuinticSpline, WendlandQuinticC4,
-                                Gaussian, SuperGaussian)
+from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline,
+                                WendlandQuinticC4, Gaussian, SuperGaussian)
 
-from rigid_body_common import (
-    set_total_mass, set_center_of_mass,
-    set_body_frame_position_vectors,
-    set_body_frame_normal_vectors,
-    set_moment_of_inertia_and_its_inverse,
-    BodyForce,
-    SumUpExternalForces,
-    normalize_R_orientation)
+from rigid_body_common import (set_total_mass, set_center_of_mass,
+                               set_body_frame_position_vectors,
+                               set_body_frame_normal_vectors,
+                               set_moment_of_inertia_and_its_inverse,
+                               BodyForce, SumUpExternalForces,
+                               normalize_R_orientation)
 
 # compute the boundary particles
 from boundary_particles import (get_boundary_identification_etvf_equations,
@@ -43,6 +40,7 @@ class ContinuityEquation(Equation):
     def loop(self, d_idx, s_idx, d_arho, s_m, s_vol, d_rho, VIJ, DWIJ):
         vijdotdwij = VIJ[0] * DWIJ[0] + VIJ[1] * DWIJ[1] + VIJ[2] * DWIJ[2]
         d_arho[d_idx] += d_rho[d_idx] * vijdotdwij * s_vol[d_idx]
+
 
 class SetVolumeFromDensityBoundary(Equation):
     def post_loop(self, d_idx, d_rho, d_vol, d_m_fluid):
@@ -61,12 +59,12 @@ class MomentumEquationPressureGradient(Equation):
         d_av[d_idx] = self.gy
         d_aw[d_idx] = self.gz
 
[…]

### 2020-08-16 code/rings.py

@@ -27,7 +27,7 @@ from pysph.tools.geometry import rotate
 
 # from boundary_particles import (add_boundary_identification_properties,
 #                                 get_boundary_identification_etvf_equations)
-from fluid_structure_coupling import FSIScheme
+from fluid_structure_interaction import FSIScheme
 
 
 def get_fixed_beam(beam_length, beam_height, beam_inside_length,

### 2021-03-27 manuscript/paper.tex
Fix fluids part in rigid fluid coupling.
Update the fluids and solids etvf code

--- 2020-03-10 manuscript/paper.tex
@@
 
-  \title{Comparison of SPH schemes for solid mechanics}
-  \author[IITB]{A Dinesh\corrcoef{cor1}}
+  \title{Fluid structure interaction with ETVF}
+  \author[IITB]{A Dinesh\corref{cor1}}
   \ead{adepu.dinesh.a@gmail.com}
@@
 
-\section{The SPH method}
-\label{sec:sph}
+\section{Fluid structure coupling}
+\label{sec:fsi-coupling}
+
+Coupling is handled straight forwardly in SPH. While modelling the fluid phase
+and treating the fluid-structure interactions, the structure particles are
+assumed to be boundary particles. And from the boundary handling given in
+Adami [14], we compute the pressure of the boundary particles from the
+extrapolated equation (12) and correspondingly set its density using equation
+(13). Please note that the pressure we set here are only pertaining to the fsi
+force and does not correspond to the real pressure or density of the structure
+particles.
+
+The force acting on the fluid particles is now computed from the pressure set
+using the adami boundary conditions and density set consequently. We mark
+particles comprising the solid as `a` and fluid as `i`, and the force acting
+on the fluid particle `i` is given as
+
+\begin{equation}
+  f_i^s = -m_i \Sum_{a} m_a \bigg(\frac{p_i}{\rho_{i}^2} +
+  \frac{p_a}{\rho_{a}^2} + \Pi_{ia} \bigg) \nabla_{i} W(x_{ia})
+\end{equation}
+
+Force on the structure particle due to the fluid particle computed using
+Newton's third law. Since each structure particle experiences equal and
+opposite force as experienced by the fluid particle, the expression for the
+force on structure due to a fluid particle is
+
+\begin{equation}
+  f_a^F = -m_i \Sum_{a} m_a \bigg(\frac{p_a}{\rho_{a}^2} +
+  \frac{p_i}{\rho_{i}^2} + \Pi_{ai} \bigg) \nabla_{a} W(x_{ai})
+\end{equation}
 
@@
 \label{sec:results}
+
+We can get many simple to advanced benchmarks in this area by looking at
+applied ocean engineering, coastal engineering, journal of fluids and
+structures, marine structures and ocean engineering papers.
+
+% =========================================
+% =========================================
+% start
+% =========================================
+
+\subsection{Hydrostatic water column on an elastic plate}
+\label{sec:results:hstank-elastic-plate}
+
+In this problem we check the accuracy and stability-preserving property of the
+proposed scheme in handling the fluid structure interaction. This problem has
+been studied in Li et al. (2015), Fourey et al. (2017), Khayyer et
+al. (2018a), Hu et al. (2019), (2021), (2021) papers. This benchmark has an
+analytical solution derived in Li et al. (2015).
+
+We can see the problem description in figure XXX. The water column height is
+2m and has a width of 0.5m. An aluminum plate of thickness 0.05m is placed at
+the bottom of the tank.The material properties of the aluminum are as follows,
+a density of 2700 kg/m^3, an Young’s modulus of $E = 6.75 \times 10^{10} Pa$,
+and the Poisson’s ratio $\nu = 0.34$. The plate is clamped on both the
+sides. Once the simulation begins, a sudden hydrostatic pressure force is
+applied on the aluminum plate. With time the plate oscillates and comes to
+rest. We compare the static displacement of the plate with the analytical
+solution.
+
+In the current simulation a total of two particle spacing is used. One with
+$\delta x = 0.04 , 0.02m and 0.01 m$ and use quintic spline as a kernel. We
+use 1e-6, 1e-7 for timestepping of fluid, solid phases respectively. All the
+simulations are run for a total time of $t_f = 1e-4s$. In figures XXX, XXX,
+XXX we show the final positions of the particles with different particle
+resolutions. The fluid contours are pressure and the structure contours is the
+y-displacement. In figure XXX we plot the midpoint deflection with time and
+compare it with the analytical solution provided by khayyer . It can be seen
+that the results produced by the current scheme are accurate and validates the
+scheme for further use in FSI problems. We have run a convergence analysis
+with a reducing spacing and as can be seen in the figure, that as the particle
+spacing is reduced the error is reduced.
+
+Also analyse any other extra plots you are planning to put.
+
+% =========================================
+% end
+% =========================================
+
+\subsection{Elastic bar hanging under gravity}
+\label{sec:elastic-bar-hanging}
+
+Currently this is a sub problem of elastic dam break. In that problem we are
+simulating gate with out considering the gravity. By considering the gravity
+we get float division error. It will be interesting to see why such thing is
+happening only in the case with gravity and solving such is fun.
+
+\subsection{Dam break with elastic gate}
+\label{sec:dam-break-elastic-gate}
+
+This is to test fluid structure interaction.
+
+\subsection{Water impact onto a forefront elastic plate}
+\label{sec:water-impact-forefront}
+
+In this example the elastic plate is placed at the end. Which gets
+impacted due to the moving fluid. Further information can be found at
+section 3.2 of \cite{liu2013numerical}
 

### 2021-03-27 code/fluids.py

@@ -303,47 +303,63 @@ class EDACSolidEquation(Equation):
         d_ap[d_idx] = 0.0
 
     def loop(self, d_idx, s_idx, d_p, d_rho, d_c0_ref, d_u, d_v, d_w, d_uhat,
-             d_vhat, d_what, s_p, s_m, s_rho, d_ap, DWIJ, XIJ, s_ughatfs,
-             s_vghatfs, s_wghatfs, s_ugfs, s_vgfs, s_wgfs, R2IJ, VIJ, EPS):
+             d_vhat, d_what, s_p, s_m, s_rho, d_ap, DWIJ, XIJ, s_ughatfs, s_vghatfs,
+             s_wghatfs, s_ugfs, s_vgfs, s_wgfs, R2IJ, EPS):
         vhatij = declare('matrix(3)')
+        vij = declare('matrix(3)')
         vhatij[0] = d_uhat[d_idx] - s_ughatfs[s_idx]
         vhatij[1] = d_vhat[d_idx] - s_vghatfs[s_idx]
         vhatij[2] = d_what[d_idx] - s_wghatfs[s_idx]
+
+        vij[0] = d_u[d_idx] - s_ugfs[s_idx]
+        vij[1] = d_v[d_idx] - s_vgfs[s_idx]
+        vij[2] = d_w[d_idx] - s_wgfs[s_idx]
 
         cs2 = d_c0_ref[0] * d_c0_ref[0]
 
         rhoj1 = 1.0 / s_rho[s_idx]
         Vj = s_m[s_idx] * rhoj1
         rhoi = d_rho[d_idx]
+        pi = d_p[d_idx]
+        # rhoj = s_rho[s_idx]
+        pj = s_p[s_idx]
 
-        vhatij_dot_dwij = (vhatij[0] * DWIJ[0] + vhatij[1] * DWIJ[1] +
-                           vhatij[2] * DWIJ[2])
+        vij_dot_dwij = -(vij[0] * DWIJ[0] + vij[1] * DWIJ[1] +
+                         vij[2] * DWIJ[2])
+
+        vhatij_dot_dwij = -(vhatij[0] * DWIJ[0] + vhatij[1] * DWIJ[1] +
+                            vhatij[2] * DWIJ[2])
 
         # vhatij_dot_dwij = (VIJ[0]*DWIJ[0] + VIJ[1]*DWIJ[1] +
         #                    VIJ[2]*DWIJ[2])
 
         #######################################################
-        # first term on the rhs of Eq 19 of the current paper #
[…]

### 2021-03-27 code/solid_mech.py

@@ -140,16 +140,14 @@ class VelocityGradient2DSolid(Equation):
         d_v10[d_idx] = 0.0
         d_v11[d_idx] = 0.0
 
-    def loop(self, d_idx, s_idx, s_m, s_rho,
-             d_v00, d_v01, d_v10, d_v11,
-             d_u, d_v, d_w, s_ug, s_vg, s_wg,
-             DWIJ):
+    def loop(self, d_idx, s_idx, s_m, s_rho, d_v00, d_v01, d_v10, d_v11, d_u,
+             d_v, d_w, s_ug, s_vg, s_wg, DWIJ):
         vij = declare('matrix(3)')
         vij[0] = d_u[d_idx] - s_ug[s_idx]
         vij[1] = d_v[d_idx] - s_vg[s_idx]
         vij[2] = d_w[d_idx] - s_wg[s_idx]
 
-        tmp = s_m[s_idx]/s_rho[s_idx]
+        tmp = s_m[s_idx] / s_rho[s_idx]
 
         d_v00[d_idx] += tmp * -vij[0] * DWIJ[0]
         d_v01[d_idx] += tmp * -vij[0] * DWIJ[1]
@@ -173,18 +171,15 @@ class VelocityGradient3DSolid(Equation):
         d_v21[d_idx] = 0.0
         d_v22[d_idx] = 0.0
 
-    def loop(self, d_idx, s_idx, s_m, s_rho,
-             d_v00, d_v01, d_v02,
-             d_v10, d_v11, d_v12,
-             d_v20, d_v21, d_v22,
-             d_u, d_v, d_w, s_ug, s_vg, s_wg,
+    def loop(self, d_idx, s_idx, s_m, s_rho, d_v00, d_v01, d_v02, d_v10, d_v11,
+             d_v12, d_v20, d_v21, d_v22, d_u, d_v, d_w, s_ug, s_vg, s_wg,
              DWIJ):
         vij = declare('matrix(3)')
         vij[0] = d_u[d_idx] - s_ug[s_idx]
         vij[1] = d_v[d_idx] - s_vg[s_idx]
         vij[2] = d_w[d_idx] - s_wg[s_idx]
 
-        tmp = s_m[s_idx]/s_rho[s_idx]
+        tmp = s_m[s_idx] / s_rho[s_idx]
 
         d_v00[d_idx] += tmp * -vij[0] * DWIJ[0]
[…]

### 2021-03-27 manuscript/paper.tex
Write elastic dam break theory.

@@
 
-This is to test fluid structure interaction.
+A block of fluid, which is suddenly released under gravity hits an elastic
+plate. This benchmark is simulated in many papers.
+
+The material properties of the elastic gate are as follows, and Young's
+modulus of $0.01 GPa$ with a Poisson ratio of $0.35$ and a density of
+$2500 kg/m^3$.
+
+The length of the fluid block is taken as $0.1m$, and the height is $0.3m$,
+and the length of the elastic gate is $0.03m$ with a height of $0.05m$ and is
+placed at a distance of $0.1m$ from the end of the fluid block.
+
+As the simulation starts the fluid starts flowing under the influence of
+gravity and after some time, it hits the elastic gate. Due to the influence of
+the fluid the elastic gate deforms and due to the elastic gate the fluid
+starts raising. The dynamics of both mediums is influenced by one another.
+
+We have compared the the tip of the elastic gate with time against the
+experimental results produced by \cite{xxx}. As can be seen the results
+produced by the current scheme are accurate and are able to reproduce the
+experimental results.
 

### 2021-04-11 manuscript/paper.tex
Manuscript: Add a bit introduction and write one result

@@
 
+Some FSI introduction. Its importance in different fields. Its applications so
+far.
+
+In modelling FSI problems, there are mainly two ways to handle the fluid and
+structures modelling. One way is to model the fluid part with mesh based
+scheme and solids part also with mesh based scheme. Like how (cite many papers
+which have done this). Or fluid part is modelled with a particle based scheme
+and the structures part with a mesh based scheme (Cite articles which have
+done this). One more way is to model both the phases using particle based
+schemes. In this paper we use particle based method to model both the phases.
+
+Recently there has been very good work on modelling fsi with particle based
+methods. Specific to particle based modelling, the fluid is modelled with SPH,
+and structure is modelled with different numerical method. Few articles which
+have done in this regard are as follows, citet{hosseini2009particle} has
+modelled the structure part using EBG method, then \citet{wu2016coupled}
+modelled it with DEM, \citet{ng2020coupled} modeled it using volume
+compensated particle method (VCPM), \citet{peng2021coupling} modeled it with
+RKPM, citet{zhang2021deltasph} modeled it with Smoothed Point Interpolation
+Method (SPIM).
+
+Recently there have been heavy improvements to basic SPH methodology in
+modelling fluid problems. Schemes such as $\delta$ SPH, $\delta +$ SPH, TVF
+for internal flows and GTVF for external flows is been proposed. Also, many
+new strategies were proposed to in overcoming the particle homogeneity
+problem, such as IPST, which is applied in \cite{IPST paper}. Also these
+improvements take care of tensile instability problem too. Another variant of
+SPH is ISPH, todoin{please cite some ISPH papers here}.
+
+Using only SPH, articles have been proposed where we model both the phases
+only using SPH. To note some, \citet{He2017coupled} has modelled the fluid
+part with WCSPH, \citet{Sun2019study} with delta sph,
+\citet{zhan2019stabilized} with WCSPH but applied to 3d problems with GPU. All
+these schemes use TLSPH as to model the structure part. And papers by Abbas use
+usual Gray equations to model the structures part.
+
+Recently {cite our paper ETVF} has been proposed as an another extension to
+TVF to model both fluid and structures part. In the current work we couple
+purely Eulerian SPH based schemes to model the FSI problems. We take advantage
+of the accuracy of the ETVF scheme proposed in modelling the fluids. ETVF
+scheme deals with tensile instability in both fluid and solid inherently.
+
 \section{Fluid structure coupling}
@@
 using the adami boundary conditions and density set consequently. We mark
-particles comprising the solid as `a` and fluid as `i`, and the force acting
-on the fluid particle `i` is given as
+particles comprising the solid as $a$ and fluid as $i$, and the force acting
+on the fluid particle $i$ is given as
 
 \begin{equation}
-  f_i^s = -m_i \Sum_{a} m_a \bigg(\frac{p_i}{\rho_{i}^2} +
+  f_i^s = -m_i \sum_{a} m_a \bigg(\frac{p_i}{\rho_{i}^2} +
   \frac{p_a}{\rho_{a}^2} + \Pi_{ia} \bigg) \nabla_{i} W(x_{ia})
@@
 \begin{equation}
-  f_a^F = -m_i \Sum_{a} m_a \bigg(\frac{p_a}{\rho_{a}^2} +
+  f_a^F = -m_i \sum_{a} m_a \bigg(\frac{p_a}{\rho_{a}^2} +
   \frac{p_i}{\rho_{i}^2} + \Pi_{ai} \bigg) \nabla_{a} W(x_{ai})
@@
 structures, marine structures and ocean engineering papers.
+
+The papers we have followed for the benchmarks are
+\citet{sun2021accurate}, \citet{yang2016numerical}, \citet{Sun2019study},
+\citet{He2017coupled}, \citet{khayyer2018enhanced}, \citet{sun2015numerical},
+\citet{wang2020scale}, \citet{peng2021coupling}, \citet{zhang2021deltasph},
+\citet{zhan2019stabilized}, \citet{khayyer2021multi},
+\citet{long2021coupling}, \citet{ng2020coupled},
 
@@
 the bottom of the tank.The material properties of the aluminum are as follows,
-a density of 2700 kg/m^3, an Young’s modulus of $E = 6.75 \times 10^{10} Pa$,
+a density of 2700 $kg/m^3$, an Young’s modulus of $E = 6.75 \times 10^{10} Pa$,
 and the Poisson’s ratio $\nu = 0.34$. The plate is clamped on both the
@@
 
+\subsection{High speed impact of an elastic aluminum wedge on undisturbed
+  water surface}
+\label{sec:wedge-impact-on-water}
+
+Here we simulate a high speed elastic aluminum wedge impacting on undisturbed
+water surface. This benchmark was dealt in
+{A $\delta$ SPH-SPIM coupled method for fluid-structure interaction problems} and
+{abbas khayyer} papers.
+This is an attractive benchmark as it has an semi-analytical solution.
+
+A fluid of length 6 m and a height of 2.2 m is settled inside a tank of length
+6m and height 4m which gives rise to a pressure distribution of a hydrostatic
+tank. Into this hydrostatic tank a wedge of length 0.6m and a thickness of
+0.04m is been dropped with a velocity of 30 m/s. The wedge angle is 10
+degrees. Please see figure \ref{fig:half-wedge-deformable} for visual clarity.
+
+The initial particle spacing is set as 0.005m and the total number of
+particles combining the wedge, tank and fluid is TOBEDONE. The density of the
+fluid is taken as 1000 $kg/m^3$. The material properties of the wedge are as
+follows: density of 2700 $Kg/m^3$, Young's modulus of 6.75 1e10 $N/m^2$ and a
+Poisson ratio of 0.34. An artificial viscosity $alpha$ of 0.1 is used for
+fluids and 1 for solid phase.
+
+In figure \ref{wedge-entering-the-tank}, at different time stamps, we plot the
+pressure fields of water and sigma 00 if the flexible wedge. (We need to give
+some physical insight of what is expected and what is been observed, provided
+our simulations are correct)
+
+A total of three points are marked on the wedge for a qualitative validation.
+In figure \ref{point-A-wedge-displacement}, we plot the displacement of point
+A with time, and compared with Abbhas and and the semi analytical solution of
+scolon 2004. Similarly at point B and point C we compare the pressure of the
+current scheme with the one provided with Abbas and the semi analytical
+solution. It can be seen that the current scheme is able to produce the
+results with a reasonable accuracy.
+
 \section{Conclusions}

### 2021-04-13 code/dam_break.py
Make fsi coupling scheme agnostic to structures. Add dam break examples

@@ -1,0 +1,320 @@
+"""
+A \delta SPH-SPIM coupled method for fluid-structure interaction problems
+
+https://doi.org/10.1016/j.jfluidstructs.2020.103210
+
+Section 3.4 Dam-break flow impacting on an elastic plate
+"""
+
+import numpy as np
+
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+# from rigid_fluid_coupling import RigidFluidCouplingScheme
+from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
+
+from pysph.examples.solid_mech.impact import add_properties
+# from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+#                                                                create_fluid,
+#                                                                create_sphere)
+from pysph.tools.geometry import get_2d_block, rotate
+
+from fsi_coupling import FSIScheme
+from boundary_particles import (add_boundary_identification_properties,
+                                get_boundary_identification_etvf_equations)
+
+from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
+                                        get_shear_modulus)
+
+
+def get_fixed_beam(beam_length, beam_height, beam_inside_length,
+                   boundary_layers, spacing):
+    """
+ |||=============
+ |||=============
+ |||===================================================================|
+ |||===================================================================|Beam height
+ |||===================================================================|
+ |||=============
+ |||=============
+   <------------><---------------------------------------------------->
+      Beam inside                   Beam length
+      length
+    """
+    # create a block first
+    xb, yb = get_2d_block(dx=spacing, length=beam_length, height=beam_height)
+
+    # create a (support) block with required number of layers
+    xs, ys = get_2d_block(dx=spacing, length=beam_length,
+                          height=boundary_layers * spacing)
+    ys -= np.max(yb) - np.min(ys) + spacing
+
+    # import matplotlib.pyplot as plt
+    # plt.scatter(xs, ys, s=1)
+    # plt.scatter(xb, yb, s=1)
+    # plt.axes().set_aspect('equal', 'datalim')
+    # plt.savefig("geometry", dpi=300)
+    # plt.show()
+
+    return xb, yb, xs, ys
+
+
+def get_fixed_beam_with_clamp(beam_length, beam_height, beam_inside_length,
[…]

### 2021-04-13 code/fsi_coupling.py

@@ -507,32 +507,33 @@ class FSIScheme(Scheme):
         all = self.structures + self.structure_solids
         g1 = []
 
-        for structure in self.structures:
-            g1.append(ContinuityEquationUhat(dest=structure, sources=all))
-            g1.append(
-                ContinuityEquationETVFCorrection(dest=structure, sources=all))
+        if len(self.structures) > 0.:
+            for structure in self.structures:
+                g1.append(ContinuityEquationUhat(dest=structure, sources=all))
+                g1.append(
+                    ContinuityEquationETVFCorrection(dest=structure, sources=all))
 
-            if self.dim == 2:
-                g1.append(VelocityGradient2D(dest=structure, sources=all))
-            elif self.dim == 3:
-                g1.append(VelocityGradient3D(dest=structure, sources=all))
+                if self.dim == 2:
+                    g1.append(VelocityGradient2D(dest=structure, sources=all))
+                elif self.dim == 3:
+                    g1.append(VelocityGradient3D(dest=structure, sources=all))
 
-        stage1.append(Group(equations=g1))
+            stage1.append(Group(equations=g1))
 
-        g2 = []
-        for structure in self.structures:
-            g2.append(HookesDeviatoricStressRate(dest=structure, sources=None))
+            g2 = []
+            for structure in self.structures:
+                g2.append(HookesDeviatoricStressRate(dest=structure, sources=None))
 
-        stage1.append(Group(equations=g2))
+            stage1.append(Group(equations=g2))
 
-        # # edac pressure evolution equation
-        # if self.edac is True:
-        #     gtmp = []
-        #     for solid in self.solids:
-        #         gtmp.append(
-        #             EDACEquation(dest=solid, sources=all, nu=self.edac_nu))
+            # # edac pressure evolution equation
+            # if self.edac is True:
+            #     gtmp = []
+            #     for solid in self.solids:
+            #         gtmp.append(
+            #             EDACEquation(dest=solid, sources=all, nu=self.edac_nu))
 
-        #     stage1.append(Group(gtmp))
+            #     stage1.append(Group(gtmp))
 
         # =========================#
         # structure equations ends
@@ -630,11 +631,11 @@ class FSIScheme(Scheme):
                     eqs.append(
                         MomentumEquationViscosityNoSlip(
                             dest=fluid, sources=self.solids, nu=self.nu_fluid))
-
-            eqs.append(
-                AccelerationOnFluidDueToStructure(
-                    dest=fluid,
-                    sources=self.structures + self.structure_solids), )
[…]

### 2021-05-04 manuscript/paper.tex
Make fsi coupling scheme agnostic to structures. Add dam break examples
GTVF fsi scheme added. No results though.

@@
 
-\section{Fluid structure coupling}
-\label{sec:fsi-coupling}
+\section{Governing equations}
+
+\subsection{Discrete governing equations}
+
+In this current paper the fluid medium is modelled using the improvised scheme
+of TVF, which is been applied to the free surface flows, called ETVF.
+
+For detailed derivation we point the reader to paper \cite{cite our paper},
+here we only give the discrete equations.
+
+The discretized equations of the fluid medium are
+
+\begin{equation}
+  \label{eq:sph-discretization-continuity}
+  \frac{\tilde{d}\rho_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; (
+  \rho_{a} \; \tilde{\ten{u}}_{ab} \; + \;
+  (\rho \; (\tilde{\ten{u}} \; - \;
+  \ten{u}))_{ab}) \; \cdot \nabla_{a} W_{ab},
+\end{equation}
+
+\begin{multline}
+  \label{eq:sph-discretization-edac}
+  \frac{\tilde{d}p_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; \bigg(
+  (p_{a} - \rho_{a} c_{s}^2) \; \ten{u}_{ab} \; - \;
+  p_{a} \; \tilde{\ten{u}}_{ab} \; - \;
+  (p \; (\tilde{\ten{u}} - \ten{u}))_{ab} \; + \; \\
+  4 \; \nu_{edac}
+  \frac{p_a - p_b}{(\rho_a + \rho_b) (r^2_{ab} + EPS)} \ten{r}_{ab}
+  \bigg) \; \cdot \nabla_{a} W_{ab}
+\end{multline}
+
+\begin{multline}
+  \label{eq:sph-momentum-fluid}
+  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
+  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}\bigg) \bigg]
+  \nabla_{a} W_{ab} \\
+  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot \nabla_{a} W_{ab} +
+  \ten{g}_{a}.
+\end{multline}
+
+\begin{equation}
+  \label{eq:sph-momentum-solid}
+  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
+  \bigg(\frac{\teng{\sigma}^{'}_{a}}{\rho_a^2} +
+  \frac{\teng{\sigma}^{'}_{b}}{\rho_b^2}\bigg) \bigg]  \nabla_{a} W_{ab} +
+  \ten{g}_{a}.
+\end{equation}
+
+The Jaumann's formulation for Hooke's stress provides us with the rate of
+change of deviatoric stress,
+\begin{equation}
+  \label{eq:jaumann-stress-rate}
+  \frac{d \sigma'_{ij}}{dt} = 2G (\dot{\epsilon}_{ij} - \frac{1}{3}
+  \dot{\epsilon}_{ij} \delta_{ij}) + \sigma^{'}_{ik}  \Omega_{jk} +
+  \Omega_{ik} \sigma^{'}_{kj}
+\end{equation}
+where $G$ is the shear modulus, $\dot{\epsilon}_{ij}$ is the strain rate tensor,
+\begin{equation}
+  \label{eq:strain-tensor}
+  \dot{\epsilon}_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} +
+  \frac{\partial u_j}{\partial x_i} \bigg)
+\end{equation}
+and $\Omega_{ij}$ is the rotational tensor,
+\begin{equation}
+  \label{eq:rotational-tensor}
+  \Omega_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} -
+  \frac{\partial u_j}{\partial x_i} \bigg)
+\end{equation}
+
+\begin{equation}
+  \label{eq:sph-vel-grad}
+  \nabla \ten{u}_a =
+  - \sum_{b} \frac{m_b}{\rho_{b}} (\ten{u}_{a} - \ten{u}_{b}) \otimes (\nabla_{a} W_{ab}),
+\end{equation}
+
+In both fluid and solid modelling, the pressure is computed using an
+isothermal equation of state, given as,
+\begin{equation}
+  \label{eq:pressure-equation}
+  p = K \bigg(\frac{\rho}{\rho_{0}} - 1 \bigg),
+\end{equation}
+where $K = \rho_{0} c_0^2$ is the bulk modulus. Here, the constants $c_0$ and
+$\rho_0$ are the reference speed of sound and density, respectively.
+
+\subsection{Boundary conditions}
+
+\subsection{Time integration}
+
+\subsection{Coupling between fluid and solid}
+\label{subsec:fsi-coupling}
 
@@
 
+\subsection{Hydrostatic water column on an elastic plate}
+\label{sec:hydrostatic-water-column-on-an-elastic-plate}
+
+In this problem we check the accuracy and stability-preserving property of the
+proposed scheme in handling the fluid structure interaction. This problem has
+been studied in Li et al. (2015), Fourey et al. (2017), Khayyer et
+al. (2018a), Hu et al. (2019), (2021), (2021) papers. This benchmark has an
+analytical solution derived in Li et al. (2015).
+
+We can see the problem description in figure XXX. The water column height is
+2m and has a width of 0.5m. An aluminum plate of thickness 0.05m is placed at
+the bottom of the tank.The material properties of the aluminum are as follows,
+a density of 2700 $kg/m^3$, an Young’s modulus of $E = 6.75 \times 10^{10} Pa$,
+and the Poisson’s ratio $\nu = 0.34$. The plate is clamped on both the
+sides. Once the simulation begins, a sudden hydrostatic pressure force is
+applied on the aluminum plate. With time the plate oscillates and comes to
+rest. We compare the static displacement of the plate with the analytical
+solution.
+
+In the current simulation a total of two particle spacing is used. One with
+$\delta x = 0.04 , 0.02m and 0.01 m$ and use quintic spline as a kernel. We
+use 1e-6, 1e-7 for timestepping of fluid, solid phases respectively. All the
+simulations are run for a total time of $t_f = 1e-4s$. In figures XXX, XXX,
+XXX we show the final positions of the particles with different particle
+resolutions. The fluid contours are pressure and the structure contours is the
+y-displacement. In figure XXX we plot the midpoint deflection with time and
+compare it with the analytical solution provided by khayyer. It can be seen
+that the results produced by the current scheme are accurate and validates the
+scheme for further use in FSI problems. We have run a convergence analysis
+with a reducing spacing and as can be seen in the figure, that as the particle
+spacing is reduced the error is reduced.
+
+Also analyse any other extra plots you are planning to put.
+
 \subsection{Water impact onto a forefront elastic plate}

### 2021-05-04 code/elastic_dam_break.py

@@ -19,7 +19,7 @@ from pysph.examples.solid_mech.impact import add_properties
 #                                                                create_sphere)
 from pysph.tools.geometry import get_2d_block, rotate
 
-from fsi_coupling import FSIScheme
+from fsi_coupling import FSIScheme, FSIGTVFScheme
 from boundary_particles import (add_boundary_identification_properties,
                                 get_boundary_identification_etvf_equations)
 
@@ -401,7 +401,21 @@ class ElasticGate(Application):
                          mach_no_structure=0.,
                          gy=0.)
 
-        s = SchemeChooser(default='etvf', etvf=etvf)
+        gtvf = FSIGTVFScheme(fluids=['fluid'],
+                             solids=['tank'],
+                             structures=['gate'],
+                             structure_solids=['gate_support'],
+                             dim=2,
+                             h_fluid=0.,
+                             rho0_fluid=0.,
+                             pb_fluid=0.,
+                             c0_fluid=0.,
+                             nu_fluid=0.,
+                             mach_no_fluid=0.,
+                             mach_no_structure=0.,
+                             gy=0.)
+
+        s = SchemeChooser(default='etvf', etvf=etvf, gtvf=gtvf)
         return s
 
     def configure_scheme(self):
@@ -432,10 +446,14 @@ class ElasticGate(Application):
     def create_equations(self):
         eqns = self.scheme.get_equations()
 
-        print(eqns)
-        equation = eqns.groups[-1][5].equations[4]
-        equation.sources = ["tank", "fluid", "gate", "gate_support"]
-        print(equation)
+        if self.options.scheme == 'etvf':
+            equation = eqns.groups[-1][5].equations[4]
+            equation.sources = ["tank", "fluid", "gate", "gate_support"]
+
+        elif self.options.scheme == 'gtvf':
+            equation = eqns.groups[-1][4].equations[3]
+            # print(equation)
+            equation.sources = ["tank", "fluid", "gate", "gate_support"]
 
         return eqns
 

### 2021-05-04 code/fsi_coupling.py

@@ -20,7 +20,8 @@ from solid_mech import (ComputeAuHatETVF, ComputeAuHatETVFSun2019,
                         CheckUniformityIPST, ComputeAuhatETVFIPST,
                         ResetParticlePositionsIPST, EDACEquation, setup_ipst,
                         SetHIJForInsideParticles, ContinuityEquationUhat,
-                        ContinuityEquationETVFCorrection)
+                        ContinuityEquationETVFCorrection, GTVFEOS, ComputeAuHatGTVF,
+                        VelocityGradient2DUhat)
 
 from pysph.sph.wc.edac import (SolidWallPressureBC)
 
@@ -914,6 +915,784 @@ class FSIScheme(Scheme):
 
             c0_ref = get_speed_of_sound(pa.E[0], pa.nu[0], pa.rho_ref[0])
             pa.add_constant('c0_ref', c0_ref)
+
+            # auhat properties are needed for gtvf, etvf but not for gray. But
+            # for the compatability with the integrator we will add
+            add_properties(pa, 'auhat', 'avhat', 'awhat', 'uhat', 'vhat',
+                           'what')
+
+            add_properties(pa, 'sigma00', 'sigma01', 'sigma02', 'sigma11',
+                           'sigma12', 'sigma22')
+
+            # output arrays
+            pa.add_output_arrays(['sigma00', 'sigma01', 'sigma11'])
+
+            # for boundary identification and for sun2019 pst
+            pa.add_property('normal', stride=3)
+            pa.add_property('normal_tmp', stride=3)
+            pa.add_property('normal_norm')
+
+            # check for boundary particle
+            pa.add_property('is_boundary', type='int')
+
+            # used to set the particles near the boundary
+            pa.add_property('h_b')
+
+            # for edac
+            if self.edac is True:
+                add_properties(pa, 'ap')
+
+            # update the h if using wendlandquinticc4
+            if self.kernel_choice == "4":
+                pa.h[:] = pa.h[:] / self.hdx * 2.
+
+            pa.add_output_arrays(['p'])
+
+        for boundary in self.structure_solids:
+            pa = pas[boundary]
+            pa.add_property('wij')
+
+            # for adami boundary condition
+
+            add_properties(pa, 'ug', 'vg', 'wg', 'uf', 'vf', 'wf', 's00',
+                           's01', 's02', 's11', 's12', 's22', 'cs', 'uhat',
[…]

### 2021-05-09 manuscript/paper.tex
Add new dynamic plate example by Turek. Improve boundary condition of pressure

@@
 
+\subsection{Dynamics response of an elastic plate}
+\label{sec:elastic-plate}
+
+In this example we validate the ETVF scheme in modeling an elastic structure.
+This example is taken from \cite{Sun2019study}, who took it from Turek and
+Hron, who simulated it using FEM.
+
+An elastic plate is attached to a rigid cylinder. The material properties of
+the elastic plate are as follows, the Young's modulus is $1.4\times10^6Pa$ and
+a Poisson ratio of $0.4$ and the density is $1000 kg/m^3$. This plate is held
+free in a gravity field whose value is $2m/s^2$.
+
+Here we simulate a high speed elastic aluminum wedge impacting on undisturbed
+water surface. This benchmark was dealt in
+{A $\delta$ SPH-SPIM coupled method for fluid-structure interaction problems} and
+{abbas khayyer} papers.
+This is an attractive benchmark as it has an semi-analytical solution.
+
+A fluid of length 6 m and a height of 2.2 m is settled inside a tank of length
+6m and height 4m which gives rise to a pressure distribution of a hydrostatic
+tank. Into this hydrostatic tank a wedge of length 0.6m and a thickness of
+0.04m is been dropped with a velocity of 30 m/s. The wedge angle is 10
+degrees. Please see figure \ref{fig:half-wedge-deformable} for visual clarity.
+
+The initial particle spacing is set as 0.005m and the total number of
+particles combining the wedge, tank and fluid is TOBEDONE. The density of the
+fluid is taken as 1000 $kg/m^3$. The material properties of the wedge are as
+follows: density of 2700 $Kg/m^3$, Young's modulus of 6.75 1e10 $N/m^2$ and a
+Poisson ratio of 0.34. An artificial viscosity $alpha$ of 0.1 is used for
+fluids and 1 for solid phase.
+
+In figure \ref{wedge-entering-the-tank}, at different time stamps, we plot the
+pressure fields of water and sigma 00 if the flexible wedge. (We need to give
+some physical insight of what is expected and what is been observed, provided
+our simulations are correct)
+
+A total of three points are marked on the wedge for a qualitative validation.
+In figure \ref{point-A-wedge-displacement}, we plot the displacement of point
+A with time, and compared with Abbhas and and the semi analytical solution of
+scolon 2004. Similarly at point B and point C we compare the pressure of the
+current scheme with the one provided with Abbas and the semi analytical
+solution. It can be seen that the current scheme is able to produce the
+results with a reasonable accuracy.
+
 \section{Conclusions}

### 2021-05-09 automate.py

@@ -1,19 +1,328 @@
 #!/usr/bin/env python
 import os
+import matplotlib.pyplot as plt
 
+from itertools import product
+import json
 from automan.api import PySPHProblem as Problem
-from automan.api import Automator, Simulation, filter_cases
+from automan.api import Automator, Simulation, filter_by_name
+
 import numpy as np
 import matplotlib
+from pysph.solver.utils import load, get_files
+
 matplotlib.use('pdf')
 
-# XXX
+matplotlib.use('pdf')
+n_core = 2
+n_thread = 2
+backend = ' --openmp '
+
+
+def pretty(d, indent=0):
+    for key, value in d.items():
+        print('\t' * indent + str(key))
+        if isinstance(value, dict):
+            pretty(value, indent + 1)
+        else:
+            print('\t' * (indent + 1) + str(value))
+
+
+def scheme_opts(params):
+    if isinstance(params, tuple):
+        return params[0]
+    return params
+
+
+def get_files_at_given_times(files, times):
+    from pysph.solver.utils import load
+    result = []
+    count = 0
+    for f in files:
+        data = load(f)
+        t = data['solver_data']['t']
+        if count >= len(times):
+            break
+        if abs(t - times[count]) < t * 1e-8:
+            result.append(f)
+            count += 1
+        elif t > times[count]:
+            result.append(f)
+            count += 1
+    return result
+
+
+def get_files_at_given_times_from_log(files, times, logfile):
+    import re
+    result = []
+    time_pattern = r"output at time\ (\d+(?:\.\d+)?)"
+    file_count, time_count = 0, 0
+    with open(logfile, 'r') as f:
+        for line in f:
+            if time_count >= len(times):
+                break
+            t = re.findall(time_pattern, line)
+            if t:
+                if float(t[0]) in times:
+                    result.append(files[file_count])
+                    time_count += 1
+                elif float(t[0]) > times[time_count]:
+                    result.append(files[file_count])
+                    time_count += 1
+                file_count += 1
+    return result
+
+
+class OscillatingPlateTurek(Problem):
+    def get_name(self):
+        return 'oscillating_plate_turek'
+
+    def setup(self):
+        get_path = self.input_path
+
+        cmd = 'python code/oscillating_plate_turek.py' + backend
+
+        # length = [1., 2., 3., 4.]
+        # height = [0.1]
+        # pfreq = 500
+
+        # Base case info
[…]

### 2021-05-09 code/fsi_coupling.py

@@ -71,7 +71,8 @@ class SolidWallPressureBCFSI(Equation):
             (self.gy - d_av[d_idx])*XIJ[1] + \
             (self.gz - d_aw[d_idx])*XIJ[2]
 
-        d_p_fsi[d_idx] += s_p[s_idx] * WIJ + s_rho[s_idx] * gdotxij * WIJ
+        max_val = max(0., gdotxij)
+        d_p_fsi[d_idx] += s_p[s_idx] * WIJ + s_rho[s_idx] * max_val * WIJ
 
     def post_loop(self, d_idx, d_wij, d_p_fsi):
         # extrapolated pressure at the ghost particle
@@ -1595,6 +1596,8 @@ class FSIGTVFScheme(Scheme):
             pa.add_output_arrays(['normal'])
             pa.add_property('normal_tmp', stride=3)
 
+            pa.add_output_arrays(['p_fsi'])
+
             name = pa.name
 
             props = ['m', 'rho', 'h']
@@ -1634,8 +1637,9 @@ class FSIGTVFScheme(Scheme):
 
             # for normals
             pa.add_property('normal', stride=3)
-            pa.add_output_arrays(['normal'])
+            # pa.add_output_arrays(['normal'])
             pa.add_property('normal_tmp', stride=3)
+            pa.add_output_arrays(['p_fsi'])
 
             name = pa.name
 

### 2021-05-09 code/oscillating_plate_turek.py

@@ -1,0 +1,404 @@
+import numpy as np
+from math import cos, sin, sinh, cosh
+
+# SPH equations
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.scheme import SchemeChooser
+
+from pysph.base.utils import get_particle_array
+
+from solid_mech import SetHIJForInsideParticles, SolidsScheme
+
+from boundary_particles import (add_boundary_identification_properties,
+                                get_boundary_identification_etvf_equations)
+
+from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
+                                        get_shear_modulus)
+from pysph.tools.geometry import get_2d_tank, get_2d_block
+from solid_mech_common import AddGravityToStructure
+from pysph.sph.scheme import add_bool_argument
+
+
+def get_fixed_beam(beam_length, beam_height, beam_inside_length,
+                   boundary_layers, spacing):
+    """
+ |||=============
+ |||=============
+ |||===================================================================|
+ |||===================================================================|Beam height
+ |||===================================================================|
+ |||=============
+ |||=============
+   <------------><---------------------------------------------------->
+      Beam inside                   Beam length
+      length
+    """
+    import matplotlib.pyplot as plt
+    # create a block first
+    xb, yb = get_2d_block(dx=spacing,
+                          length=beam_length + beam_inside_length,
+                          height=beam_height)
+
+    # create a (support) block with required number of layers
+    xs1, ys1 = get_2d_block(dx=spacing,
+                            length=beam_inside_length,
+                            height=boundary_layers * spacing)
+    xs1 += np.min(xb) - np.min(xs1)
+    ys1 += np.min(yb) - np.max(ys1) - spacing
+
+    # create a (support) block with required number of layers
+    xs2, ys2 = get_2d_block(dx=spacing,
+                            length=beam_inside_length,
+                            height=boundary_layers * spacing)
+    xs2 += np.min(xb) - np.min(xs2)
+    ys2 += np.max(ys2) - np.min(yb) + spacing
+
+    xs = np.concatenate([xs1, xs2])
+    ys = np.concatenate([ys1, ys2])
+
+    xs3, ys3 = get_2d_block(dx=spacing,
+                            length=boundary_layers * spacing,
+                            height=np.max(ys) - np.min(ys))
[…]

### 2021-05-09 code/solid_mech.py

@@ -1890,7 +1890,9 @@ class SolidsScheme(Scheme):
             else:
                 g3.append(
                     AdamiBoundaryConditionExtrapolateNoSlip(
-                        dest=boundary, sources=self.solids))
+                        dest=boundary, sources=self.solids,
+                        gx=self.gx, gy=self.gy, gz=self.gz
+                    ))
         if len(g3) > 0:
             stage2.append(Group(g3))
 

### 2021-07-05 manuscript/paper.tex
Fix substepping and update examples.

@@
 usual Gray equations to model the structures part.
+
+\citet{sun2019fully} couples MPS and BPM model to simulate FSI. He models both
+elastic dam break and flow over an elastic obstacle.
 
@@
 
+Taken from \citet{sun2019fully}.
+
 A block of fluid, which is suddenly released under gravity hits an elastic
@@
 impacted due to the moving fluid. Further information can be found at
-section 3.2 of \cite{liu2013numerical}
+section 3.2 of \cite{liu2013numerical}, \citet{sun2019fully}.
 

### 2021-07-05 code/elastic_dam_break.py

@@ -20,6 +20,7 @@ from pysph.examples.solid_mech.impact import add_properties
 from pysph.tools.geometry import get_2d_block, rotate
 
 from fsi_coupling import FSIScheme, FSIGTVFScheme
+from fsi_substepping import FSISubSteppingScheme
 from fsi_coupling_wcsph import FSIWCSPHScheme
 
 from boundary_particles import (add_boundary_identification_properties,
@@ -246,6 +247,10 @@ class ElasticGate(Application):
 
         self.artificial_stress_eps = 0.3
 
+        self.dt_fluid = 0.25 * self.fluid_spacing * self.hdx / (self.c0_fluid * 1.1)
+        self.dt_solid = 0.25 * self.h_fluid / (
+            (self.gate_E / self.gate_rho0)**0.5 + self.u_max_gate)
+
     def create_particles(self):
         # ===================================
         # Create fluid
@@ -297,7 +302,7 @@ class ElasticGate(Application):
             xp, yp, xw, yw = get_fixed_beam(self.H, self.L, self.H/2.5,
                                             self.wall_layers, self.fluid_spacing)
 
-        # # make sure that the beam intersection with wall starts at the 0.
+        # make sure that the beam intersection with wall starts at the 0.
         # min_xp = np.min(xp)
 
         # # add this to the beam and wall
@@ -439,7 +444,24 @@ class ElasticGate(Application):
                                mach_no_structure=0.,
                                gy=0.)
 
-        s = SchemeChooser(default='etvf', etvf=etvf, gtvf=gtvf, wcsph=wcsph)
+        substep = FSISubSteppingScheme(fluids=['fluid'],
+                                       solids=['tank'],
+                                       structures=['gate'],
+                                       structure_solids=['gate_support'],
+                                       dt_fluid=1.,
+                                       dt_solid=1.,
+                                       dim=2,
+                                       h_fluid=0.,
+                                       rho0_fluid=0.,
+                                       pb_fluid=0.,
+                                       c0_fluid=0.,
+                                       nu_fluid=0.,
+                                       mach_no_fluid=0.,
+                                       mach_no_structure=0.,
+                                       gy=0.)
+
+        s = SchemeChooser(default='etvf', etvf=etvf, gtvf=gtvf, wcsph=wcsph,
[…]

### 2021-07-05 code/fsi_coupling.py

@@ -1171,8 +1171,6 @@ class FSIScheme(Scheme):
                                              kernel_factor=self.kernel_factor))
             stage2.append(Group(eqs))
 
-        print("alpha is")
-        print(self.alpha)
         eqs = []
         for fluid in self.fluids:
             # FIXME: Change alpha to variable

### 2021-07-05 code/fsi_coupling_wcsph.py

@@ -72,7 +72,8 @@ class SolidWallPressureBCFSI(Equation):
             (self.gy - d_av[d_idx])*XIJ[1] + \
             (self.gz - d_aw[d_idx])*XIJ[2]
 
-        max_val = max(0., gdotxij)
+        # max_val = max(0., gdotxij)
+        max_val = gdotxij
         d_p_fsi[d_idx] += s_p[s_idx] * WIJ + s_rho[s_idx] * max_val * WIJ
 
     def post_loop(self, d_idx, d_wij, d_p_fsi, d_rho_fsi):
@@ -107,6 +108,76 @@ class AccelerationOnStructureDueToFluid(Equation):
         pij = d_p_fsi[d_idx] / rhoi2 + s_p[s_idx] / rhoj2
 
         tmp = -s_m[s_idx] * pij * d_m_fsi[d_idx] / d_m[d_idx]
+
+        d_au[d_idx] += tmp * DWIJ[0]
+        d_av[d_idx] += tmp * DWIJ[1]
+        d_aw[d_idx] += tmp * DWIJ[2]
+
+
+class AccelerationOnStructureDueToStructure(Equation):
+    def loop(self, d_m, d_m_fsi, d_rho_fsi, s_rho_fsi, d_idx, s_idx, d_p_fsi,
+             s_p_fsi, s_m_fsi, d_au, d_av, d_aw, DWIJ):
+        rhoi2 = d_rho_fsi[d_idx] * d_rho_fsi[d_idx]
+        rhoj2 = s_rho_fsi[s_idx] * s_rho_fsi[s_idx]
+
+        pij = d_p_fsi[d_idx] / rhoi2 + s_p_fsi[s_idx] / rhoj2
+
+        tmp = -s_m_fsi[s_idx] * pij * d_m_fsi[d_idx] / d_m[d_idx]
+
+        d_au[d_idx] += tmp * DWIJ[0]
+        d_av[d_idx] += tmp * DWIJ[1]
+        d_aw[d_idx] += tmp * DWIJ[2]
+
+
+class AccelerationOnFluidDueToStructurePita(Equation):
+    """
+    https://www.sciencedirect.com/science/article/pii/S0045782516303644
+    """
+    def loop(self, d_m, d_rho, s_rho_fsi, d_idx, s_idx, d_p, s_p_fsi, s_m_fsi,
+             d_au, d_av, d_aw, DWIJ):
[…]

### 2021-07-05 code/hydrostatic_water_column_on_elastic_plate.py

@@ -21,6 +21,7 @@ from pysph.tools.geometry import get_2d_block, rotate
 
 from fsi_coupling import FSIScheme
 from fsi_coupling_wcsph import FSIWCSPHScheme
+from fsi_substepping import FSISubSteppingScheme
 from boundary_particles import (add_boundary_identification_properties,
                                 get_boundary_identification_etvf_equations)
 
@@ -33,8 +34,8 @@ def get_hydrostatic_tank_with_fluid(fluid_length=1., fluid_height=2., tank_heigh
     import matplotlib.pyplot as plt
 
     xf, yf = get_2d_block(dx=fluid_spacing,
-                          length=fluid_length+fluid_spacing/2.,
-                          height=fluid_height+fluid_spacing/2.)
+                          length=fluid_length,
+                          height=fluid_height)
 
     xt_1, yt_1 = get_2d_block(dx=fluid_spacing,
                               length=tank_layers*fluid_spacing,
@@ -64,7 +65,7 @@ def get_elastic_plate_with_support(beam_length, beam_height, boundary_layers,
                                    spacing):
     import matplotlib.pyplot as plt
     # create a block first
-    xb, yb = get_2d_block(dx=spacing, length=beam_length + spacing/2.,
+    xb, yb = get_2d_block(dx=spacing, length=beam_length,
                           height=beam_height)
 
     # create a (support) block with required number of layers
@@ -144,7 +145,7 @@ class ElasticGate(Application):
         # ================================================
         # properties related to the only fluids
         # ================================================
-        spacing = 0.05 / 2.
+        spacing = 0.05 / 5.
         self.hdx = 1.0
 
         self.fluid_length = 1.0
@@ -162,6 +163,7 @@ class ElasticGate(Application):
         # self.solid_rho = 500
         # self.m = 1000 * self.dx * self.dx
         self.vref_fluid = np.sqrt(2 * 9.81 * self.fluid_height)
+        print("vref is ", self.vref_fluid)
         self.u_max_fluid = self.vref_fluid
         self.c0_fluid = 10 * self.vref_fluid
         self.mach_no_fluid = self.vref_fluid / self.c0_fluid
@@ -221,6 +223,11 @@ class ElasticGate(Application):
 
         self.artificial_stress_eps = 0.3
 
+        self.dt_fluid = 0.25 * self.fluid_spacing * self.hdx / (self.c0_fluid * 1.1)
+        print("dt fluid is", self.dt_fluid)
+        self.dt_solid = 0.25 * self.h_fluid / (
[…]

### 2021-07-16 manuscript/paper.tex
Add new structures example UDF and FSI Bendict Rogers scheme

@@
 
+One more way of coupling is by using \citet{khayyer2018enhanced} formulation.
+
+\subsection{Total energy of the structure}
+\label{sec:total-energy-struct}
+
+\citet{khayyer2018enhanced} had an extra section where he discusses about the
+energy conservation properties of the proposed FSI scheme. He discusses
+different energies in structure, kinetic energy and strain energy.
+
 \section{Results and discussion}
@@
 
+\subsection{Static test to test Structure formulation}
+\label{sec:static-test}
+
+In \citet{hwang2015development} has a static test where a cantilever beam is
+acted upon by a constant load at the tip.
+
 \section{Conclusions}

### 2021-07-16 code/beam_under_udf.py

@@ -1,0 +1,571 @@
+import numpy as np
+from math import cos, sin, sinh, cosh
+
+# SPH equations
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.scheme import SchemeChooser
+from pysph.sph.equation import Equation
+
+from pysph.base.utils import get_particle_array
+
+from solid_mech import SetHIJForInsideParticles, SolidsScheme
+
+from boundary_particles import (add_boundary_identification_properties,
+                                get_boundary_identification_etvf_equations)
+
+from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
+                                        get_shear_modulus)
+from pysph.tools.geometry import get_2d_tank, get_2d_block
+from solid_mech_common import AddGravityToStructure
+from pysph.sph.scheme import add_bool_argument
+
+
+def get_fixed_beam(beam_length, beam_height, beam_inside_length,
+                   boundary_layers, spacing):
+    """
+ |||=============
+ |||=============
+ |||===================================================================|
+ |||===================================================================|Beam height
+ |||===================================================================|
+ |||=============
+ |||=============
+   <------------><---------------------------------------------------->
+      Beam inside                   Beam length
+      length
+    """
+    import matplotlib.pyplot as plt
+    # create a block first
+    xb, yb = get_2d_block(dx=spacing,
+                          length=beam_length + beam_inside_length,
+                          height=beam_height)
+
+    # create a (support) block with required number of layers
+    xs1, ys1 = get_2d_block(dx=spacing,
+                            length=beam_inside_length,
+                            height=boundary_layers * spacing)
+    xs1 += np.min(xb) - np.min(xs1)
+    ys1 += np.min(yb) - np.max(ys1) - spacing
+
+    # create a (support) block with required number of layers
+    xs2, ys2 = get_2d_block(dx=spacing,
+                            length=beam_inside_length,
+                            height=boundary_layers * spacing)
+    xs2 += np.min(xb) - np.min(xs2)
+    ys2 += np.max(ys2) - np.min(yb) + spacing
+
+    xs = np.concatenate([xs1, xs2])
[…]

### 2021-07-16 code/elastic_dam_break.py

@@ -22,6 +22,7 @@ from pysph.tools.geometry import get_2d_block, rotate
 from fsi_coupling import FSIScheme, FSIGTVFScheme
 from fsi_substepping import FSISubSteppingScheme, FSISubSteppingWCSPHScheme
 from fsi_coupling_wcsph import FSIWCSPHScheme
+from fsi_coupling_rogers import FSIWCSPHSchemeRogers
 
 from boundary_particles import (add_boundary_identification_properties,
                                 get_boundary_identification_etvf_equations)
@@ -326,7 +327,8 @@ class ElasticGate(Application):
                 'n': 4.,
                 'nu': self.gate_nu,
                 'spacing0': self.gate_spacing,
-                'rho_ref': self.gate_rho0
+                'rho_ref': self.gate_rho0,
+                'rho_ref_fluid': self.fluid_density,
             })
 
         # ===================================
@@ -476,21 +478,43 @@ class ElasticGate(Application):
                                                   mach_no_structure=0.,
                                                   gy=0.)
 
+        rogers = FSIWCSPHSchemeRogers(fluids=['fluid'],
+                                      solids=['tank'],
+                                      structures=['gate'],
+                                      structure_solids=['gate_support'],
+                                      dim=2,
+                                      h_fluid=0.,
+                                      rho0_fluid=0.,
+                                      pb_fluid=0.,
+                                      c0_fluid=0.,
+                                      nu_fluid=0.,
+                                      mach_no_fluid=0.,
+                                      mach_no_structure=0.,
+                                      gy=0.)
+
         s = SchemeChooser(default='etvf', etvf=etvf, gtvf=gtvf, wcsph=wcsph,
-                          substep=substep, sswcsph=wcsph_substep)
+                          substep=substep, sswcsph=wcsph_substep, rogers=rogers)
         return s
 
     def configure_scheme(self):
         # dt = 0.125 * self.fluid_spacing * self.hdx / (self.c0_fluid * 1.1)
         # TODO: This has to be changed for solid
-        dt = 0.25 * self.h_fluid / (
-            (self.gate_E / self.gate_rho0)**0.5 + (self.u_max_gate/50.))
+        # dt = 0.25 * self.h_fluid / (
[…]

### 2021-07-16 code/fsi_bm_1.py

@@ -23,9 +23,10 @@ from pysph.examples.solid_mech.impact import add_properties
 #                                                                create_sphere)
 from pysph.tools.geometry import get_2d_block, rotate
 
-from fsi_coupling import FSIScheme
+from fsi_coupling import FSIScheme, FSIGTVFScheme
+from fsi_substepping import FSISubSteppingScheme, FSISubSteppingWCSPHScheme
 from fsi_coupling_wcsph import FSIWCSPHScheme
-from fsi_substepping import FSISubSteppingScheme
+
 from boundary_particles import (add_boundary_identification_properties,
                                 get_boundary_identification_etvf_equations)
 
@@ -149,7 +150,7 @@ class ElasticGate(Application):
         self.fluid_height = 0.6
         self.fluid_density = 1000.0
 
-        spacing = 0.02 / 4.
+        spacing = 0.02 / 7.
         self.hdx = 1.0
 
         self.fluid_spacing = spacing
@@ -204,7 +205,7 @@ class ElasticGate(Application):
 
         # attributes for Sun PST technique
         # dummy value, will be updated in consume user options
-        self.u_max_gate = 13
+        self.u_max_gate = 1
         self.mach_no_gate = self.u_max_gate / self.c0_gate
 
         # for pre step
@@ -223,7 +224,7 @@ class ElasticGate(Application):
 
         self.artificial_stress_eps = 0.3
 
-        self.dt_fluid = 0.125 * self.fluid_spacing * self.hdx / (self.c0_fluid * 1.1)
+        self.dt_fluid = 0.25 * self.fluid_spacing * self.hdx / (self.c0_fluid * 1.1)
         self.dt_solid = 0.25 * self.h_fluid / (
             (self.gate_E / self.gate_rho0)**0.5 + self.u_max_gate)
 
@@ -250,6 +251,8 @@ class ElasticGate(Application):
                                    h=self.h_fluid,
                                    rho=self.fluid_density,
                                    name="fluid")
+        # set the pressure of the fluid
+        fluid.p[:] = - self.fluid_density * self.gy * (max(fluid.y) - fluid.y[:])
 
         # ===================================
         # Create tank
@@ -370,6 +373,20 @@ class ElasticGate(Application):
                          mach_no_structure=0.,
                          gy=0.)
 
+        gtvf = FSIGTVFScheme(fluids=['fluid'],
+                             solids=['tank'],
+                             structures=['gate'],
+                             structure_solids=['gate_support'],
[…]

### 2021-07-16 code/fsi_coupling.py

@@ -1194,6 +1194,14 @@ class FSIScheme(Scheme):
                         )
                     )
 
+            # if self.nu_fluid > 0.:
+            #     eqs.append(
+            #         MomentumEquationViscosity(
+            #             dest=fluid, sources=self.fluids, nu=self.nu_fluid
+            #         )
+
+            #     )
+
             eqs.append(
                 MomentumEquationPressureGradient(
                     dest=fluid, sources=self.fluids + self.solids, gx=self.gx,

### 2021-07-16 code/fsi_coupling_rogers.py

@@ -21,7 +21,7 @@ from solid_mech import (ComputeAuHatETVF, ComputeAuHatETVFSun2019,
                         ResetParticlePositionsIPST, setup_ipst,
                         SetHIJForInsideParticles, ContinuityEquationUhat,
                         ContinuityEquationETVFCorrection, GTVFEOS, ComputeAuHatGTVF,
-                        VelocityGradient2DUhat)
+                        VelocityGradient2DUhat, SolidMechStep)
 
 from pysph.sph.wc.edac import (SolidWallPressureBC)
 
@@ -341,7 +341,74 @@ class EDACEquationFSI(Equation):
         d_ap[d_idx] += tmp*(d_p[d_idx] - s_p_fsi[s_idx])
 
 
-class FSIWCSPHScheme(Scheme):
+class ContinuityEquationHydrodynamicsFluids(Equation):
+    def initialize(self, d_idx, d_arho_fsi):
+        d_arho_fsi[d_idx] = 0.0
+
+    def loop(self, d_idx, d_arho_fsi, d_rho_fsi, s_idx, s_m, s_rho,
+             DWIJ, VIJ):
+        vijdotdwij = DWIJ[0]*VIJ[0] + DWIJ[1]*VIJ[1] + DWIJ[2]*VIJ[2]
+        fac = d_rho_fsi[d_idx] * s_m[s_idx] / s_rho[s_idx]
+        d_arho_fsi[d_idx] += fac * vijdotdwij
+
+
+class ContinuityEquationHydrodynamicsSolids(Equation):
+    def initialize(self, d_idx, d_arho_fsi):
+        d_arho_fsi[d_idx] = 0.0
+
+    def loop(self, d_idx, d_arho_fsi, d_rho_fsi, s_idx, s_m_fsi, s_rho_fsi,
+             DWIJ, VIJ):
+        vijdotdwij = DWIJ[0]*VIJ[0] + DWIJ[1]*VIJ[1] + DWIJ[2]*VIJ[2]
+        fac = d_rho_fsi[d_idx] * s_m_fsi[s_idx] / s_rho_fsi[s_idx]
+        d_arho_fsi[d_idx] += fac * vijdotdwij
+
+
+class SolidMechStepEDAC(SolidMechStep):
+    """This step follows GTVF paper by Zhang 2017"""
+    def stage2(self, d_idx, d_m, d_uhat, d_vhat, d_what, d_x, d_y, d_z, d_rho,
[…]

### 2021-10-22 manuscript/paper.tex
Update to new files. Working UDL simulation.

@@
 \usepackage{multirow}
+\usepackage{booktabs}
 \usepackage[utf8]{inputenc}
 \usepackage{cleveref}
+\usepackage[section]{placeins}
 
@@
 % =========================================
-
-\subsection{Hydrostatic water column on an elastic plate}
-\label{sec:results:hstank-elastic-plate}
-
-In this problem we check the accuracy and stability-preserving property of the
-proposed scheme in handling the fluid structure interaction. This problem has
-been studied in Li et al. (2015), Fourey et al. (2017), Khayyer et
-al. (2018a), Hu et al. (2019), (2021), (2021) papers. This benchmark has an
-analytical solution derived in Li et al. (2015).
-
-We can see the problem description in figure XXX. The water column height is
-2m and has a width of 0.5m. An aluminum plate of thickness 0.05m is placed at
-the bottom of the tank.The material properties of the aluminum are as follows,
-a density of 2700 $kg/m^3$, an Young’s modulus of $E = 6.75 \times 10^{10} Pa$,
-and the Poisson’s ratio $\nu = 0.34$. The plate is clamped on both the
-sides. Once the simulation begins, a sudden hydrostatic pressure force is
-applied on the aluminum plate. With time the plate oscillates and comes to
-rest. We compare the static displacement of the plate with the analytical
-solution.
-
-In the current simulation a total of two particle spacing is used. One with
-$\delta x = 0.04 , 0.02m and 0.01 m$ and use quintic spline as a kernel. We
-use 1e-6, 1e-7 for timestepping of fluid, solid phases respectively. All the
-simulations are run for a total time of $t_f = 1e-4s$. In figures XXX, XXX,
-XXX we show the final positions of the particles with different particle
-resolutions. The fluid contours are pressure and the structure contours is the
-y-displacement. In figure XXX we plot the midpoint deflection with time and
-compare it with the analytical solution provided by khayyer . It can be seen
-that the results produced by the current scheme are accurate and validates the
-scheme for further use in FSI problems. We have run a convergence analysis
-with a reducing spacing and as can be seen in the figure, that as the particle
-spacing is reduced the error is reduced.
-
-Also analyse any other extra plots you are planning to put.
-
 % =========================================
-% end
-% =========================================
-
-\subsection{Elastic bar hanging under gravity}
-\label{sec:elastic-bar-hanging}
-
+\subsection{Hwang 2014 static cantilever beam}
+\label{sec:hwang-2014-static-cantilever-beam}
 Currently this is a sub problem of elastic dam break. In that problem we are
@@
 happening only in the case with gravity and solving such is fun.
-
-\subsection{Dam break with elastic gate}
-\label{sec:dam-break-elastic-gate}
-
-Taken from \citet{sun2019fully}.
-
-A block of fluid, which is suddenly released under gravity hits an elastic
-plate. This benchmark is simulated in many papers.
-
-The material properties of the elastic gate are as follows, and Young's
-modulus of $0.01 GPa$ with a Poisson ratio of $0.35$ and a density of
-$2500 kg/m^3$.
-
-The length of the fluid block is taken as $0.1m$, and the height is $0.3m$,
-and the length of the elastic gate is $0.03m$ with a height of $0.05m$ and is
-placed at a distance of $0.1m$ from the end of the fluid block.
-
-As the simulation starts the fluid starts flowing under the influence of
-gravity and after some time, it hits the elastic gate. Due to the influence of
-the fluid the elastic gate deforms and due to the elastic gate the fluid
-starts raising. The dynamics of both mediums is influenced by one another.
-
-We have compared the the tip of the elastic gate with time against the
-experimental results produced by \cite{xxx}. As can be seen the results
-produced by the current scheme are accurate and are able to reproduce the
-experimental results.
-
-\subsection{Hydrostatic water column on an elastic plate}
-\label{sec:hydrostatic-water-column-on-an-elastic-plate}
-
-In this problem we check the accuracy and stability-preserving property of the
-proposed scheme in handling the fluid structure interaction. This problem has
-been studied in Li et al. (2015), Fourey et al. (2017), Khayyer et
-al. (2018a), Hu et al. (2019), (2021), (2021) papers. This benchmark has an
-analytical solution derived in Li et al. (2015).
-
-We can see the problem description in figure XXX. The water column height is
-2m and has a width of 0.5m. An aluminum plate of thickness 0.05m is placed at
-the bottom of the tank.The material properties of the aluminum are as follows,
-a density of 2700 $kg/m^3$, an Young’s modulus of $E = 6.75 \times 10^{10} Pa$,
-and the Poisson’s ratio $\nu = 0.34$. The plate is clamped on both the
-sides. Once the simulation begins, a sudden hydrostatic pressure force is
-applied on the aluminum plate. With time the plate oscillates and comes to
-rest. We compare the static displacement of the plate with the analytical
-solution.
-
-In the current simulation a total of two particle spacing is used. One with
-$\delta x = 0.04 , 0.02m and 0.01 m$ and use quintic spline as a kernel. We
-use 1e-6, 1e-7 for timestepping of fluid, solid phases respectively. All the
-simulations are run for a total time of $t_f = 1e-4s$. In figures XXX, XXX,
-XXX we show the final positions of the particles with different particle
-resolutions. The fluid contours are pressure and the structure contours is the
-y-displacement. In figure XXX we plot the midpoint deflection with time and
-compare it with the analytical solution provided by khayyer. It can be seen
-that the results produced by the current scheme are accurate and validates the
-scheme for further use in FSI problems. We have run a convergence analysis
-with a reducing spacing and as can be seen in the figure, that as the particle
-spacing is reduced the error is reduced.
-
-Also analyse any other extra plots you are planning to put.
-
-\subsection{Water impact onto a forefront elastic plate}
-\label{sec:water-impact-forefront}
-
-In this example the elastic plate is placed at the end. Which gets
-impacted due to the moving fluid. Further information can be found at
-section 3.2 of \cite{liu2013numerical}, \citet{sun2019fully}.
-
-\subsection{High speed impact of an elastic aluminum wedge on undisturbed
-  water surface}
-\label{sec:wedge-impact-on-water}
-
-Here we simulate a high speed elastic aluminum wedge impacting on undisturbed
-water surface. This benchmark was dealt in
-{A $\delta$ SPH-SPIM coupled method for fluid-structure interaction problems} and
-{abbas khayyer} papers.
-This is an attractive benchmark as it has an semi-analytical solution.
-
-A fluid of length 6 m and a height of 2.2 m is settled inside a tank of length
-6m and height 4m which gives rise to a pressure distribution of a hydrostatic
-tank. Into this hydrostatic tank a wedge of length 0.6m and a thickness of
-0.04m is been dropped with a velocity of 30 m/s. The wedge angle is 10
-degrees. Please see figure \ref{fig:half-wedge-deformable} for visual clarity.
-
-The initial particle spacing is set as 0.005m and the total number of
-particles combining the wedge, tank and fluid is TOBEDONE. The density of the
-fluid is taken as 1000 $kg/m^3$. The material properties of the wedge are as
-follows: density of 2700 $Kg/m^3$, Young's modulus of 6.75 1e10 $N/m^2$ and a
-Poisson ratio of 0.34. An artificial viscosity $alpha$ of 0.1 is used for
-fluids and 1 for solid phase.
-
-In figure \ref{wedge-entering-the-tank}, at different time stamps, we plot the
-pressure fields of water and sigma 00 if the flexible wedge. (We need to give
-some physical insight of what is expected and what is been observed, provided
-our simulations are correct)
-
-A total of three points are marked on the wedge for a qualitative validation.
-In figure \ref{point-A-wedge-displacement}, we plot the displacement of point
-A with time, and compared with Abbhas and and the semi analytical solution of
-scolon 2004. Similarly at point B and point C we compare the pressure of the
-current scheme with the one provided with Abbas and the semi analytical
-solution. It can be seen that the current scheme is able to produce the
-results with a reasonable accuracy.
 
@@
 
-\subsection{Static test to test Structure formulation}
-\label{sec:static-test}
+\subsection{Elastic bar hanging under gravity}
+\label{sec:elastic-bar-hanging}
 
-In \citet{hwang2015development} has a static test where a cantilever beam is
-acted upon by a constant load at the tip.
+Currently this is a sub problem of elastic dam break. In that problem we are
+simulating gate with out considering the gravity. By considering the gravity
+we get float division error.
+
+\subsection{Ng 2020 Hydrostatic water column on an elastic plate}
+\label{sec:hydrostatic-water-column-on-an-composite-elastic-plate}
+
+This has two simulations, one taken from \cite{ng2020coupled} and \cite{khayyer2021coupled}.
+\begin{table}[!ht]
+  \centering
+  \begin{tabular}[!ht]{ll}
+    % \toprule
+    Quantity & Values \\
+    % \midrule
+    $D$, Diameter & 2m \\
+    $\rho_0$, reference density & 1000kg/m\textsuperscript{3} \\
+    $c_s$ & 10m/s \\
+    $D/\Delta x_{\max}$, lowest resolution & 4 \\
+    $D/\Delta x_{\min} $, highest resolution & 160, 250, 500\\
+    $C_r$ & 1.08 \\
+    Reynolds number & 40, 550, 1000, 3000, and 9500 \\
+    Time of simulation & 6 \\
+    % \bottomrule
+  \end{tabular}
+  \caption{Parameters used for the flow past a circular cylinder problem.}%
+  \label{tab:fpc-params}
+\end{table}
+%
+%
+%
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/hydrostatic_water_column_on_an_elastic_plate/hydrostatic_water_column_on_an_elastic_plate}
+  \caption{Hydrostatic tank}
+\label{fig:hs-water-on-plate}
+\end{figure}
+%
+%
+
+\todoin{Comment on the Poisson ratio range of the current scheme}
+\todoin{Who did it previously}
+\todoin{How to derive the analytical solution in short}
+\todoin{Write about the different resolutions}
+\todoin{Any other artificial parameters regarding the scheme, alpha, beta}
+
+\todoin{In this problem we check the accuracy and stability-preserving property of the
+proposed scheme in handling the fluid structure interaction. This problem has
+been studied in Li et al. (2015), Fourey et al. (2017), Khayyer et
+al. (2018a), Hu et al. (2019), (2021), (2021) papers. This benchmark has an
+analytical solution derived in Li et al. (2015).}
+
+The first benchmark test to validate the fluid structure interaction model
+corresponds to an elastic plate under a hydrostatic water tank. An elastic
+plate of length 1m and width of 5cm is placed under a block of water column of
+height 2m is allowed to settle under gravity. The elastic plate is fixed on
+both the ends. The material properties of the water are as follows, the
+density is 1000 $kg/m^3$, viscosity of $1e-6$. And the material properties of
+the elastic plate are as follows, density 2700$kg/m^3$, Young's modulus
+$67.5 \times 10^7$ Pa and a Poisson ratio of 0.34. Three different particle
+spacing are considered. Initially the fluid is set up with a hydrostatic
+pressure distribution as in equation,
+%
+%
+\begin{equation}
+  f_a^F = -m_i \sum_{a} m_a \bigg(\frac{p_a}{\rho_{a}^2} +
+  \frac{p_i}{\rho_{i}^2} + \Pi_{ai} \bigg) \nabla_{a} W(x_{ai}).
+\end{equation}
+%
+%
+Once the plate reaches an equilibrium state, the
+deflection at the midpoint is compared with the analytical solution,
+%
+%
+\begin{equation}
+  f_a^F = -m_i \sum_{a} m_a \bigg(\frac{p_a}{\rho_{a}^2} +
+  \frac{p_i}{\rho_{i}^2} + \Pi_{ai} \bigg) \nabla_{a} W(x_{ai}).
+\end{equation}
+%
+%
+%
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=1\textwidth]{figures/khayyer_2021_hydrostatic_water_column_on_composite_elastic_plate/y_amplitude}
+  \caption{Hydrostatic tank}
+\label{fig:y-disp-hs-water-on-plate}
+\end{figure}
+%
+%
+\Cref{fig:y-disp-hs-water-on-plate} depicts the time histories of the plate's
+center point deflection with three different particle spacing. From the
+presented \Cref{fig:y-disp-hs-water-on-plate} and table \todoin{citetable} we
+can see as the particle spacing is reduced the numerical solution by the
+current model approaches the analytical model, which proves the convergence
+properties of the current scheme. \todoin{compare with other numerical schemes}
+%
+%
+%
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=1\textwidth]{figures/khayyer_2021_hydrostatic_water_column_on_composite_elastic_plate/y_amplitude}
+  \caption{Hydrostatic tank}
+\label{fig:p-hs-tank-elastic-plate}
+\end{figure}
+%
+%
+%
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=1\textwidth]{figures/khayyer_2021_hydrostatic_water_column_on_composite_elastic_plate/y_amplitude}
+  \caption{Hydrostatic tank}
+\label{fig:sigma-hs-tank-elastic-plate}
+\end{figure}
+
+\Cref{fig:p-hs-tank-elastic-plate} shows the pressure distribution in the
+fluid domain at different time histories. \Cref{fig:sigma-hs-water-on-plate}
+shows the plots of $\sigma_{00}$ distribution of the elastic plate at
+different time steps.
+
+\FloatBarrier%
+
+\subsection{Dam break with elastic gate}
+\label{sec:dam-break-elastic-gate}
+
+Taken from \citet{sun2019fully}.
+
+A block of fluid, which is suddenly released under gravity hits an elastic
+plate. This benchmark is simulated in many papers.
+
+The material properties of the elastic gate are as follows, and Young's
+modulus of $0.01 GPa$ with a Poisson ratio of $0.35$ and a density of
+$2500 kg/m^3$.
+
+The length of the fluid block is taken as $0.1m$, and the height is $0.3m$,
+and the length of the elastic gate is $0.03m$ with a height of $0.05m$ and is
+placed at a distance of $0.1m$ from the end of the fluid block.
+
+As the simulation starts the fluid starts flowing under the influence of
+gravity and after some time, it hits the elastic gate. Due to the influence of
+the fluid the elastic gate deforms and due to the elastic gate the fluid
+starts raising. The dynamics of both mediums is influenced by one another.
+
+We have compared the the tip of the elastic gate with time against the
+experimental results produced by \cite{xxx}. As can be seen the results
+produced by the current scheme are accurate and are able to reproduce the
+experimental results.
+
+\subsection{Water impact onto a forefront elastic plate}
+\label{sec:water-impact-forefront}
+
+In this example the elastic plate is placed at the end. Which gets
+impacted due to the moving fluid. Further information can be found at
+section 3.2 of \cite{liu2013numerical}, \citet{sun2019fully}.
+
+\subsection{Water slamming on a sandwich hull}
+\label{sec:water-slamming-on-a-sandwich-hull}
+
+Here we simulate a high speed elastic aluminum wedge impacting on undisturbed
+water surface. This benchmark was dealt in
+{A $\delta$ SPH-SPIM coupled method for fluid-structure interaction problems} and
+{abbas khayyer} papers.
+This is an attractive benchmark as it has an semi-analytical solution.
+
+A fluid of length 6 m and a height of 2.2 m is settled inside a tank of length
+6m and height 4m which gives rise to a pressure distribution of a hydrostatic
+tank. Into this hydrostatic tank a wedge of length 0.6m and a thickness of
+0.04m is been dropped with a velocity of 30 m/s. The wedge angle is 10
+degrees. Please see figure \ref{fig:half-wedge-deformable} for visual clarity.
+
+The initial particle spacing is set as 0.005m and the total number of
+particles combining the wedge, tank and fluid is TOBEDONE. The density of the
+fluid is taken as 1000 $kg/m^3$. The material properties of the wedge are as
+follows: density of 2700 $Kg/m^3$, Young's modulus of 6.75 1e10 $N/m^2$ and a
+Poisson ratio of 0.34. An artificial viscosity $alpha$ of 0.1 is used for
+fluids and 1 for solid phase.
+
+In figure \ref{wedge-entering-the-tank}, at different time stamps, we plot the
+pressure fields of water and sigma 00 if the flexible wedge. (We need to give
+some physical insight of what is expected and what is been observed, provided
+our simulations are correct)
+
+A total of three points are marked on the wedge for a qualitative validation.
+In figure \ref{point-A-wedge-displacement}, we plot the displacement of point
+A with time, and compared with Abbhas and and the semi analytical solution of
+scolon 2004. Similarly at point B and point C we compare the pressure of the
+current scheme with the one provided with Abbas and the semi analytical
+solution. It can be seen that the current scheme is able to produce the
+results with a reasonable accuracy.
+
+\subsection{High speed impact of an elastic aluminum wedge on undisturbed
+  water surface}
+\label{sec:wedge-impact-on-water}
+
+Here we simulate a high speed elastic aluminum wedge impacting on undisturbed
+water surface. This benchmark was dealt in
+{A $\delta$ SPH-SPIM coupled method for fluid-structure interaction problems} and
+{abbas khayyer} papers.
+This is an attractive benchmark as it has an semi-analytical solution.
+
+A fluid of length 6 m and a height of 2.2 m is settled inside a tank of length
+6m and height 4m which gives rise to a pressure distribution of a hydrostatic
+tank. Into this hydrostatic tank a wedge of length 0.6m and a thickness of
+0.04m is been dropped with a velocity of 30 m/s. The wedge angle is 10
+degrees. Please see figure \ref{fig:half-wedge-deformable} for visual clarity.
+
+The initial particle spacing is set as 0.005m and the total number of
+particles combining the wedge, tank and fluid is TOBEDONE. The density of the
+fluid is taken as 1000 $kg/m^3$. The material properties of the wedge are as
+follows: density of 2700 $Kg/m^3$, Young's modulus of 6.75 1e10 $N/m^2$ and a
+Poisson ratio of 0.34. An artificial viscosity $alpha$ of 0.1 is used for
+fluids and 1 for solid phase.
+
+In figure \ref{wedge-entering-the-tank}, at different time stamps, we plot the
+pressure fields of water and sigma 00 if the flexible wedge. (We need to give
+some physical insight of what is expected and what is been observed, provided
+our simulations are correct)
+
+A total of three points are marked on the wedge for a qualitative validation.
+In figure \ref{point-A-wedge-displacement}, we plot the displacement of point
+A with time, and compared with Abbhas and and the semi analytical solution of
+scolon 2004. Similarly at point B and point C we compare the pressure of the
+current scheme with the one provided with Abbas and the semi analytical
+solution. It can be seen that the current scheme is able to produce the
+results with a reasonable accuracy.
 

### 2021-10-22 automate.py

@@ -15,11 +15,11 @@ from pysph.solver.utils import load, get_files
 matplotlib.use('pdf')
 
 matplotlib.use('pdf')
-n_core = free_cores()
-n_thread = 2 * free_cores()
+# n_core = free_cores()
+# n_thread = 2 * free_cores()
 
-# n_core = 4
-# n_thread = 8
+n_core = 16
+n_thread = 32
 backend = ' --openmp '
 
 
@@ -75,6 +75,120 @@ def get_files_at_given_times_from_log(files, times, logfile):
                     time_count += 1
                 file_count += 1
     return result
+
+
+class Hwang2014StaticCantileverBeam(Problem):
+    def get_name(self):
+        return 'hwang_2014_static_cantilever_beam'
+
+    def setup(self):
+        get_path = self.input_path
+
+        cmd = 'python code/hwang_2014_static_cantilever_beam.py' + backend
+
+        # Base case info
+        self.case_info = {
+            'n_5': (dict(
+                pst='sun2019',
+                solid_stress_bc=None,
+                solid_velocity_bc=None,
+                no_edac=None,
+                continuity_correction=None,
+                no_clamp=None,
+                artificial_vis_alpha=2.0,
+                N=5,
+                distributed=None,
+                gradual_force=None,
+                gradual_force_time=0.1,
+                no_wall_pst=None,
+                no_two_layer=None,
+                no_sandwich=None,
+                pfreq=500,
+                tf=0.3,
+                ), 'N 5 '),
+
+            'n_10': (dict(
+                pst='sun2019',
+                solid_stress_bc=None,
+                solid_velocity_bc=None,
+                no_edac=None,
+                continuity_correction=None,
+                no_clamp=None,
+                artificial_vis_alpha=2.0,
+                N=10,
+                distributed=None,
+                gradual_force=None,
+                gradual_force_time=0.1,
+                no_wall_pst=None,
+                pfreq=500,
+                tf=0.3,
+                ), 'N 10'),
+
+            # 'n_10_rk2': (dict(
+            #     pst='sun2019',
+            #     solid_stress_bc=None,
+            #     solid_velocity_bc=None,
+            #     no_edac=None,
+            #     continuity_correction=None,
+            #     no_uhat_vgrad=None,
+            #     integrator="rk2",
+            #     no_clamp=None,
+            #     artificial_vis_alpha=2.0,
+            #     N=10,
+            #     distributed=None,
[…]

### 2021-10-22 code/dam_break.py

@@ -1,320 +1,0 @@
-"""
-A \delta SPH-SPIM coupled method for fluid-structure interaction problems
-
-https://doi.org/10.1016/j.jfluidstructs.2020.103210
-
-Section 3.4 Dam-break flow impacting on an elastic plate
-"""
-
-import numpy as np
-
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-# from rigid_fluid_coupling import RigidFluidCouplingScheme
-from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
-
-from pysph.examples.solid_mech.impact import add_properties
-# from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-#                                                                create_fluid,
-#                                                                create_sphere)
-from pysph.tools.geometry import get_2d_block, rotate
-
-from fsi_coupling import FSIScheme
-from boundary_particles import (add_boundary_identification_properties,
-                                get_boundary_identification_etvf_equations)
-
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-
-
-def get_fixed_beam(beam_length, beam_height, beam_inside_length,
-                   boundary_layers, spacing):
-    """
- |||=============
- |||=============
- |||===================================================================|
- |||===================================================================|Beam height
- |||===================================================================|
- |||=============
- |||=============
-   <------------><---------------------------------------------------->
-      Beam inside                   Beam length
-      length
-    """
-    # create a block first
-    xb, yb = get_2d_block(dx=spacing, length=beam_length, height=beam_height)
-
-    # create a (support) block with required number of layers
-    xs, ys = get_2d_block(dx=spacing, length=beam_length,
-                          height=boundary_layers * spacing)
-    ys -= np.max(yb) - np.min(ys) + spacing
-
-    # import matplotlib.pyplot as plt
-    # plt.scatter(xs, ys, s=1)
-    # plt.scatter(xb, yb, s=1)
-    # plt.axes().set_aspect('equal', 'datalim')
-    # plt.savefig("geometry", dpi=300)
-    # plt.show()
-
-    return xb, yb, xs, ys
-
-
-def get_fixed_beam_with_clamp(beam_length, beam_height, beam_inside_length,
[…]

### 2021-10-22 code/force_application_utils.py

@@ -1,0 +1,83 @@
+import numpy as np
+from pysph.sph.equation import Equation
+
+
+class ApplyForceGradual(Equation):
+    def __init__(self, dest, sources, delta_fx, delta_fy, delta_fz):
+        self.delta_fx = delta_fx
+        self.delta_fy = delta_fy
+        self.delta_fz = delta_fz
+        super(ApplyForceGradual, self).__init__(dest, sources)
+
+    def initialize(self, d_idx, d_au, d_av, d_aw, d_gradual_force_time,
+                   d_total_force_applied_x, d_total_force_applied_y,
+                   d_total_force_applied_z, d_force_idx, d_m, t):
+        if t < d_gradual_force_time[0]:
+            if d_idx == 0:
+                d_total_force_applied_x[0] += self.delta_fx
+                d_total_force_applied_y[0] += self.delta_fy
+                d_total_force_applied_z[0] += self.delta_fz
+
+        if d_force_idx[d_idx] == 1:
+            d_au[d_idx] += d_total_force_applied_x[0] / d_m[d_idx]
+            d_av[d_idx] += d_total_force_applied_y[0] / d_m[d_idx]
+            d_aw[d_idx] += d_total_force_applied_z[0] / d_m[d_idx]
+
+
+class ApplyForceSudden(Equation):
+    def __init__(self, dest, sources, fx, fy, fz):
+        self.fx = fx
+        self.fy = fy
+        self.fz = fz
+        super(ApplyForceSudden, self).__init__(dest, sources)
+
+    def initialize(self, d_idx, d_au, d_av, d_aw, d_force_idx, d_m, t):
+        if d_force_idx[d_idx] == 1:
+            d_au[d_idx] += self.fx / d_m[d_idx]
+            d_av[d_idx] += self.fy / d_m[d_idx]
+            d_aw[d_idx] += self.fz / d_m[d_idx]
+
+
+def tip_load_force_index_single(plate):
+    max_y = np.max(plate.y)
+    indices_1 = np.where(max_y == plate.y)[0]
+    max_x = np.max(plate.x)
+
+    for i in indices_1:
+        if plate.x[i] == max_x:
+            break
+    plate.force_idx[i] = 1
+
+
+def tip_load_force_index_distributed(plate):
+    max_x = np.max(plate.x)
+    indices = np.where(max_x == plate.x)[0]
+
+    plate.force_idx[indices] = 1
+
+
[…]

### 2021-10-22 code/fsi_bm_1.py

@@ -1,581 +1,0 @@
-"""A hydrostatic water column on an elastic plate
-
-https://www.sciencedirect.com/science/article/pii/S0029801820314608#appsec1
-
-Appendix A
-"""
-
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-# from rigid_fluid_coupling import RigidFluidCouplingScheme
-from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
-
-from pysph.examples.solid_mech.impact import add_properties
-# from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-#                                                                create_fluid,
-#                                                                create_sphere)
-from pysph.tools.geometry import get_2d_block, rotate
-
-from fsi_coupling import FSIScheme, FSIGTVFScheme
-from fsi_substepping import FSISubSteppingScheme, FSISubSteppingWCSPHScheme
-from fsi_coupling_wcsph import FSIWCSPHScheme
-
-from boundary_particles import (add_boundary_identification_properties,
-                                get_boundary_identification_etvf_equations)
-
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-
-
-def get_hydrostatic_tank_with_fluid(fluid_length=1., fluid_height=2., tank_height=2.3,
-                                    tank_layers=2, fluid_spacing=0.1):
-    import matplotlib.pyplot as plt
-
-    xf, yf = get_2d_block(dx=fluid_spacing,
-                          length=fluid_length+fluid_spacing/2.,
-                          height=fluid_height+fluid_spacing/2.)
-
-    xt_1, yt_1 = get_2d_block(dx=fluid_spacing,
-                              length=tank_layers*fluid_spacing,
-                              height=tank_height+fluid_spacing/2.)
-    xt_1 -= max(xt_1) - min(xf) + fluid_spacing
-    yt_1 += min(yf) - min(yt_1)
-
-    xt_2, yt_2 = get_2d_block(dx=fluid_spacing,
[…]

### 2021-10-22 code/fsi_coupling.py

@@ -15,14 +15,6 @@ from pysph.tools.sph_evaluator import SPHEvaluator
 from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline,
                                 WendlandQuinticC4, Gaussian, SuperGaussian)
 
-from solid_mech import (ComputeAuHatETVF, ComputeAuHatETVFSun2019,
-                        SavePositionsIPSTBeforeMoving, AdjustPositionIPST,
-                        CheckUniformityIPST, ComputeAuhatETVFIPST,
-                        ResetParticlePositionsIPST, EDACEquation, setup_ipst,
-                        SetHIJForInsideParticles, ContinuityEquationUhat,
-                        ContinuityEquationETVFCorrection, GTVFEOS, ComputeAuHatGTVF,
-                        VelocityGradient2DUhat)
-
 from pysph.sph.wc.edac import (SolidWallPressureBC)
 from pysph.sph.wc.edac import ClampWallPressure
 
@@ -35,109 +27,36 @@ from boundary_particles import (ComputeNormals, SmoothNormals,
 from common import EDACIntegrator
 from pysph.examples.solid_mech.impact import add_properties
 from pysph.sph.wc.linalg import mat_vec_mult
-from pysph.sph.basic_equations import (ContinuityEquation,
-                                       MonaghanArtificialViscosity,
+from pysph.sph.basic_equations import (MonaghanArtificialViscosity,
                                        VelocityGradient3D, VelocityGradient2D)
 from pysph.sph.solid_mech.basic import (IsothermalEOS,
                                         HookesDeviatoricStressRate)
 from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
                                         get_shear_modulus)
 
-from solid_mech_common import AddGravityToStructure
 from pysph.sph.wc.transport_velocity import (MomentumEquationArtificialViscosity)
[…]

### 2021-10-22 code/fsi_coupling_inlet_outlet.py

@@ -1,9 +1,3 @@
-"""
-Run it by
-
-python lid_driven_cavity.py --openmp --scheme etvf --integrator pec --internal-flow --pst sun2019 --re 100 --tf 25 --nx 50 --no-edac -d lid_driven_cavity_scheme_etvf_integrator_pec_pst_sun2019_re_100_nx_50_no_edac_output --detailed-output --pfreq 100
-
-"""
 import numpy
 import numpy as np
 
@@ -18,10 +12,9 @@ from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline,
 from solid_mech import (ComputeAuHatETVF, ComputeAuHatETVFSun2019,
                         SavePositionsIPSTBeforeMoving, AdjustPositionIPST,
                         CheckUniformityIPST, ComputeAuhatETVFIPST,
-                        ResetParticlePositionsIPST, setup_ipst,
+                        ResetParticlePositionsIPST, EDACEquation, setup_ipst,
                         SetHIJForInsideParticles, ContinuityEquationUhat,
-                        ContinuityEquationETVFCorrection, GTVFEOS, ComputeAuHatGTVF,
-                        VelocityGradient2DUhat)
+                        ContinuityEquationETVFCorrection)
 
 from pysph.sph.wc.edac import (SolidWallPressureBC)
 
@@ -44,7 +37,7 @@ from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
 
 from solid_mech_common import AddGravityToStructure
 from pysph.sph.wc.transport_velocity import (MomentumEquationArtificialViscosity)
-from fsi_coupling import (ClampWallPressure, ClampWallPressureFSI)
+from pysph.sph.wc.basic import (TaitEOSHGCorrection)
 
 
 class SolidWallPressureBCFSI(Equation):
@@ -72,16 +65,12 @@ class SolidWallPressureBCFSI(Equation):
             (self.gy - d_av[d_idx])*XIJ[1] + \
             (self.gz - d_aw[d_idx])*XIJ[2]
[…]

### 2021-10-22 code/fsi_substepping.py

@@ -1,2078 +1,0 @@
-import numpy
-import numpy as np
-
-from pysph.sph.equation import Equation, Group, MultiStageEquations
-from pysph.sph.integrator_step import IntegratorStep
-from pysph.sph.scheme import Scheme
-from pysph.sph.scheme import add_bool_argument
-from pysph.tools.sph_evaluator import SPHEvaluator
-from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline,
-                                WendlandQuinticC4, Gaussian, SuperGaussian)
-from pysph.sph.integrator import Integrator
-
-from solid_mech import (ComputeAuHatETVF, ComputeAuHatETVFSun2019,
-                        SavePositionsIPSTBeforeMoving, AdjustPositionIPST,
-                        CheckUniformityIPST, ComputeAuhatETVFIPST,
-                        ResetParticlePositionsIPST, EDACEquation, setup_ipst,
-                        SetHIJForInsideParticles, ContinuityEquationUhat,
-                        ContinuityEquationETVFCorrection, GTVFEOS, ComputeAuHatGTVF,
-                        VelocityGradient2DUhat)
-
-from pysph.sph.wc.edac import (SolidWallPressureBC)
-
-from pysph.sph.integrator import PECIntegrator
-from boundary_particles import (add_boundary_identification_properties)
-
-from boundary_particles import (ComputeNormals, SmoothNormals,
-                                IdentifyBoundaryParticleCosAngleEDAC)
-
-from common import EDACIntegrator
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.sph.wc.linalg import mat_vec_mult
-from pysph.sph.basic_equations import (ContinuityEquation,
-                                       MonaghanArtificialViscosity,
-                                       VelocityGradient3D, VelocityGradient2D)
-from pysph.sph.solid_mech.basic import (IsothermalEOS,
-                                        HookesDeviatoricStressRate)
[…]

### 2021-10-22 code/geometry.py

@@ -103,7 +103,7 @@ def get_fluid_tank_3d(fluid_length,
 
 
 def create_tank_2d_from_block_2d(xf, yf, tank_length, tank_height,
-                                 tank_spacing, tank_layers):
+                                 tank_spacing, tank_layers, close=False):
     """
     This is mainly used by granular flows
 
@@ -129,8 +129,18 @@ def create_tank_2d_from_block_2d(xf, yf, tank_length, tank_height,
     xbottom += min(xleft) - min(xbottom)
     ybottom += min(yleft) - max(ybottom) - tank_spacing
 
-    x = np.concatenate([xleft, xright, xbottom])
-    y = np.concatenate([yleft, yright, ybottom])
+    xtop = np.array([])
+    ytop = np.array([])
+    if close is True:
+        xtop, ytop = get_2d_block(dx=tank_spacing,
+                                  length=max(xright) - min(xleft),
+                                  height=(tank_layers - 1) * tank_spacing,
+                                  center=[0., 0.])
+        xtop += min(xleft) - min(xtop)
+        ytop += max(yleft) - min(ytop) - tank_spacing
+
+    x = np.concatenate([xleft, xright, xbottom, xtop])
+    y = np.concatenate([yleft, yright, ybottom, ytop])
 
     return x, y
 

### 2021-10-22 code/hwang_2014_rolling_tank_with_embedded_hanging_elastic_beam.py

@@ -1,6 +1,13 @@
-"""A hydrostatic water column on an elastic plate
-"""
+"""This is also there is Sun2021, An accurate FSI-SPH modeling of challenging
+fluid-structure interaction problems in two and three dimensions. Which gives
+us the expression for the rolling tank's theta.
 
+
+1. Development of a fully Lagrangian MPS-based coupled method for simulation of
+fluid-structure interaction problems. 3.2.2
+https://doi.org/10.1016/j.jfluidstructs.2014.07.007
+
+"""
 import numpy as np
 
 from pysph.base.kernels import CubicSpline
@@ -9,9 +16,6 @@ from pysph.base.utils import get_particle_array
 from pysph.sph.integrator import EPECIntegrator
 from pysph.solver.application import Application
 from pysph.sph.scheme import SchemeChooser
-
-# from rigid_fluid_coupling import RigidFluidCouplingScheme
-from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
 
 from pysph.examples.solid_mech.impact import add_properties
 # from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
@@ -28,10 +32,53 @@ from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
                                         get_shear_modulus)
 
 
-def get_hydrostatic_tank_with_fluid(fluid_length=1., fluid_height=2., tank_height=2.3,
-                                    tank_layers=2, fluid_spacing=0.1):
-    import matplotlib.pyplot as plt
+def create_tank_2d_from_block_2d(xf, yf, tank_length, tank_height,
+                                 tank_spacing, tank_layers, close=False):
+    """
+    This is mainly used by granular flows
 
+    Tank particles radius is spacing / 2.
+    """
+    ####################################
+    # create the left wall of the tank #
+    ####################################
+    xleft, yleft = get_2d_block(dx=tank_spacing,
+                                length=(tank_layers - 1) * tank_spacing,
+                                height=tank_height + 1. * tank_spacing,
+                                center=[0., 0.])
+    xleft += min(xf) - max(xleft) - tank_spacing
+    yleft += min(yf) - min(yleft)
+
+    xright = xleft + abs(min(xleft)) + tank_length
+    xright -= min(xright) - max(xf) - tank_spacing
+    yright = yleft
+
+    xbottom, ybottom = get_2d_block(dx=tank_spacing,
[…]

### 2021-10-22 code/hwang_2014_static_cantilever_beam.py

@@ -1,0 +1,476 @@
+import numpy as np
+from math import cos, sin, sinh, cosh
+
+# SPH equations
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.scheme import SchemeChooser
+from pysph.sph.equation import Equation
+
+from pysph.base.utils import get_particle_array
+
+from solid_mech_ctvf import SolidsSchemeCTVF
+
+from boundary_particles import (add_boundary_identification_properties,
+                                get_boundary_identification_etvf_equations)
+
+from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
+                                        get_shear_modulus)
+from pysph.tools.geometry import get_2d_tank, get_2d_block
+from solid_mech_common import AddGravityToStructure
+from pysph.sph.scheme import add_bool_argument
+from force_application_utils import (ApplyForceGradual, ApplyForceSudden,
+                                     setup_properties_for_gradual_force,
+                                     setup_properties_for_sudden_force,
+                                     tip_load_force_index_distributed,
+                                     tip_load_force_index_single)
+
+
+def create_circle_1(diameter=1, spacing=0.05, center=None):
+    dx = spacing
+    x = [0.0]
+    y = [0.0]
+    r = spacing
+    nt = 0
+    radius = diameter / 2.
+
+    tmp_dist = radius - spacing/2.
+    i = 0
+    while tmp_dist > spacing/2.:
+        perimeter = 2. * np.pi * tmp_dist
+        no_of_points = int(perimeter / spacing) + 1
+        theta = np.linspace(0., 2. * np.pi, no_of_points)
+        for t in theta[:-1]:
+            x.append(tmp_dist * np.cos(t))
+            y.append(tmp_dist * np.sin(t))
+        i = i + 1
+        tmp_dist = radius - spacing/2. - i * spacing
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
+        return x + center[0], y + center[1]
+
+
+def get_fixed_beam(beam_length, beam_height, cylinder_radius,
+                   boundary_layers, spacing):
+    """
+ |||=============
+ |||=============
+ |||===================================================================|
+ |||===================================================================|Beam height
[…]

### 2021-10-22 code/hydrostatic_tank_2d.py

@@ -1,150 +1,0 @@
-"""A 2d hydrostatic tank.
-"""
-
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-# from rigid_fluid_coupling import RigidFluidCouplingScheme
-from geometry import hydrostatic_tank_2d
-
-from pysph.examples.solid_mech.impact import add_properties
-# from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-#                                                                create_fluid,
-#                                                                create_sphere)
-from pysph.tools.geometry import get_2d_block
-
-from fluids import ETVFScheme
-from boundary_particles import (add_boundary_identification_properties,
-                                get_boundary_identification_etvf_equations)
-
-
-class HydrostaticTank2D(Application):
-    def initialize(self):
-        spacing = 0.05
-        self.hdx = 1.3
-
-        self.fluid_length = 1.0
-        self.fluid_height = 1.0
-        self.fluid_density = 1000.0
-        self.fluid_spacing = spacing
-
-        self.tank_height = 1.5
-        self.tank_layers = 3
-        self.tank_spacing = spacing
-
-        self.body_height = 0.2
-        self.body_length = 0.2
-        self.body_density = 2000
-        self.body_spacing = spacing / 2.
-        self.body_h = self.hdx * self.body_spacing
-
-        self.h = self.hdx * self.fluid_spacing
-
-        # self.solid_rho = 500
-        # self.m = 1000 * self.dx * self.dx
-        self.vref = np.sqrt(2 * 9.81 * self.fluid_height)
-        self.u_max = self.vref
-        self.co = 10 * self.vref
-        self.mach_no = self.vref / self.co
-        self.p0 = self.fluid_density * self.co**2.
-        self.c0 = self.co
-        self.alpha = 0.1
-        self.gy = -9.81
-        self.dim = 2
-
-        # for boundary particles
-        self.seval = None
-        self.boundary_equations = get_boundary_identification_etvf_equations(
-            destinations=["fluid"], sources=["fluid", "tank"],
-            boundaries=None)
-        # print(self.boundary_equations)
-
-    def create_particles(self):
[…]

### 2021-10-22 code/khayyer_2021_clamped_elastic_plate_under_a_uniformly_distributed_load.py

@@ -1,0 +1,618 @@
+import numpy as np
+from math import cos, sin, sinh, cosh
+
+# SPH equations
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.scheme import SchemeChooser
+from pysph.sph.equation import Equation
+
+from pysph.base.utils import get_particle_array
+
+from solid_mech import SolidsScheme, SolidsSchemeGray
+
+from boundary_particles import (add_boundary_identification_properties,
+                                get_boundary_identification_etvf_equations)
+
+from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
+                                        get_shear_modulus)
+from pysph.tools.geometry import get_2d_tank, get_2d_block
+from solid_mech import AddGravityToStructure
+from pysph.sph.scheme import add_bool_argument
+from force_application_utils import (ApplyForceGradual, ApplyForceSudden,
+                                     setup_properties_for_gradual_force,
+                                     setup_properties_for_sudden_force,
+                                     tip_load_force_index_distributed,
+                                     tip_load_force_index_single)
+from pysph.tools.geometry import (remove_overlap_particles)
+from pysph.solver.utils import iter_output, load
+from pysph.solver.utils import get_files
+
+
+def UDL_force_index_single(plate, clamp):
+    max_y = np.max(plate.y)
+    indices = np.where(max_y == plate.y)[0]
+    if clamp is True:
+        indices = (max_y == plate.y) & (plate.x > -0.1) & (plate.x < 0.1)
+    else:
+        indices = np.where(max_y == plate.y)[0]
+
+    plate.force_idx[indices] = 1
+
+
+def UDL_force_index_distributed(plate, clamp):
+    if clamp is True:
+        indices = (plate.x > -0.1) & (plate.x < 0.1)
+        plate.force_idx[indices] = 1
+    else:
+        plate.force_idx[:] = 1
+
+
+def create_circle_1(diameter=1, spacing=0.05, center=None):
+    dx = spacing
+    x = [0.0]
+    y = [0.0]
+    r = spacing
+    nt = 0
+    radius = diameter / 2.
+
+    tmp_dist = radius - spacing/2.
+    i = 0
[…]

### 2021-10-22 code/khayyer_2021_free_oscillating_cantilever_composite_elastic_plate.py

@@ -1,0 +1,465 @@
+import numpy as np
+from numpy import cos, sin, sinh, cosh
+
+# SPH equations
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.scheme import SchemeChooser
+from pysph.sph.equation import Equation
+
+from pysph.base.utils import get_particle_array
+
+from solid_mech import SolidsScheme
+
+from boundary_particles import (add_boundary_identification_properties,
+                                get_boundary_identification_etvf_equations)
+
+from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
+                                        get_shear_modulus)
+from pysph.tools.geometry import get_2d_tank, get_2d_block
+from pysph.sph.scheme import add_bool_argument
+from force_application_utils import (ApplyForceGradual, ApplyForceSudden,
+                                     setup_properties_for_gradual_force,
+                                     setup_properties_for_sudden_force,
+                                     UDL_force_index_distributed,
+                                     UDL_force_index_single,
+                                     tip_load_force_index_distributed,
+                                     tip_load_force_index_single)
+from pysph.solver.utils import iter_output, load
+from pysph.solver.utils import get_files
+
+
+def create_circle_1(diameter=1, spacing=0.05, center=None):
+    dx = spacing
+    x = [0.0]
+    y = [0.0]
+    r = spacing
+    nt = 0
+    radius = diameter / 2.
+
+    tmp_dist = radius - spacing/2.
+    i = 0
+    while tmp_dist > spacing/2.:
+        perimeter = 2. * np.pi * tmp_dist
+        no_of_points = int(perimeter / spacing) + 1
+        theta = np.linspace(0., 2. * np.pi, no_of_points)
+        for t in theta[:-1]:
+            x.append(tmp_dist * np.cos(t))
+            y.append(tmp_dist * np.sin(t))
+        i = i + 1
+        tmp_dist = radius - spacing/2. - i * spacing
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
+        return x + center[0], y + center[1]
+
+
+def get_beam_clamp(beam_length, beam_height, boundary_length,
[…]

### 2021-10-22 code/nasar_2019_non_linear_quasi_static_deflection_of_2d_cantilever_beam.py

@@ -1,0 +1,372 @@
+"""Flexible slender body fluid interaction: Vector-based discrete element
+method with Eulerian smoothed particle hydrodynamics.
+
+$4.1 Non-linear quasi-static deflection of 2-D cantilever beam
+"""
+import numpy as np
+from math import cos, sin, sinh, cosh
+
+# SPH equations
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.scheme import SchemeChooser
+from pysph.sph.equation import Equation
+
+from pysph.base.utils import get_particle_array
+
+from vector_based_dem import VectorBasedDEM
+
+from boundary_particles import (add_boundary_identification_properties,
+                                get_boundary_identification_etvf_equations)
+
+from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
+                                        get_shear_modulus)
+from pysph.tools.geometry import get_2d_tank, get_2d_block
+from pysph.sph.scheme import add_bool_argument
+from force_application_utils import (setup_properties_for_gradual_force,
+                                     setup_properties_for_sudden_force)
+
+
+class ApplyForceGradual(Equation):
+    def __init__(self, dest, sources, delta_fx, delta_fy, delta_fz):
+        self.delta_fx = delta_fx
+        self.delta_fy = delta_fy
+        self.delta_fz = delta_fz
+        super(ApplyForceGradual, self).__init__(dest, sources)
+
+    def initialize(self, d_idx, d_fx, d_fy, d_fz, d_gradual_force_time,
+                   d_total_force_applied_x, d_total_force_applied_y,
+                   d_total_force_applied_z, d_force_idx, d_m, t):
+        if t < d_gradual_force_time[0]:
+            if d_idx == 0:
+                d_total_force_applied_x[0] += self.delta_fx
+                d_total_force_applied_y[0] += self.delta_fy
+                d_total_force_applied_z[0] += self.delta_fz
+
+        if d_force_idx[d_idx] == 1:
+            d_fx[d_idx] += d_total_force_applied_x[0]
+            d_fy[d_idx] += d_total_force_applied_y[0]
+            d_fz[d_idx] += d_total_force_applied_z[0]
+
+
[…]

### 2021-10-22 code/ng_2020_dam_breaking_flow_impacting_an_elastic_plate.py

@@ -24,8 +24,7 @@ from pysph.examples.solid_mech.impact import add_properties
 #                                                                create_sphere)
 from pysph.tools.geometry import get_2d_block, rotate
 
-from fsi_coupling import FSIScheme, FSIGTVFScheme
-from fsi_substepping import FSISubSteppingScheme
+from fsi_coupling import FSIETVFScheme, FSIETVFSubSteppingScheme
 from boundary_particles import (add_boundary_identification_properties,
                                 get_boundary_identification_etvf_equations)
 
@@ -132,100 +131,87 @@ def get_fixed_beam_with_out_clamp(beam_length, beam_height, beam_inside_length,
     return xb, yb, xs, ys
 
 
-class ElasticGate(Application):
-    # def add_user_options(self, group):
-    #     group.add_argument("--rho", action="store", type=float, dest="rho",
-    #                        default=7800.,
-    #                        help="Density of the particle (Defaults to 7800.)")
-    #     add_bool_argument(group, 'clamp', dest='clamp',
-    #                       default=False, help='Clamped beam')
+class Ng2020DamBreakWithAnElasticStructureDB2(Application):
+    def add_user_options(self, group):
+        group.add_argument("--d0", action="store", type=float, dest="d0",
+                           default=1e-3,
+                           help="Spacing between the particles")
 
     def consume_user_options(self):
-        self.dim = 2
+        # ================================================
+        # consume the user options first
+        # ================================================
+        spacing = self.options.d0
 
         # ================================================
-        # properties related to the only fluids
+        # common properties
         # ================================================
-        spacing = 0.004/4.
         self.hdx = 1.0
+        self.gx = 0.
+        self.gy = -9.81
+        self.gz = 0.
+        self.dim = 2
+        self.seval = None
 
+        # ================================================
+        # Fluid properties
+        # ================================================
         self.fluid_length = 0.2
         self.fluid_height = 0.2
-        self.fluid_density = 1000.0
         self.fluid_spacing = spacing
-
-        self.tank_height = 0.4
-        self.tank_length = 0.8
-        self.tank_layers = 3
-        self.tank_spacing = spacing
-
         self.h_fluid = self.hdx * self.fluid_spacing
-
-        # self.solid_rho = 500
-        # self.m = 1000 * self.dx * self.dx
         self.vref_fluid = np.sqrt(2 * 9.81 * self.fluid_height)
[…]

### 2021-10-22 code/ng_2020_elastic_dam_break.py

@@ -1,4 +1,5 @@
-"""A 2d hydrostatic tank.
+"""A coupled Smoothed Particle Hydrodynamics-Volume Compensated Particle Method
+(SPH-VCPM) for Fluid Structure Interaction (FSI) modelling
 """
 
 import numpy as np
@@ -19,16 +20,24 @@ from pysph.examples.solid_mech.impact import add_properties
 #                                                                create_sphere)
 from pysph.tools.geometry import get_2d_block, rotate
 
-from fsi_coupling import FSIScheme, FSIGTVFScheme
-from fsi_substepping import FSISubSteppingScheme, FSISubSteppingWCSPHScheme
-from fsi_coupling_wcsph import FSIWCSPHScheme
-from fsi_coupling_rogers import FSIWCSPHSchemeRogers
+from fsi_coupling import FSIETVFScheme, FSIETVFSubSteppingScheme
 
 from boundary_particles import (add_boundary_identification_properties,
                                 get_boundary_identification_etvf_equations)
 
 from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
                                         get_shear_modulus)
+
+
+def find_displacement_index(pa):
+    x = pa.x
+    y = pa.y
+    min_y = min(y)
+    max_x = max(x)
+    index = (pa.x == max_x) & (pa.y == min_y)
+    pa.add_property('tip_displacemet_index', type='int',
+                    data=np.zeros(len(pa.x)))
+    pa.tip_displacemet_index[index] = 1
 
 
 def get_fixed_beam(beam_length, beam_height, beam_inside_length,
@@ -116,93 +125,86 @@ def get_fixed_beam_without_clamp(beam_length, beam_height, boundary_height, spac
     return xb, yb, xs, ys
 
 
+def set_normals_tank(pa, spacing):
+    min_x = min(pa.x)
+    max_x = max(pa.x)
+    min_y = min(pa.y)
+    # left wall
+    fltr = (pa.x < min_x + 3. * spacing) & (pa.y > min_y + 3. * spacing)
+    for i in range(len(fltr)):
+        if fltr[i] == True:
+            pa.normal[3*i] = 1.
+            pa.normal[3*i+1] = 0.
+            pa.normal[3*i+2] = 0.
+
+    # right wall
+    fltr = (pa.x > max_x - 3. * spacing) & (pa.y > min_y + 3. * spacing)
[…]

### 2021-10-22 code/ng_2020_hydrostatic_water_column_on_elastic_plate.py

@@ -1,4 +1,5 @@
-"""A hydrostatic water column on an elastic plate
+"""A coupled Smoothed Particle Hydrodynamics-Volume Compensated Particle Method
+(SPH-VCPM) for Fluid Structure Interaction (FSI) modelling
 """
 
 import numpy as np
@@ -19,8 +20,8 @@ from pysph.examples.solid_mech.impact import add_properties
 #                                                                create_sphere)
 from pysph.tools.geometry import get_2d_block, rotate
 
-from fsi_coupling import FSIScheme
-from fsi_coupling_wcsph import FSIWCSPHScheme
+from fsi_coupling import FSIETVFSubSteppingScheme
+
 from boundary_particles import (add_boundary_identification_properties,
                                 get_boundary_identification_etvf_equations)
 
@@ -33,8 +34,8 @@ def get_hydrostatic_tank_with_fluid(fluid_length=1., fluid_height=2., tank_heigh
     import matplotlib.pyplot as plt
 
     xf, yf = get_2d_block(dx=fluid_spacing,
-                          length=fluid_length+fluid_spacing/2.,
-                          height=fluid_height+fluid_spacing/2.)
+                          length=fluid_length,
+                          height=fluid_height)
 
     xt_1, yt_1 = get_2d_block(dx=fluid_spacing,
                               length=tank_layers*fluid_spacing,
@@ -60,98 +61,73 @@ def get_hydrostatic_tank_with_fluid(fluid_length=1., fluid_height=2., tank_heigh
     return xf, yf, xt, yt
 
 
-def get_fixed_beam_no_clamp(beam_length, beam_height, beam_inside_length,
-                            boundary_layers, spacing):
-    """
- |||=============
- |||=============
- |||===================================================================|
- |||===================================================================|Beam height
- |||===================================================================|
- |||=============
- |||=============
-   <------------><---------------------------------------------------->
-      Beam inside                   Beam length
-      length
-    """
+def get_elastic_plate_with_support(beam_length, beam_height, boundary_layers,
+                                   spacing):
+    import matplotlib.pyplot as plt
     # create a block first
-    xb, yb = get_2d_block(dx=spacing,
-                          length=beam_length,
+    xb, yb = get_2d_block(dx=spacing, length=beam_length,
                           height=beam_height)
 
     # create a (support) block with required number of layers
-    xs, ys = get_2d_block(dx=spacing,
-                          length=boundary_layers*spacing,
-                          height=beam_height + beam_height)
[…]

### 2021-10-22 code/owen_2020_quasi_static_cantilever_beam.py

@@ -1,0 +1,476 @@
+import numpy as np
+from math import cos, sin, sinh, cosh
+
+# SPH equations
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.scheme import SchemeChooser
+from pysph.sph.equation import Equation
+
+from pysph.base.utils import get_particle_array
+
+from vector_based_dem import VectorBasedDEM
+
+from boundary_particles import (add_boundary_identification_properties,
+                                get_boundary_identification_etvf_equations)
+
+from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
+                                        get_shear_modulus)
+from pysph.tools.geometry import get_2d_tank, get_2d_block
+from solid_mech_common import AddGravityToStructure
+from pysph.sph.scheme import add_bool_argument
+from force_application_utils import (ApplyForceGradual, ApplyForceSudden,
+                                     setup_properties_for_gradual_force,
+                                     setup_properties_for_sudden_force,
+                                     tip_load_force_index_distributed,
+                                     tip_load_force_index_single)
+
+
+def create_circle_1(diameter=1, spacing=0.05, center=None):
+    dx = spacing
+    x = [0.0]
+    y = [0.0]
+    r = spacing
+    nt = 0
+    radius = diameter / 2.
+
+    tmp_dist = radius - spacing/2.
+    i = 0
+    while tmp_dist > spacing/2.:
+        perimeter = 2. * np.pi * tmp_dist
+        no_of_points = int(perimeter / spacing) + 1
+        theta = np.linspace(0., 2. * np.pi, no_of_points)
+        for t in theta[:-1]:
+            x.append(tmp_dist * np.cos(t))
+            y.append(tmp_dist * np.sin(t))
+        i = i + 1
+        tmp_dist = radius - spacing/2. - i * spacing
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
+        return x + center[0], y + center[1]
+
+
+def get_fixed_beam(beam_length, beam_height, cylinder_radius,
+                   boundary_layers, spacing):
+    """
+ |||=============
+ |||=============
+ |||===================================================================|
+ |||===================================================================|Beam height
[…]

### 2021-10-22 code/rb_case_1.py

@@ -1,118 +1,0 @@
-"""A cube translating and rotating freely without the influence of gravity.
-This is used to test the rigid body dynamics equations.
-"""
-
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-from rigid_body_3d import RigidBody3DScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-
-
-class Case0(Application):
-    def initialize(self):
-        self.rho0 = 10.0
-        self.hdx = 1.3
-        self.dx = 0.02
-        self.dy = 0.02
-        self.kn = 1e4
-        self.mu = 0.5
-        self.en = 1.0
-        self.dim = 2
-
-        self.dt = 1e-3
-        self.tf = 10
-
-    def create_scheme(self):
-        rb3d = RigidBody3DScheme(rigid_bodies=['body'], boundaries=None, dim=2)
-        s = SchemeChooser(default='rb3d', rb3d=rb3d)
-        return s
-
-    def configure_scheme(self):
-        dt = self.dt
-        tf = self.tf
-        self.scheme.configure_solver(dt=dt, tf=tf, pfreq=100)
-
-    def create_particles(self):
-        nx, ny = 10, 10
-        dx = self.dx
-        x, y = np.mgrid[0:1:nx * 1j, 0:1:ny * 1j]
-        x = x.flat
-        y = y.flat
-        m = np.ones_like(x) * dx * dx * self.rho0
-        h = np.ones_like(x) * self.hdx * dx
-        # radius of each sphere constituting in cube
-        rad_s = np.ones_like(x) * dx
-        body = get_particle_array(name='body', x=x, y=y, h=h, m=m, rad_s=rad_s)
-        body_id = np.zeros(len(x), dtype=int)
-        body.add_property('body_id', type='int', data=body_id)
-
-        # setup the properties
-        self.scheme.setup_properties([body])
-
-        self.scheme.scheme.set_linear_velocity(body, np.array([0.5, 0.5, 0.]))
-        self.scheme.scheme.set_angular_velocity(body, np.array([0., 0., 1.]))
-
-        # body.vcm[0] = 0.5
-        # body.vcm[1] = 0.5
-        # body.omega[2] = 1.
-
-        return [body]
-
[…]

### 2021-10-22 code/rigid_body_common.py

@@ -1,381 +1,0 @@
-import numpy as np
-from pysph.sph.equation import Equation
-
-from numpy import sqrt, log
-
-
-def set_total_mass(pa):
-    # left limit of body i
-    for i in range(max(pa.body_id) + 1):
-        fltr = np.where(pa.body_id == i)
-        pa.total_mass[i] = np.sum(pa.m[fltr])
-        assert pa.total_mass[i] > 0., "Total mass has to be greater than zero"
-
-
-def set_center_of_mass(pa):
-    # loop over all the bodies
-    for i in range(max(pa.body_id) + 1):
-        fltr = np.where(pa.body_id == i)
-        pa.xcm[3 * i] = np.sum(pa.m[fltr] * pa.x[fltr]) / pa.total_mass[i]
-        pa.xcm[3 * i + 1] = np.sum(pa.m[fltr] * pa.y[fltr]) / pa.total_mass[i]
-        pa.xcm[3 * i + 2] = np.sum(pa.m[fltr] * pa.z[fltr]) / pa.total_mass[i]
-
-
-def set_moment_of_inertia_izz(pa):
-    for i in range(max(pa.body_id) + 1):
-        fltr = np.where(pa.body_id == i)
-        izz = np.sum(pa.m[fltr] * ((pa.x[fltr] - pa.xcm[3 * i])**2. +
-                                   (pa.y[fltr] - pa.xcm[3 * i + 1])**2.))
-        pa.izz[i] = izz
-
-
-def set_moment_of_inertia_and_its_inverse(pa):
-    """Compute the moment of inertia at the beginning of the simulation.
-    And set moment of inertia inverse for further computations.
-    This method assumes the center of mass is already computed."""
-    # no of bodies
-    nb = pa.nb[0]
-    # loop over all the bodies
-    for i in range(nb):
-        fltr = np.where(pa.body_id == i)[0]
-        cm_i = pa.xcm[3 * i:3 * i + 3]
-
-        I = np.zeros(9)
-        for j in fltr:
-            # Ixx
-            I[0] += pa.m[j] * ((pa.y[j] - cm_i[1])**2. +
-                               (pa.z[j] - cm_i[2])**2.)
-
-            # Iyy
-            I[4] += pa.m[j] * ((pa.x[j] - cm_i[0])**2. +
-                               (pa.z[j] - cm_i[2])**2.)
-
-            # Izz
[…]

### 2021-10-22 code/solid_mech.py

@@ -38,10 +38,24 @@ from pysph.sph.integrator import Integrator
 import numpy as np
 from math import sqrt, acos
 from math import pi as M_PI
-from solid_mech_common import AddGravityToStructure
 
 
-class ContinuityEquationUhat(Equation):
+class ElasticSolidContinuityEquation(Equation):
+    def initialize(self, d_idx, d_arho):
+        d_arho[d_idx] = 0.0
+
+    def loop(self, d_idx, d_arho, d_u, d_v, d_w, s_idx, s_m, s_u, s_v, s_w,
+             DWIJ, VIJ):
+        vij = declare('matrix(3)')
+        vij[0] = d_u[d_idx] - s_u[s_idx]
+        vij[1] = d_v[d_idx] - s_v[s_idx]
+        vij[2] = d_w[d_idx] - s_w[s_idx]
+
+        vijdotdwij = DWIJ[0] * vij[0] + DWIJ[1] * vij[1] + DWIJ[2] * vij[2]
+        d_arho[d_idx] += s_m[s_idx] * vijdotdwij
+
+
+class ElasticSolidContinuityEquationUhat(Equation):
     def initialize(self, d_idx, d_arho):
         d_arho[d_idx] = 0.0
 
@@ -56,7 +70,7 @@ class ContinuityEquationUhat(Equation):
         d_arho[d_idx] += s_m[s_idx] * vijdotdwij
 
 
-class ContinuityEquationETVFCorrection(Equation):
+class ElasticSolidContinuityEquationETVFCorrection(Equation):
     """
     This is the additional term arriving in the new ETVF continuity equation
     """
@@ -193,7 +207,7 @@ class SetHIJForInsideParticles(Equation):
                 d_h_b[d_idx] = min_dist / self.kernel_factor + min_dist / 50
 
 
-class MomentumEquationSolids(Equation):
+class ElasticSolidMomentumEquation(Equation):
     def initialize(self, d_idx, d_au, d_av, d_aw):
         d_au[d_idx] = 0.0
         d_av[d_idx] = 0.0
@@ -334,240 +348,10 @@ class MonaghanArtificialStressCorrection(Equation):
                              art_stress22 * DWIJ[2])
 
 
-class ComputeAuHatETVF(Equation):
-    def __init__(self, dest, sources, pb):
-        self.pb = pb
-        super(ComputeAuHatETVF, self).__init__(dest, sources)
-
[…]

### 2021-10-22 code/solid_mech_common.py

@@ -1,14 +1,0 @@
-from pysph.sph.equation import Equation, Group, MultiStageEquations
-
-
-class AddGravityToStructure(Equation):
-    def __init__(self, dest, sources, gx=0.0, gy=0.0, gz=0.0):
-        self.gx = gx
-        self.gy = gy
-        self.gz = gz
-        super(AddGravityToStructure, self).__init__(dest, sources)
-
-    def initialize(self, d_idx, d_au, d_av, d_aw):
-        d_au[d_idx] += self.gx
-        d_av[d_idx] += self.gy
-        d_aw[d_idx] += self.gz

### 2021-10-22 code/sun_2021_appendix_1_floating_body.py

@@ -1,6 +1,8 @@
-"""A hydrostatic water column on an elastic plate
 """
+Appendix 1
 
+https://www.sciencedirect.com/science/article/pii/S0029801820314608#appsec1
+"""
 import numpy as np
 
 from pysph.base.kernels import CubicSpline
@@ -11,7 +13,7 @@ from pysph.solver.application import Application
 from pysph.sph.scheme import SchemeChooser
 
 # from rigid_fluid_coupling import RigidFluidCouplingScheme
-from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
+# from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
 
 from pysph.examples.solid_mech.impact import add_properties
 # from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
@@ -19,13 +21,17 @@ from pysph.examples.solid_mech.impact import add_properties
 #                                                                create_sphere)
 from pysph.tools.geometry import get_2d_block, rotate
 
-from fsi_coupling import FSIETVFSubSteppingScheme
-
+from fsi_coupling import FSIETVFScheme, FSIETVFSubSteppingScheme
 from boundary_particles import (add_boundary_identification_properties,
                                 get_boundary_identification_etvf_equations)
 
 from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
                                         get_shear_modulus)
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.scheme import add_bool_argument
+
+from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
+from pysph.tools.geometry import (remove_overlap_particles)
 
 
 def get_hydrostatic_tank_with_fluid(fluid_length=1., fluid_height=2., tank_height=2.3,
@@ -33,8 +39,8 @@ def get_hydrostatic_tank_with_fluid(fluid_length=1., fluid_height=2., tank_heigh
     import matplotlib.pyplot as plt
 
     xf, yf = get_2d_block(dx=fluid_spacing,
-                          length=fluid_length,
-                          height=fluid_height)
+                          length=fluid_length+fluid_spacing/2.,
+                          height=fluid_height+fluid_spacing/2.)
 
     xt_1, yt_1 = get_2d_block(dx=fluid_spacing,
                               length=tank_layers*fluid_spacing,
[…]

### 2021-10-22 code/sun_2021_sloshing_with_an_elastic_beam_clamped_on_the_tank_bottom.py

@@ -1,0 +1,6 @@
+"""An accurate FSI-SPH modeling of challenging fluid-structure interaction
+problems in two and three dimensions
+
+
+https://doi.org/10.1016/j.oceaneng.2020.108552
+ """

### 2021-10-22 code/test_cantilever_bending_with_out_clamp.py

@@ -1,780 +1,0 @@
-"""Elastic Vibration of a Cantilever Beam
-
-# Taken from
-
-
-1. Nonlinear transient analysis of isotropic and composite shell structures
-under dynamic loading by SPH method. Jun Lin thesis
-
-1. Updated Smoothed Particle Hydrodynamics forSimulating Bending and Compression FailureProgress of Ice
-doi:10.3390/w9110882
-
-
-2. A numerical study on ice failure process and ice-ship interactions by Smoothed Particle Hydrodynamics
-https://doi.org/10.1016/j.ijnaoe.2019.02.008
-
-"""
-import numpy as np
-from math import cos, sin, sinh, cosh
-
-# SPH equations
-from pysph.base.kernels import (QuinticSpline)
-from pysph.solver.solver import Solver
-from pysph.solver.application import Application
-from pysph.tools.sph_evaluator import SPHEvaluator
-from pysph.sph.equation import Group, MultiStageEquations, BasicCodeBlock
-from pysph.sph.scheme import SchemeChooser
-from pysph.sph.equation import Equation
-
-from pysph.base.utils import get_particle_array
-
-from solid_mech import SetHIJForInsideParticles, SolidsScheme
-
-from boundary_particles import (add_boundary_identification_properties,
-                                get_boundary_identification_etvf_equations)
-
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-from pysph.tools.geometry import get_2d_tank, get_2d_block
-from pysph.sph.scheme import add_bool_argument
-
-from compyle.api import declare
-from pysph.sph.equation import Equation, Group, BasicCodeBlock
-from pysph.sph.wc.linalg import gj_solve, augmented_matrix, identity
-from mako.template import Template
-
-
-def shepard_corrections():
-    Group.pre_comp.update(
-        OLDWIJ=BasicCodeBlock(code="OLDWIJ = KERNEL(XIJ, RIJ, HIJ)", OLDWIJ=0.0),
-        WIJ=BasicCodeBlock(code="WIJ = OLDWIJ*d_wij_shepard_denom_1[d_idx]", WIJ=0.0)
-    )
-
-
[…]

### 2021-10-22 code/test_cantilever_bending_with_out_clamp_vertical.py

@@ -1,832 +1,0 @@
-"""Elastic Vibration of a Cantilever Beam
-
-# Taken from
-
-
-1. Nonlinear transient analysis of isotropic and composite shell structures
-under dynamic loading by SPH method. Jun Lin thesis
-
-1. Updated Smoothed Particle Hydrodynamics forSimulating Bending and Compression FailureProgress of Ice
-doi:10.3390/w9110882
-
-
-2. A numerical study on ice failure process and ice-ship interactions by Smoothed Particle Hydrodynamics
-https://doi.org/10.1016/j.ijnaoe.2019.02.008
-
-"""
-import numpy as np
-from math import cos, sin, sinh, cosh
-
-# SPH equations
-from pysph.base.kernels import (QuinticSpline)
-from pysph.solver.solver import Solver
-from pysph.solver.application import Application
-from pysph.tools.sph_evaluator import SPHEvaluator
-from pysph.sph.equation import Group, MultiStageEquations, BasicCodeBlock
-from pysph.sph.scheme import SchemeChooser
-from pysph.sph.equation import Equation
-
-from pysph.base.utils import get_particle_array
-
-from solid_mech import SetHIJForInsideParticles, SolidsScheme
-
-from boundary_particles import (add_boundary_identification_properties,
-                                get_boundary_identification_etvf_equations)
-
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-from pysph.tools.geometry import get_2d_tank, get_2d_block
-from pysph.sph.scheme import add_bool_argument
-
-from compyle.api import declare
-from pysph.sph.equation import Equation, Group, BasicCodeBlock
-from pysph.sph.wc.linalg import gj_solve, augmented_matrix, identity
-from mako.template import Template
-
-
-def shepard_corrections():
-    Group.pre_comp.update(
-        OLDWIJ=BasicCodeBlock(code="OLDWIJ = KERNEL(XIJ, RIJ, HIJ)", OLDWIJ=0.0),
-        WIJ=BasicCodeBlock(code="WIJ = OLDWIJ*d_wij_shepard_denom_1[d_idx]", WIJ=0.0)
-    )
-
-
[…]

### 2021-10-22 code/test_vertical_beam_with_gravity_also_clamped.py

@@ -1,813 +1,0 @@
-"""Elastic Vibration of a Cantilever Beam
-
-# Taken from
-
-
-1. Nonlinear transient analysis of isotropic and composite shell structures
-under dynamic loading by SPH method. Jun Lin thesis
-
-1. Updated Smoothed Particle Hydrodynamics forSimulating Bending and Compression FailureProgress of Ice
-doi:10.3390/w9110882
-
-
-2. A numerical study on ice failure process and ice-ship interactions by Smoothed Particle Hydrodynamics
-https://doi.org/10.1016/j.ijnaoe.2019.02.008
-
-"""
-import numpy as np
-from math import cos, sin, sinh, cosh
-
-# SPH equations
-from pysph.base.kernels import (QuinticSpline)
-from pysph.solver.solver import Solver
-from pysph.solver.application import Application
-from pysph.tools.sph_evaluator import SPHEvaluator
-from pysph.sph.equation import Group, MultiStageEquations, BasicCodeBlock
-from pysph.sph.scheme import SchemeChooser
-from pysph.sph.equation import Equation
-
-from pysph.base.utils import get_particle_array
-
-from solid_mech import SetHIJForInsideParticles, SolidsScheme
-
-from boundary_particles import (add_boundary_identification_properties,
-                                get_boundary_identification_etvf_equations)
-
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-from pysph.tools.geometry import get_2d_tank, get_2d_block, rotate
-from pysph.sph.scheme import add_bool_argument
-
-from compyle.api import declare
-from pysph.sph.equation import Equation, Group, BasicCodeBlock
-from pysph.sph.wc.linalg import gj_solve, augmented_matrix, identity
-from mako.template import Template
-
-
-def shepard_corrections():
-    Group.pre_comp.update(
-        OLDWIJ=BasicCodeBlock(code="OLDWIJ = KERNEL(XIJ, RIJ, HIJ)", OLDWIJ=0.0),
[…]

### 2021-10-22 code/test_water_flowing_under_a_gate.py

@@ -1,455 +1,0 @@
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-# from rigid_fluid_coupling import RigidFluidCouplingScheme
-from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
-
-from pysph.examples.solid_mech.impact import add_properties
-# from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-#                                                                create_fluid,
-#                                                                create_sphere)
-from pysph.tools.geometry import get_2d_block, rotate
-
-from fsi_coupling import FSIScheme
-from boundary_particles import (add_boundary_identification_properties,
-                                get_boundary_identification_etvf_equations)
-
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-
-
-def get_fixed_beam(beam_length, beam_height, beam_inside_length,
-                   boundary_layers, spacing):
-    """
- |||=============
- |||=============
- |||===================================================================|
- |||===================================================================|Beam height
- |||===================================================================|
- |||=============
- |||=============
-   <------------><---------------------------------------------------->
-      Beam inside                   Beam length
-      length
-    """
-    import matplotlib.pyplot as plt
-    # create a block first
-    xb, yb = get_2d_block(dx=spacing, length=beam_length + beam_inside_length,
-                          height=beam_height)
-
-    # create a (support) block with required number of layers
-    xs1, ys1 = get_2d_block(dx=spacing, length=beam_inside_length,
-                            height=boundary_layers * spacing)
-    xs1 += np.min(xb) - np.min(xs1)
-    ys1 += np.min(yb) - np.max(ys1) - spacing
-
-    # create a (support) block with required number of layers
-    xs2, ys2 = get_2d_block(dx=spacing, length=beam_inside_length,
-                            height=boundary_layers * spacing)
-    xs2 += np.min(xb) - np.min(xs2)
-    ys2 += np.max(ys2) - np.min(yb) + spacing
-
-    xs = np.concatenate([xs1, xs2])
-    ys = np.concatenate([ys1, ys2])
-
-    xs3, ys3 = get_2d_block(dx=spacing, length=boundary_layers * spacing,
[…]

### 2021-10-22 code/test_zhang_2021_high_speed_water_entry_of_an_elastic_wedge.py

@@ -1,4 +1,9 @@
-"""A hydrostatic water column on an elastic plate
+"""
+
+A delta SPH-SPIM coupled method for fluid-structure interaction
+problems
+
+https://doi.org/10.1016/j.jfluidstructs.2020.103210
 """
 
 import numpy as np
@@ -11,7 +16,7 @@ from pysph.solver.application import Application
 from pysph.sph.scheme import SchemeChooser
 
 # from rigid_fluid_coupling import RigidFluidCouplingScheme
-from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
+# from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
 
 from pysph.examples.solid_mech.impact import add_properties
 # from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
@@ -19,13 +24,24 @@ from pysph.examples.solid_mech.impact import add_properties
 #                                                                create_sphere)
 from pysph.tools.geometry import get_2d_block, rotate
 
-from fsi_coupling import FSIETVFSubSteppingScheme
-
+# from fsi_coupling import FSIScheme
+from fsi_coupling import FSIETVFScheme, FSIETVFSubSteppingScheme
 from boundary_particles import (add_boundary_identification_properties,
                                 get_boundary_identification_etvf_equations)
 
 from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
                                         get_shear_modulus)
+
+
+def find_displacement_index(pa):
+    x = pa.x
+    y = pa.y
+    min_y = min(y)
+    min_y_indices = np.where(y == min_y)[0]
+    index = min_y_indices[int(len(min_y_indices)/2)]
+    pa.add_property('tip_displacemet_index', type='int',
+                    data=np.zeros(len(pa.x)))
+    pa.tip_displacemet_index[index] = 1
 
 
 def get_hydrostatic_tank_with_fluid(fluid_length=1., fluid_height=2., tank_height=2.3,
@@ -48,8 +64,14 @@ def get_hydrostatic_tank_with_fluid(fluid_length=1., fluid_height=2., tank_heigh
     xt_2 += max(xf) - min(xt_2) + fluid_spacing
     yt_2 += min(yf) - min(yt_2)
 
-    xt = np.concatenate([xt_1, xt_2])
-    yt = np.concatenate([yt_1, yt_2])
+    # create the bottom part
[…]

### 2021-10-22 code/vector_dem_case_1.py

@@ -1,0 +1,370 @@
+"""Case 1 of two particles bonded under axial force
+"""
+import numpy as np
+from math import cos, sin, sinh, cosh
+
+# SPH equations
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.scheme import SchemeChooser
+from pysph.sph.equation import Equation
+
+from pysph.base.utils import get_particle_array
+
+from vector_based_dem import VectorBasedDEM
+
+from boundary_particles import (add_boundary_identification_properties,
+                                get_boundary_identification_etvf_equations)
+
+from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
+                                        get_shear_modulus)
+from pysph.tools.geometry import get_2d_tank, get_2d_block
+from pysph.sph.scheme import add_bool_argument
+from force_application_utils import (setup_properties_for_gradual_force,
+                                     setup_properties_for_sudden_force)
+
+
+class ApplyForceGradual(Equation):
+    def __init__(self, dest, sources, delta_fx, delta_fy, delta_fz):
+        self.delta_fx = delta_fx
+        self.delta_fy = delta_fy
+        self.delta_fz = delta_fz
+        super(ApplyForceGradual, self).__init__(dest, sources)
+
+    def initialize(self, d_idx, d_fx, d_fy, d_fz, d_gradual_force_time,
+                   d_total_force_applied_x, d_total_force_applied_y,
+                   d_total_force_applied_z, d_force_idx, d_m, t):
+        if t < d_gradual_force_time[0]:
+            if d_idx == 0:
+                d_total_force_applied_x[0] += self.delta_fx
+                d_total_force_applied_y[0] += self.delta_fy
+                d_total_force_applied_z[0] += self.delta_fz
+
+        if d_force_idx[d_idx] == 1:
+            d_fx[d_idx] += d_total_force_applied_x[0]
+            d_fy[d_idx] += d_total_force_applied_y[0]
+            d_fz[d_idx] += d_total_force_applied_z[0]
+
+
+class ApplyForceSudden(Equation):
+    def __init__(self, dest, sources, fx, fy, fz):
+        self.fx = fx
[…]

### 2021-10-22 code/vector_dem_case_2.py

@@ -1,0 +1,370 @@
+"""Case 2 of two particles bonded under shear force
+"""
+import numpy as np
+from math import cos, sin, sinh, cosh
+
+# SPH equations
+from pysph.base.kernels import (QuinticSpline)
+from pysph.solver.solver import Solver
+from pysph.solver.application import Application
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.scheme import SchemeChooser
+from pysph.sph.equation import Equation
+
+from pysph.base.utils import get_particle_array
+
+from vector_based_dem import VectorBasedDEM
+
+from boundary_particles import (add_boundary_identification_properties,
+                                get_boundary_identification_etvf_equations)
+
+from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
+                                        get_shear_modulus)
+from pysph.tools.geometry import get_2d_tank, get_2d_block
+from pysph.sph.scheme import add_bool_argument
+from force_application_utils import (setup_properties_for_gradual_force,
+                                     setup_properties_for_sudden_force)
+
+
+class ApplyForceGradual(Equation):
+    def __init__(self, dest, sources, delta_fx, delta_fy, delta_fz):
+        self.delta_fx = delta_fx
+        self.delta_fy = delta_fy
+        self.delta_fz = delta_fz
+        super(ApplyForceGradual, self).__init__(dest, sources)
+
+    def initialize(self, d_idx, d_fx, d_fy, d_fz, d_gradual_force_time,
+                   d_total_force_applied_x, d_total_force_applied_y,
+                   d_total_force_applied_z, d_force_idx, d_m, t):
+        if t < d_gradual_force_time[0]:
+            if d_idx == 0:
+                d_total_force_applied_x[0] += self.delta_fx
+                d_total_force_applied_y[0] += self.delta_fy
+                d_total_force_applied_z[0] += self.delta_fz
+
+        if d_force_idx[d_idx] == 1:
+            d_fx[d_idx] += d_total_force_applied_x[0]
+            d_fy[d_idx] += d_total_force_applied_y[0]
+            d_fz[d_idx] += d_total_force_applied_z[0]
+
+
+class ApplyForceSudden(Equation):
+    def __init__(self, dest, sources, fx, fy, fz):
+        self.fx = fx
[…]

### 2021-10-22 code/zhang_2021_high_speed_water_entry_of_an_elastic_wedge.py

@@ -1,4 +1,19 @@
-"""A hydrostatic water column on an elastic plate
+"""A delta SPH-SPIM coupled method for fluid-structure interaction
+problems
+
+https://doi.org/10.1016/j.jfluidstructs.2020.103210
+
+Also at
+
+Coupling edge-based smoothed finite element method with smoothed particle
+hydrodynamics for fluid structure interaction problems
+
+https://doi.org/10.1016/j.oceaneng.2021.108772
+
+An enhanced ISPH-SPH coupled method for simulation of incompressible
+fluid-elastic structure interactions
+
+https://doi.org/10.1016/j.cpc.2018.05.012
 """
 
 import numpy as np
@@ -11,7 +26,7 @@ from pysph.solver.application import Application
 from pysph.sph.scheme import SchemeChooser
 
 # from rigid_fluid_coupling import RigidFluidCouplingScheme
-from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
+# from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
 
 from pysph.examples.solid_mech.impact import add_properties
 # from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
@@ -19,13 +34,24 @@ from pysph.examples.solid_mech.impact import add_properties
 #                                                                create_sphere)
 from pysph.tools.geometry import get_2d_block, rotate
 
-from fsi_coupling import FSIETVFSubSteppingScheme
-
+# from fsi_coupling import FSIScheme
+from fsi_coupling import FSIETVFScheme, FSIETVFSubSteppingScheme
 from boundary_particles import (add_boundary_identification_properties,
                                 get_boundary_identification_etvf_equations)
 
 from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
                                         get_shear_modulus)
+
+
+def find_displacement_index(pa):
+    x = pa.x
+    y = pa.y
+    min_y = min(y)
+    min_y_indices = np.where(y == min_y)[0]
+    index = min_y_indices[int(len(min_y_indices)/2)]
+    pa.add_property('tip_displacemet_index', type='int',
+                    data=np.zeros(len(pa.x)))
+    pa.tip_displacemet_index[index] = 1
 
 
[…]

### 2021-10-31 manuscript/paper.tex
Updates files according to paper.

@@
 
-\subsection{Elastic bar hanging under gravity}
-\label{sec:elastic-bar-hanging}
-
-Currently this is a sub problem of elastic dam break. In that problem we are
-simulating gate with out considering the gravity. By considering the gravity
-we get float division error.
-
 \subsection{Ng 2020 Hydrostatic water column on an elastic plate}
@@
 
-Taken from \citet{sun2019fully}.
+Taken from \citet{sun2019fully, ng2020coupled}.
 
@@
 
-In this example the elastic plate is placed at the end. Which gets
-impacted due to the moving fluid. Further information can be found at
-section 3.2 of \cite{liu2013numerical}, \citet{sun2019fully}.
-
-\subsection{Water slamming on a sandwich hull}
-\label{sec:water-slamming-on-a-sandwich-hull}
-
-Here we simulate a high speed elastic aluminum wedge impacting on undisturbed
-water surface. This benchmark was dealt in
-{A $\delta$ SPH-SPIM coupled method for fluid-structure interaction problems} and
-{abbas khayyer} papers.
-This is an attractive benchmark as it has an semi-analytical solution.
-
-A fluid of length 6 m and a height of 2.2 m is settled inside a tank of length
-6m and height 4m which gives rise to a pressure distribution of a hydrostatic
-tank. Into this hydrostatic tank a wedge of length 0.6m and a thickness of
-0.04m is been dropped with a velocity of 30 m/s. The wedge angle is 10
-degrees. Please see figure \ref{fig:half-wedge-deformable} for visual clarity.
-
-The initial particle spacing is set as 0.005m and the total number of
-particles combining the wedge, tank and fluid is TOBEDONE. The density of the
-fluid is taken as 1000 $kg/m^3$. The material properties of the wedge are as
-follows: density of 2700 $Kg/m^3$, Young's modulus of 6.75 1e10 $N/m^2$ and a
-Poisson ratio of 0.34. An artificial viscosity $alpha$ of 0.1 is used for
-fluids and 1 for solid phase.
-
-In figure \ref{wedge-entering-the-tank}, at different time stamps, we plot the
-pressure fields of water and sigma 00 if the flexible wedge. (We need to give
-some physical insight of what is expected and what is been observed, provided
-our simulations are correct)
-
-A total of three points are marked on the wedge for a qualitative validation.
-In figure \ref{point-A-wedge-displacement}, we plot the displacement of point
-A with time, and compared with Abbhas and and the semi analytical solution of
-scolon 2004. Similarly at point B and point C we compare the pressure of the
-current scheme with the one provided with Abbas and the semi analytical
-solution. It can be seen that the current scheme is able to produce the
-results with a reasonable accuracy.
+In this example the elastic plate is placed at the end. Which gets impacted
+due to the moving fluid. Further information can be found at section 3.2 of
+\cite{liu2013numerical}, \citet{sun2019fully}, {A $\delta$ SPH-SPIM coupled
+  method for fluid-structure interaction problems}.
 

### 2021-10-31 automate.py

@@ -497,648 +497,6 @@ class OscillatingPlateTurek(Problem):
         plt.close()
 
 
-
-
-class Khayyer2021UDLHomogeneous(Problem):
-    def get_name(self):
-        return 'khayyer_2021_udl_homogeneous'
-
-    def setup(self):
-        get_path = self.input_path
-
-        cmd = 'python code/khayyer_2021_clamped_elastic_plate_under_a_uniformly_distributed_load.py' + backend
-
-        # Base case info
-        self.case_info = {
-            'n_5': (dict(
-                pst='sun2019',
-                solid_stress_bc=None,
-                no_solid_velocity_bc=None,
-                no_edac=None,
-                no_clamp=None,
-                artificial_vis_alpha=2.0,
-                N=5,
-                distributed=None,
-                gradual_force=None,
-                gradual_force_time=0.1,
-                no_wall_pst=None,
-                no_two_layer=None,
-                no_sandwich=None,
-                pfreq=500,
-                tf=1.,
-                ), 'N 5'),
-
-            'damping_n_5': (dict(
-                pst='sun2019',
-                solid_stress_bc=None,
-                no_solid_velocity_bc=None,
-                no_edac=None,
-                damping=None,
-                no_clamp=None,
-                artificial_vis_alpha=2.0,
-                N=5,
-                distributed=None,
-                gradual_force=None,
-                gradual_force_time=0.1,
-                no_wall_pst=None,
-                no_two_layer=None,
-                no_sandwich=None,
-                pfreq=500,
-                tf=0.3,
-                ), 'Damping N 5'),
-
-            'damping_n_10': (dict(
-                pst='sun2019',
-                solid_stress_bc=None,
-                no_solid_velocity_bc=None,
-                no_edac=None,
-                damping=None,
-                no_clamp=None,
-                artificial_vis_alpha=2.0,
-                N=10,
-                distributed=None,
-                gradual_force=None,
-                gradual_force_time=0.1,
-                no_wall_pst=None,
-                no_two_layer=None,
-                no_sandwich=None,
-                pfreq=500,
-                tf=2.,
-                ), 'Damping N 10'),
-
-            'damping_n_20': (dict(
-                pst='sun2019',
-                solid_stress_bc=None,
-                no_solid_velocity_bc=None,
-                no_edac=None,
-                damping=None,
-                no_clamp=None,
[…]

### 2021-10-31 code/beam_under_udf.py

@@ -1,571 +1,0 @@
-import numpy as np
-from math import cos, sin, sinh, cosh
-
-# SPH equations
-from pysph.base.kernels import (QuinticSpline)
-from pysph.solver.solver import Solver
-from pysph.solver.application import Application
-from pysph.tools.sph_evaluator import SPHEvaluator
-from pysph.sph.equation import Group, MultiStageEquations
-from pysph.sph.scheme import SchemeChooser
-from pysph.sph.equation import Equation
-
-from pysph.base.utils import get_particle_array
-
-from solid_mech import SetHIJForInsideParticles, SolidsScheme
-
-from boundary_particles import (add_boundary_identification_properties,
-                                get_boundary_identification_etvf_equations)
-
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-from pysph.tools.geometry import get_2d_tank, get_2d_block
-from solid_mech_common import AddGravityToStructure
-from pysph.sph.scheme import add_bool_argument
-
-
-def get_fixed_beam(beam_length, beam_height, beam_inside_length,
-                   boundary_layers, spacing):
-    """
- |||=============
- |||=============
- |||===================================================================|
- |||===================================================================|Beam height
- |||===================================================================|
- |||=============
- |||=============
-   <------------><---------------------------------------------------->
-      Beam inside                   Beam length
-      length
-    """
-    import matplotlib.pyplot as plt
-    # create a block first
-    xb, yb = get_2d_block(dx=spacing,
-                          length=beam_length + beam_inside_length,
-                          height=beam_height)
-
-    # create a (support) block with required number of layers
-    xs1, ys1 = get_2d_block(dx=spacing,
-                            length=beam_inside_length,
-                            height=boundary_layers * spacing)
-    xs1 += np.min(xb) - np.min(xs1)
-    ys1 += np.min(yb) - np.max(ys1) - spacing
-
-    # create a (support) block with required number of layers
-    xs2, ys2 = get_2d_block(dx=spacing,
-                            length=beam_inside_length,
-                            height=boundary_layers * spacing)
-    xs2 += np.min(xb) - np.min(xs2)
-    ys2 += np.max(ys2) - np.min(yb) + spacing
-
-    xs = np.concatenate([xs1, xs2])
[…]

### 2021-10-31 code/flapping_flexible_wing.py

@@ -1,556 +1,0 @@
-"""
-Flow past cylinder
-"""
-import logging
-from time import time
-import os
-import numpy as np
-from numpy import pi, cos, sin, exp
-
-from pysph.base.kernels import QuinticSpline
-from pysph.base.utils import get_particle_array
-from pysph.sph.equation import Equation
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-from pysph.tools import geometry as G
-from pysph.sph.bc.inlet_outlet_manager import (
-    InletInfo, OutletInfo)
-from pysph.sph.scheme import add_bool_argument
-from pysph.tools.geometry import (get_2d_tank, get_2d_block,
-                                  remove_overlap_particles)
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-
-from pysph.examples.solid_mech.impact import add_properties
-from fsi_substepping import FSISubSteppingScheme
-from nrbc import (EvaluateCharacterisctics, EvaluateNumberDensity,
-                  EvaluatePropertyfromCharacteristics,
-                  ShepardInterpolateCharacteristics)
-from boundary_particles import (add_boundary_identification_properties,
-                                get_boundary_identification_etvf_equations)
-
-logger = logging.getLogger()
-
-# Fluid mechanical/numerical parameters
-u_freestream = 1.0
-rho = 1000
-umax = 1.0
-c0 = 10 * umax
-p0 = rho * c0 * c0
-
-
-def create_circle_1(diameter=0.1, spacing=0.005, center=None):
-    dx = spacing
-    x = [0.0]
-    y = [0.0]
-    r = spacing
-    nt = 0
-    radius = diameter / 2.
-
-    tmp_dist = radius - spacing/2.
-    i = 0
-    while tmp_dist > spacing/2.:
-        perimeter = 2. * np.pi * tmp_dist
-        no_of_points = int(perimeter / spacing) + 1
-        theta = np.linspace(0., 2. * np.pi, no_of_points)
-        for t in theta[:-1]:
-            x.append(tmp_dist * np.cos(t))
-            y.append(tmp_dist * np.sin(t))
-        i = i + 1
-        tmp_dist = radius - spacing/2. - i * spacing
-
-    x = np.array(x)
-    y = np.array(y)
-    x, y = (t.ravel() for t in (x, y))
-    if center is None:
-        return x, y
-    else:
[…]

### 2021-10-31 code/flow_past_cylinder.py

@@ -1,388 +1,0 @@
-"""
-Flow past cylinder
-"""
-import numpy as np
-import os
-
-from pysph.base.kernels import QuinticSpline
-from pysph.sph.equation import Equation
-from pysph.base.utils import get_particle_array
-from pysph.solver.application import Application
-from pysph.tools import geometry as G
-from pysph.sph.wc.edac import EDACScheme
-from pysph.sph.bc.inlet_outlet_manager import (
-        InletInfo, OutletInfo)
-
-# Fluid mechanical/numerical parameters
-rho = 1000
-umax = 1.0
-c0 = 10 * umax
-p0 = rho * c0 * c0
-
-
-class SolidWallNoSlipBCReverse(Equation):
-    def __init__(self, dest, sources, nu):
-        self.nu = nu
-        super(SolidWallNoSlipBCReverse, self).__init__(dest, sources)
-
-    def initialize(self, d_idx, d_auf, d_avf, d_awf):
-        d_auf[d_idx] = 0.0
-        d_avf[d_idx] = 0.0
-        d_awf[d_idx] = 0.0
-
-    def loop(self, d_idx, s_idx, d_m, d_rho, s_rho, d_V, s_V,
-             d_ug, d_vg, d_wg,
-             d_auf, d_avf, d_awf,
-             s_u, s_v, s_w,
-             DWIJ, R2IJ, EPS, XIJ):
-
-        # averaged shear viscosity Eq. (6).
-        etai = self.nu * d_rho[d_idx]
-        etaj = self.nu * s_rho[s_idx]
-
-        etaij = 2 * (etai * etaj)/(etai + etaj)
-
-        # particle volumes; d_V inverse volume.
-        Vi = 1./d_V[d_idx]
-        Vj = 1./s_V[s_idx]
-        Vi2 = Vi * Vi
-        Vj2 = Vj * Vj
-
-        # scalar part of the kernel gradient
-        Fij = XIJ[0]*DWIJ[0] + XIJ[1]*DWIJ[1] + XIJ[2]*DWIJ[2]
-
-        # viscous contribution (third term) from Eq. (8), with VIJ
-        # defined appropriately using the ghost values
-        tmp = 1./d_m[d_idx] * (Vi2 + Vj2) * (etaij * Fij/(R2IJ + EPS))
-
-        d_auf[d_idx] += tmp * (d_ug[d_idx] - s_u[s_idx])
[…]

### 2021-10-31 code/fsi_coupling_inlet_outlet.py

@@ -1,1046 +1,0 @@
-import numpy
-import numpy as np
-
-from pysph.sph.equation import Equation, Group, MultiStageEquations
-from pysph.sph.integrator_step import IntegratorStep
-from pysph.sph.scheme import Scheme
-from pysph.sph.scheme import add_bool_argument
-from pysph.tools.sph_evaluator import SPHEvaluator
-from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline,
-                                WendlandQuinticC4, Gaussian, SuperGaussian)
-
-from solid_mech import (ComputeAuHatETVF, ComputeAuHatETVFSun2019,
-                        SavePositionsIPSTBeforeMoving, AdjustPositionIPST,
-                        CheckUniformityIPST, ComputeAuhatETVFIPST,
-                        ResetParticlePositionsIPST, EDACEquation, setup_ipst,
-                        SetHIJForInsideParticles, ContinuityEquationUhat,
-                        ContinuityEquationETVFCorrection)
-
-from pysph.sph.wc.edac import (SolidWallPressureBC)
-
-from pysph.sph.integrator import PECIntegrator
-from boundary_particles import (add_boundary_identification_properties)
-
-from boundary_particles import (ComputeNormals, SmoothNormals,
-                                IdentifyBoundaryParticleCosAngleEDAC)
-
-from common import EDACIntegrator
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.sph.wc.linalg import mat_vec_mult
-from pysph.sph.basic_equations import (ContinuityEquation,
-                                       MonaghanArtificialViscosity,
-                                       VelocityGradient3D, VelocityGradient2D)
-from pysph.sph.solid_mech.basic import (IsothermalEOS,
-                                        HookesDeviatoricStressRate)
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-
-from solid_mech_common import AddGravityToStructure
-from pysph.sph.wc.transport_velocity import (MomentumEquationArtificialViscosity)
[…]

### 2021-10-31 code/hydrostatic_water_column_on_elastic_plate.py

@@ -1,436 +1,0 @@
-"""A hydrostatic water column on an elastic plate
-"""
-
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-# from rigid_fluid_coupling import RigidFluidCouplingScheme
-from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
-
-from pysph.examples.solid_mech.impact import add_properties
-# from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-#                                                                create_fluid,
-#                                                                create_sphere)
-from pysph.tools.geometry import get_2d_block, rotate
-
-from fsi_coupling import FSIETVFSubSteppingScheme
-
-from boundary_particles import (add_boundary_identification_properties,
-                                get_boundary_identification_etvf_equations)
-
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-
-
-def get_hydrostatic_tank_with_fluid(fluid_length=1., fluid_height=2., tank_height=2.3,
-                                    tank_layers=2, fluid_spacing=0.1):
-    import matplotlib.pyplot as plt
-
-    xf, yf = get_2d_block(dx=fluid_spacing,
-                          length=fluid_length,
-                          height=fluid_height)
-
-    xt_1, yt_1 = get_2d_block(dx=fluid_spacing,
-                              length=tank_layers*fluid_spacing,
-                              height=tank_height+fluid_spacing/2.)
-    xt_1 -= max(xt_1) - min(xf) + fluid_spacing
-    yt_1 += min(yf) - min(yt_1)
-
-    xt_2, yt_2 = get_2d_block(dx=fluid_spacing,
-                              length=tank_layers*fluid_spacing,
-                              height=tank_height+fluid_spacing/2.)
-    xt_2 += max(xf) - min(xt_2) + fluid_spacing
-    yt_2 += min(yf) - min(yt_2)
-
-    xt = np.concatenate([xt_1, xt_2])
-    yt = np.concatenate([yt_1, yt_2])
-
-    # plt.scatter(xf, yf, s=10)
[…]

### 2021-10-31 code/khayyer_2021_clamped_elastic_plate_under_a_uniformly_distributed_load.py

@@ -1,618 +1,0 @@
-import numpy as np
-from math import cos, sin, sinh, cosh
-
-# SPH equations
-from pysph.base.kernels import (QuinticSpline)
-from pysph.solver.solver import Solver
-from pysph.solver.application import Application
-from pysph.tools.sph_evaluator import SPHEvaluator
-from pysph.sph.equation import Group, MultiStageEquations
-from pysph.sph.scheme import SchemeChooser
-from pysph.sph.equation import Equation
-
-from pysph.base.utils import get_particle_array
-
-from solid_mech import SolidsScheme, SolidsSchemeGray
-
-from boundary_particles import (add_boundary_identification_properties,
-                                get_boundary_identification_etvf_equations)
-
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-from pysph.tools.geometry import get_2d_tank, get_2d_block
-from solid_mech import AddGravityToStructure
-from pysph.sph.scheme import add_bool_argument
-from force_application_utils import (ApplyForceGradual, ApplyForceSudden,
-                                     setup_properties_for_gradual_force,
-                                     setup_properties_for_sudden_force,
-                                     tip_load_force_index_distributed,
-                                     tip_load_force_index_single)
-from pysph.tools.geometry import (remove_overlap_particles)
-from pysph.solver.utils import iter_output, load
-from pysph.solver.utils import get_files
-
-
-def UDL_force_index_single(plate, clamp):
-    max_y = np.max(plate.y)
-    indices = np.where(max_y == plate.y)[0]
-    if clamp is True:
-        indices = (max_y == plate.y) & (plate.x > -0.1) & (plate.x < 0.1)
-    else:
-        indices = np.where(max_y == plate.y)[0]
-
-    plate.force_idx[indices] = 1
-
-
-def UDL_force_index_distributed(plate, clamp):
-    if clamp is True:
-        indices = (plate.x > -0.1) & (plate.x < 0.1)
-        plate.force_idx[indices] = 1
-    else:
-        plate.force_idx[:] = 1
-
-
-def create_circle_1(diameter=1, spacing=0.05, center=None):
-    dx = spacing
-    x = [0.0]
-    y = [0.0]
-    r = spacing
-    nt = 0
-    radius = diameter / 2.
-
-    tmp_dist = radius - spacing/2.
-    i = 0
[…]

### 2021-10-31 code/khayyer_2021_free_oscillating_cantilever_composite_elastic_plate.py

@@ -1,465 +1,0 @@
-import numpy as np
-from numpy import cos, sin, sinh, cosh
-
-# SPH equations
-from pysph.base.kernels import (QuinticSpline)
-from pysph.solver.solver import Solver
-from pysph.solver.application import Application
-from pysph.tools.sph_evaluator import SPHEvaluator
-from pysph.sph.equation import Group, MultiStageEquations
-from pysph.sph.scheme import SchemeChooser
-from pysph.sph.equation import Equation
-
-from pysph.base.utils import get_particle_array
-
-from solid_mech import SolidsScheme
-
-from boundary_particles import (add_boundary_identification_properties,
-                                get_boundary_identification_etvf_equations)
-
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-from pysph.tools.geometry import get_2d_tank, get_2d_block
-from pysph.sph.scheme import add_bool_argument
-from force_application_utils import (ApplyForceGradual, ApplyForceSudden,
-                                     setup_properties_for_gradual_force,
-                                     setup_properties_for_sudden_force,
-                                     UDL_force_index_distributed,
-                                     UDL_force_index_single,
-                                     tip_load_force_index_distributed,
-                                     tip_load_force_index_single)
-from pysph.solver.utils import iter_output, load
-from pysph.solver.utils import get_files
-
-
-def create_circle_1(diameter=1, spacing=0.05, center=None):
-    dx = spacing
-    x = [0.0]
-    y = [0.0]
-    r = spacing
-    nt = 0
-    radius = diameter / 2.
-
-    tmp_dist = radius - spacing/2.
-    i = 0
-    while tmp_dist > spacing/2.:
-        perimeter = 2. * np.pi * tmp_dist
-        no_of_points = int(perimeter / spacing) + 1
-        theta = np.linspace(0., 2. * np.pi, no_of_points)
-        for t in theta[:-1]:
-            x.append(tmp_dist * np.cos(t))
-            y.append(tmp_dist * np.sin(t))
-        i = i + 1
-        tmp_dist = radius - spacing/2. - i * spacing
-
-    x = np.array(x)
-    y = np.array(y)
-    x, y = (t.ravel() for t in (x, y))
-    if center is None:
-        return x, y
-    else:
-        return x + center[0], y + center[1]
-
-
-def get_beam_clamp(beam_length, beam_height, boundary_length,
[…]

### 2021-10-31 code/nrbc.py

@@ -1,131 +1,0 @@
-from pysph.sph.equation import Equation
-
-
-class ShepardInterpolateCharacteristics(Equation):
-    def initialize(self, d_idx, d_J1, d_J2u, d_J3u, d_J2v, d_J3v):
-        d_J1[d_idx] = 0.0
-        d_J2u[d_idx] = 0.0
-        d_J3u[d_idx] = 0.0
-
-        d_J2v[d_idx] = 0.0
-        d_J3v[d_idx] = 0.0
-
-    def loop(self, d_idx, d_J1, d_J2u, s_J1, s_J2u, d_J3u, s_J3u, s_idx, s_J2v,
-             s_J3v, d_J2v, d_J3v, WIJ):
-        d_J1[d_idx] += s_J1[s_idx] * WIJ
-        d_J2u[d_idx] += s_J2u[s_idx] * WIJ
-        d_J3u[d_idx] += s_J3u[s_idx] * WIJ
-
-        d_J2v[d_idx] += s_J2v[s_idx] * WIJ
-        d_J3v[d_idx] += s_J3v[s_idx] * WIJ
-
-    def post_loop(self, d_idx, d_J1, d_J2u, d_wij, d_avg_j2u, d_avg_j1, d_J3u,
-                  d_avg_j3u, d_J2v, d_J3v, d_avg_j2v, d_avg_j3v):
-        if d_wij[d_idx] > 1e-14:
-            d_J1[d_idx] /= d_wij[d_idx]
-            d_J2u[d_idx] /= d_wij[d_idx]
-            d_J3u[d_idx] /= d_wij[d_idx]
-
-            d_J2v[d_idx] /= d_wij[d_idx]
-            d_J3v[d_idx] /= d_wij[d_idx]
-
-        else:
-            d_J1[d_idx] = d_avg_j1[0]
-            d_J2u[d_idx] = d_avg_j2u[0]
-            d_J3u[d_idx] = d_avg_j3u[0]
-
-            d_J2v[d_idx] = d_avg_j2v[0]
-            d_J3v[d_idx] = d_avg_j3v[0]
-
-    def reduce(self, dst, t, dt):
-        dst.avg_j1[0] = numpy.average(dst.J1[dst.wij > 0.0001])
-        dst.avg_j2u[0] = numpy.average(dst.J2u[dst.wij > 0.0001])
-        dst.avg_j3u[0] = numpy.average(dst.J3u[dst.wij > 0.0001])
-
[…]

### 2021-10-31 code/sun_2019_dam_breaking_flow_impacting_an_elastic_plate.py

@@ -22,6 +22,10 @@ https://doi.org/10.1016/j.cma.2007.06.004
 
 7.2 Impact of sea waves on solid object
 
+# Image for dimensions
+
+https://ars.els-cdn.com/content/image/1-s2.0-S0889974618308673-gr7_lrg.jpg
+
 """
 
 import numpy as np

### 2021-10-31 code/sun_2021_appendix_1_floating_body.py

@@ -1,417 +1,0 @@
-"""
-Appendix 1
-
-https://www.sciencedirect.com/science/article/pii/S0029801820314608#appsec1
-"""
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-# from rigid_fluid_coupling import RigidFluidCouplingScheme
-# from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
-
-from pysph.examples.solid_mech.impact import add_properties
-# from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-#                                                                create_fluid,
-#                                                                create_sphere)
-from pysph.tools.geometry import get_2d_block, rotate
-
-from fsi_coupling import FSIETVFScheme, FSIETVFSubSteppingScheme
-from boundary_particles import (add_boundary_identification_properties,
-                                get_boundary_identification_etvf_equations)
-
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-from pysph.tools.sph_evaluator import SPHEvaluator
-from pysph.sph.scheme import add_bool_argument
-
-from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
-from pysph.tools.geometry import (remove_overlap_particles)
-
-
-def get_hydrostatic_tank_with_fluid(fluid_length=1., fluid_height=2., tank_height=2.3,
-                                    tank_layers=2, fluid_spacing=0.1):
-    import matplotlib.pyplot as plt
-
-    xf, yf = get_2d_block(dx=fluid_spacing,
-                          length=fluid_length+fluid_spacing/2.,
-                          height=fluid_height+fluid_spacing/2.)
-
-    xt_1, yt_1 = get_2d_block(dx=fluid_spacing,
-                              length=tank_layers*fluid_spacing,
-                              height=tank_height+fluid_spacing/2.)
-    xt_1 -= max(xt_1) - min(xf) + fluid_spacing
-    yt_1 += min(yf) - min(yt_1)
-
-    xt_2, yt_2 = get_2d_block(dx=fluid_spacing,
[…]

### 2021-10-31 code/sun_2021_sloshing_with_an_elastic_beam_clamped_on_the_tank_bottom.py

@@ -1,6 +1,0 @@
-"""An accurate FSI-SPH modeling of challenging fluid-structure interaction
-problems in two and three dimensions
-
-
-https://doi.org/10.1016/j.oceaneng.2020.108552
- """

### 2021-10-31 code/test_nasar_2019_non_linear_quasi_static_deflection_of_2d_cantilever_beam.py

@@ -1,50 +1,0 @@
-from pysph.solver.utils import iter_output, load
-import os
-from matplotlib import pyplot as plt
-import numpy as np
-
-from os import listdir
-from os.path import isfile, join
-
-mypath = 'nasar_2019_non_linear_quasi_static_deflection_of_2d_cantilever_beam_output'
-files = [join(mypath, f) for f in listdir(mypath) if isfile(join(mypath, f)) and f.endswith('hdf5')]
-
-data = load(files[-1])
-arrays = data['arrays']
-pa = arrays['plate']
-
-d_idx = 59
-p = pa.cnt_limits[2 * d_idx]
-q = pa.cnt_limits[2 * d_idx + 1]
-
-for i in range(p, q):
-    sidx = pa.cnt_idxs[i]
-    if sidx == 60:
-        print(sidx)
-
-        print(pa.bc_normal_x0[i])
-        print(pa.bc_normal_y0[i])
-
-        print(pa.bc_normal_x[i])
-        print(pa.bc_normal_y[i])
-
-        print("norm", (pa.bc_normal_x0[i]**2. + pa.bc_normal_y0[i]**2.)**0.5)
-        print("norm", (pa.bc_normal_x[i]**2. + pa.bc_normal_y[i]**2.)**0.5)
-
-        print(pa.bc_normal_contact_x0[i])
-        print(pa.bc_normal_contact_y0[i])
-
-        print(pa.bc_normal_contact_x[i])
-        print(pa.bc_normal_contact_y[i])
-
-        print("norm", (pa.bc_normal_contact_x0[i]**2. + pa.bc_normal_contact_y0[i]**2.)**0.5)
-        print("norm", (pa.bc_normal_contact_x[i]**2. + pa.bc_normal_contact_y[i]**2.)**0.5)
-
-        print("bond B1", pa.bc_B1[i])
-        print("bond B2", pa.bc_B2[i])
-        print("bond B3", pa.bc_B3[i])
-
-        print("Bond length", pa.bc_l0[i])
-
-# print("total contacts", pa.tot_cnts[59])
-# print(pa.cnt_idxs[59*8:60*8])

### 2021-11-19 manuscript/paper.tex
Fresh code to work with. 6 simulations in total.

@@
 
-\subsection{Discrete governing equations}
-
-In this current paper the fluid medium is modelled using the improvised scheme
-of TVF, which is been applied to the free surface flows, called ETVF.
-
-For detailed derivation we point the reader to paper \cite{cite our paper},
-here we only give the discrete equations.
+\subsection{Solid mechanics equations}
 
@@
 
-\begin{multline}
-  \label{eq:sph-discretization-edac}
-  \frac{\tilde{d}p_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; \bigg(
-  (p_{a} - \rho_{a} c_{s}^2) \; \ten{u}_{ab} \; - \;
-  p_{a} \; \tilde{\ten{u}}_{ab} \; - \;
-  (p \; (\tilde{\ten{u}} - \ten{u}))_{ab} \; + \; \\
-  4 \; \nu_{edac}
-  \frac{p_a - p_b}{(\rho_a + \rho_b) (r^2_{ab} + EPS)} \ten{r}_{ab}
-  \bigg) \; \cdot \nabla_{a} W_{ab}
-\end{multline}
-
-\begin{multline}
-  \label{eq:sph-momentum-fluid}
-  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
-  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
-  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}\bigg) \bigg]
-  \nabla_{a} W_{ab} \\
-  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot \nabla_{a} W_{ab} +
-  \ten{g}_{a}.
-\end{multline}
-
 \begin{equation}
@@
   \bigg(\frac{\teng{\sigma}^{'}_{a}}{\rho_a^2} +
-  \frac{\teng{\sigma}^{'}_{b}}{\rho_b^2}\bigg) \bigg]  \nabla_{a} W_{ab} +
-  \ten{g}_{a}.
+  \frac{\teng{\sigma}^{'}_{b}}{\rho_b^2} + \Pi_{ab} \ten{I} \bigg) \bigg]  \cdot \nabla_{a} W_{ab} +
+  \ten{g}_{a},
 \end{equation}
+
+$\Pi_{ab}$ is the artificial
+viscosity~\cite{monaghan-review:2005} to maintain the stability of the
+numerical scheme. It is given as,
+\begin{align}
+  \label{eq:mom-av}
+  \Pi_{ab} =
+  \begin{cases}
+\frac{-\alpha h_{ab} \bar{c}_{ab} \phi_{ab}}{\bar{\rho}_{ab}}
+  & \ten{u}_{ab}\cdot \ten{r}_{ab} < 0, \\
+  0 & \ten{u}_{ab}\cdot \ten{r}_{ab} \ge 0,
+\end{cases}
+\end{align}
+where,
+%
+\begin{equation}
+  \label{eq:av-phiij}
+  \phi_{ab} = \frac{\ten{u}_{ab} \cdot \ten{r}_{ab}}{r^2_{ab} + 0.01 h^2_{ab}},
+\end{equation}
+%
+where $\ten{r}_{ab} = \ten{r}_a - \ten{r}_b$, $\ten{u}_{ab} = \ten{u}_a -
+\ten{u}_b$, $h_{ab} = (h_a + h_b)/2$, $\bar{\rho}_{ab} = (\rho_a + \rho_b)/2$,
+$\bar{c}_{ab} = (c_a + c_b) / 2$, and $\alpha$ is the artificial
+viscosity parameter.
 
@@
 
-In both fluid and solid modelling, the pressure is computed using an
-isothermal equation of state, given as,
 \begin{equation}
@@
 happening only in the case with gravity and solving such is fun.
+
+\begin{table}[!ht]
+  \centering
+  \begin{tabular}[!ht]{ll}
+    % \toprule
+    Quantity & Values \\
+    % \midrule
+    $D$, Diameter & 2m \\
+    $\rho_0$, reference density & 1000kg/m\textsuperscript{3} \\
+    $c_s$ & 10m/s \\
+    $D/\Delta x_{\max}$, lowest resolution & 4 \\
+    $D/\Delta x_{\min} $, highest resolution & 160, 250, 500\\
+    $C_r$ & 1.08 \\
+    Reynolds number & 40, 550, 1000, 3000, and 9500 \\
+    Time of simulation & 6 \\
+    % \bottomrule
+  \end{tabular}
+  \caption{Parameters used for the flow past a circular cylinder problem.}%
+  \label{tab:fpc-params}
+\end{table}
 

### 2021-11-19 code/fsi_coupling.py

@@ -736,67 +736,6 @@ class SubSteppingIntegrator(Integrator):
         self.compute_accelerations()
 
 
-# Continuity Equation for WCSPH part for fluids
-class FluidContinuityEquationWCSPH(Equation):
-    def initialize(self, d_arho, d_idx):
-        d_arho[d_idx] = 0.0
-
-    def loop(self, d_idx, s_idx, s_m, d_rho, s_rho, d_u, d_v,
-             d_w, s_u, s_v, s_w, d_arho, DWIJ):
-        uij = d_u[d_idx] - s_u[s_idx]
-        vij = d_v[d_idx] - s_v[s_idx]
-        wij = d_w[d_idx] - s_w[s_idx]
-
-        udotdij = DWIJ[0]*uij + DWIJ[1]*vij + DWIJ[2]*wij
-        fac = d_rho[d_idx] * s_m[s_idx] / s_rho[s_idx]
-        d_arho[d_idx] += fac * udotdij
-
-
-class FluidContinuityEquationWCSPHSolid(Equation):
-    def initialize(self, d_arho, d_idx):
-        d_arho[d_idx] = 0.0
-
-    def loop(self, d_idx, s_idx, s_m, d_rho, s_rho, d_u, d_v,
-             d_w, s_ugfs, s_vgfs, s_wgfs, d_arho, DWIJ):
-        uij = d_u[d_idx] - s_ugfs[s_idx]
-        vij = d_v[d_idx] - s_vgfs[s_idx]
-        wij = d_w[d_idx] - s_wgfs[s_idx]
-
-        udotdij = DWIJ[0]*uij + DWIJ[1]*vij + DWIJ[2]*wij
-        fac = d_rho[d_idx] * s_m[s_idx] / s_rho[s_idx]
-        d_arho[d_idx] += fac * udotdij
-
-
-class FluidContinuityEquationWCSPHFSI(Equation):
-    def initialize(self, d_arho, d_idx):
-        d_arho[d_idx] = 0.0
-
-    def loop(self, d_idx, s_idx, s_m_fsi, d_rho, s_rho_fsi, d_uhat, d_vhat,
-             d_what, s_uhat, s_vhat, s_what, d_arho, DWIJ):
-        uhatij = d_uhat[d_idx] - s_uhat[s_idx]
-        vhatij = d_vhat[d_idx] - s_vhat[s_idx]
[…]

### 2021-11-19 code/oscillating_plate_turek.py

@@ -19,7 +19,6 @@ from boundary_particles import (add_boundary_identification_properties,
 from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
                                         get_shear_modulus)
 from pysph.tools.geometry import get_2d_tank, get_2d_block
-from solid_mech_common import AddGravityToStructure
 from pysph.sph.scheme import add_bool_argument
 
 
@@ -103,63 +102,20 @@ def get_fixed_beam_no_clamp(beam_length, beam_height, beam_inside_length,
     return xb, yb, xs, ys
 
 
+def find_displacement_index(pa):
+    x = pa.x
+    y = pa.y
+    max_x = max(x)
+    max_x_indices = np.where(x == max_x)[0]
+    index = max_x_indices[int(len(max_x_indices)/2)]
+    pa.add_property('tip_displacemet_index', type='int',
+                    data=np.zeros(len(pa.x)))
+    pa.tip_displacemet_index[index] = 1
+    pa.add_output_arrays(['tip_displacemet_index'])
+
+
 class OscillatingPlate(Application):
-    def initialize(self):
-        # dummy value to make the scheme work
-        self.plate_rho0 = 1000.
-        self.plate_E = 1.4 * 1e6
-        self.plate_nu = 0.4
-        self.c0 = get_speed_of_sound(self.plate_E, self.plate_nu,
-                                     self.plate_rho0)
-        self.pb = self.plate_rho0 * self.c0**2
-
-        self.edac_alpha = 0.5
-        self.hdx = 1.2
-
-        # this is dummpy value
-        self.h = 0.001
-        self.edac_nu = self.edac_alpha * self.c0 * self.h / 8
-
-        # attributes for Sun PST technique
-        # dummy value, will be updated in consume user options
-        self.u_max = 2.8513
-        self.mach_no = self.u_max / self.c0
-
-        self.cylinder_r = 0.05
-
-        # for pre step
-        self.seval = None
-
-        # boundary equations
-        # self.boundary_equations = get_boundary_identification_etvf_equations(
-            # destinations=["plate"], sources=["plate"])
-        self.boundary_equations = get_boundary_identification_etvf_equations(
-            destinations=["plate"],
-            sources=["plate", "wall"],
-            boundaries=["wall"])
-
     def add_user_options(self, group):
-        group.add_argument("--rho",
-                           action="store",
-                           type=float,
-                           dest="rho",
-                           default=1000.,
[…]

### 2021-11-19 code/solid_mech.py

@@ -40,21 +40,6 @@ from math import sqrt, acos
 from math import pi as M_PI
 
 
-class ElasticSolidContinuityEquation(Equation):
-    def initialize(self, d_idx, d_arho):
-        d_arho[d_idx] = 0.0
-
-    def loop(self, d_idx, d_arho, d_u, d_v, d_w, s_idx, s_m, s_u, s_v, s_w,
-             DWIJ, VIJ):
-        vij = declare('matrix(3)')
-        vij[0] = d_u[d_idx] - s_u[s_idx]
-        vij[1] = d_v[d_idx] - s_v[s_idx]
-        vij[2] = d_w[d_idx] - s_w[s_idx]
-
-        vijdotdwij = DWIJ[0] * vij[0] + DWIJ[1] * vij[1] + DWIJ[2] * vij[2]
-        d_arho[d_idx] += s_m[s_idx] * vijdotdwij
-
-
 class ElasticSolidContinuityEquationUhat(Equation):
     def initialize(self, d_idx, d_arho):
         d_arho[d_idx] = 0.0
@@ -88,67 +73,6 @@ class ElasticSolidContinuityEquationETVFCorrection(Equation):
         vijdotdwij = (DWIJ[0] * tmp0 + DWIJ[1] * tmp1 + DWIJ[2] * tmp2)
 
         d_arho[d_idx] += s_m[s_idx] / s_rho[s_idx] * vijdotdwij
-
-
-class VelocityGradient2DUhat(Equation):
-    def initialize(self, d_idx, d_v00, d_v01, d_v10, d_v11):
-        d_v00[d_idx] = 0.0
-        d_v01[d_idx] = 0.0
-        d_v10[d_idx] = 0.0
-        d_v11[d_idx] = 0.0
-
-    def loop(self, d_uhat, d_vhat, d_what, d_idx, s_idx, s_m, s_rho, d_v00,
-             d_v01, d_v10, d_v11, s_uhat, s_vhat, s_what, DWIJ):
-        vij = declare('matrix(3)')
-        vij[0] = d_uhat[d_idx] - s_uhat[s_idx]
-        vij[1] = d_vhat[d_idx] - s_vhat[s_idx]
-        vij[2] = d_what[d_idx] - s_what[s_idx]
-
-        tmp = s_m[s_idx] / s_rho[s_idx]
-
-        d_v00[d_idx] += tmp * -vij[0] * DWIJ[0]
-        d_v01[d_idx] += tmp * -vij[0] * DWIJ[1]
-
[…]

### 2021-12-06 automate.py
Update examples to FSI WCSPH code.

@@ -213,7 +213,7 @@ class DamBreak2D(Problem):
     def setup(self):
         get_path = self.input_path
 
-        cmd = 'python code/dam_break_2d.py' + backend + ' --detailed '
+        cmd = 'python code/dam_break_2d.py' + backend
 
         # Base case info
         self.case_info = {
@@ -221,8 +221,8 @@ class DamBreak2D(Problem):
                 pst='sun2019',
                 no_edac=None,
                 no_cont_vc_bc=None,
-                dx=0.05,
-                tf=0.5,
+                dx=1e-3,
+                tf=1.,
                 pfreq=200,
                 alpha=0.05
             ), 'WCSPH'),
@@ -232,7 +232,7 @@ class DamBreak2D(Problem):
                 edac=None,
                 no_cont_vc_bc=None,
                 dx=0.05,
-                tf=0.5,
+                tf=1.,
                 pfreq=200,
                 alpha=0.05
             ), 'WCSPH'),
@@ -243,7 +243,7 @@ class DamBreak2D(Problem):
                 no_clamp_p=None,
                 cont_vc_bc=None,
                 dx=0.05,
-                tf=0.5,
+                tf=1.,
                 pfreq=200,
                 alpha=0.05
             ), 'WCSPH'),
@@ -276,7 +276,7 @@ class HydrostaticTank(Problem):
                 pst='sun2019',
                 no_edac=None,
                 no_cont_vc_bc=None,
-                dx=0.05,
+                dx=1e-3,
                 tf=1.,
                 pfreq=200,
                 alpha=0.05
@@ -326,21 +326,45 @@ class Ng2020HydrostaticWaterColumnOnElasticPlate(Problem):
     def setup(self):
         get_path = self.input_path
 
-        cmd = 'python code/ng_2020_hydrostatic_water_column_on_elastic_plate.py' + backend + ' --max-s 1 '
+        cmd = 'python code/ng_2020_hydrostatic_water_column_on_elastic_plate.py' + backend
 
         # Base case info
         self.case_info = {
-            'd0_1e_minus_2': (dict(
+            'N_10': (dict(
                 scheme='wcsph',
                 solid_velocity_bc=None,
+                alpha_fluid=2.0,
                 no_wall_pst=None,
                 damping=None,
                 damping_coeff=0.002,
                 pfreq=500,
-                tf=0.1,
-                d0=1e-2,
[…]

### 2021-12-06 code/dam_break_2d.py

@@ -22,12 +22,13 @@ from pysph.sph.scheme import SchemeChooser
 
 from boundary_particles import (add_boundary_identification_properties,
                                 get_boundary_identification_etvf_equations)
+from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
 
 
-fluid_column_height = 2.0
-fluid_column_width = 1.0
-container_height = 4.0
-container_width = 4
+fluid_column_height = 0.292
+fluid_column_width = 0.146
+container_height = 0.3
+container_width = 0.7
 nboundary_layers = 4
 
 g = 9.81
@@ -49,12 +50,17 @@ class Dambreak2D(DB.DamBreak2D):
         # print(self.boundary_equations)
 
     def create_particles(self):
-        xt, yt = get_2d_tank(dx=self.dx, length=container_width,
-                             height=container_height, num_layers=nboundary_layers)
+        # ===================================
+        # Create fluid
+        # ===================================
         xf, yf = get_2d_block(dx=self.dx, length=fluid_column_width,
-                              height=fluid_column_height, center=[-1.5, 1])
-        xt += 2.0
-        xf += 2.0
+                              height=fluid_column_height)
+
+        xt, yt = create_tank_2d_from_block_2d(
+            xf, yf, container_width, container_height, self.dx,
+            nboundary_layers)
+        # xt += 2.0
+        # xf += 2.0
         xf += self.dx
         yf += self.dx
         h = self.hdx * self.dx

### 2021-12-06 code/fluids_wcsph.py

@@ -117,9 +117,9 @@ class FluidContinuityEquationWCSPHOnFluidSolid(Equation):
 
     def loop(self, d_idx, s_idx, s_m, d_rho, s_rho, d_u, d_v, d_w,
              s_ugfs, s_vgfs, s_wgfs, d_arho, DWIJ):
-        uhatij = d_u[d_idx] - s_ugfs[s_idx]
-        vhatij = d_v[d_idx] - s_vgfs[s_idx]
-        whatij = d_w[d_idx] - s_wgfs[s_idx]
+        uhatij = d_u[d_idx] - s_ugfs[s_idx] * 0.
+        vhatij = d_v[d_idx] - s_vgfs[s_idx] * 0.
+        whatij = d_w[d_idx] - s_wgfs[s_idx] * 0.
 
         udotdij = DWIJ[0] * uhatij + DWIJ[1] * vhatij + DWIJ[2] * whatij
         fac = d_rho[d_idx] * s_m[s_idx] / s_rho[s_idx]

### 2021-12-06 code/fsi_wcsph.py

@@ -705,6 +705,7 @@ class FSIWCSPHScheme(Scheme):
             FluidEDACEquationWCSPHOnFluid,
             FluidEDACEquationWCSPHOnFluidSolid,
 
+            StateEquation,
             FluidSolidWallPressureBCFluidSolid,
             FluidClampWallPressureFluidSolid,
             FluidMomentumEquationPressureGradient,
@@ -746,26 +747,6 @@ class FSIWCSPHScheme(Scheme):
         # =========================#
         # fluid equations
         # =========================#
-        if len(self.solids) > 0:
-            eqs_u = []
-
-            for solid in self.solids:
-                eqs_u.append(
-                    FluidSetWallVelocityUFreeSlipAndNoSlip(
-                        dest=solid, sources=self.fluids))
-
-            stage1.append(Group(equations=eqs_u, real=False))
-
-        if len(self.structure_solids) > 0:
-            eqs_u = []
-
-            for solid in self.structure_solids:
-                eqs_u.append(
-                    FluidSetWallVelocityUFreeSlipAndNoSlip(
-                        dest=solid, sources=self.fluids))
-
-            stage1.append(Group(equations=eqs_u, real=False))
-
         # ============================
         # Continuity and EDAC equation
         # ============================
@@ -775,44 +756,20 @@ class FSIWCSPHScheme(Scheme):
                 dest=fluid,
                 sources=self.fluids))
 
-            eqs.append(FluidEDACEquationWCSPHOnFluid(
-                dest=fluid,
-                sources=self.fluids,
-                nu=nu_edac
-            ))
-
             if len(self.solids) > 0:
                 eqs.append(FluidContinuityEquationWCSPHOnFluidSolid(
                     dest=fluid,
                     sources=self.solids))
-
-                eqs.append(FluidEDACEquationWCSPHOnFluidSolid(
-                    dest=fluid,
-                    sources=self.solids,
-                    nu=nu_edac
-                ))
 
             if len(self.structures) > 0:
                 eqs.append(FluidContinuityEquationWCSPHOnStructure(
                     dest=fluid,
                     sources=self.structures))
 
-                eqs.append(FluidEDACEquationWCSPHOnStructure(
-                    dest=fluid,
-                    sources=self.structures,
-                    nu=nu_edac
-                ))
-
             if len(self.structure_solids) > 0:
                 eqs.append(FluidContinuityEquationWCSPHOnStructureSolid(
                     dest=fluid,
                     sources=self.structure_solids))
-
[…]

### 2021-12-14 manuscript/paper.tex
Update examples to FSI WCSPH code.
Automate snapshot code. Wedge entry automation.

@@
 
-Some FSI introduction. Its importance in different fields. Its applications so
-far.
-
-In modelling FSI problems, there are mainly two ways to handle the fluid and
-structures modelling. One way is to model the fluid part with mesh based
-scheme and solids part also with mesh based scheme. Like how (cite many papers
-which have done this). Or fluid part is modelled with a particle based scheme
-and the structures part with a mesh based scheme (Cite articles which have
-done this). One more way is to model both the phases using particle based
-schemes. In this paper we use particle based method to model both the phases.
-
-Recently there has been very good work on modelling fsi with particle based
-methods. Specific to particle based modelling, the fluid is modelled with SPH,
-and structure is modelled with different numerical method. Few articles which
-have done in this regard are as follows, citet{hosseini2009particle} has
-modelled the structure part using EBG method, then \citet{wu2016coupled}
-modelled it with DEM, \citet{ng2020coupled} modeled it using volume
-compensated particle method (VCPM), \citet{peng2021coupling} modeled it with
-RKPM, citet{zhang2021deltasph} modeled it with Smoothed Point Interpolation
-Method (SPIM).
-
-Recently there have been heavy improvements to basic SPH methodology in
-modelling fluid problems. Schemes such as $\delta$ SPH, $\delta +$ SPH, TVF
-for internal flows and GTVF for external flows is been proposed. Also, many
-new strategies were proposed to in overcoming the particle homogeneity
-problem, such as IPST, which is applied in \cite{IPST paper}. Also these
-improvements take care of tensile instability problem too. Another variant of
-SPH is ISPH, todoin{please cite some ISPH papers here}.
-
-Using only SPH, articles have been proposed where we model both the phases
-only using SPH. To note some, \citet{He2017coupled} has modelled the fluid
-part with WCSPH, \citet{Sun2019study} with delta sph,
-\citet{zhan2019stabilized} with WCSPH but applied to 3d problems with GPU. All
-these schemes use TLSPH as to model the structure part. And papers by Abbas use
-usual Gray equations to model the structures part.
-
-\citet{sun2019fully} couples MPS and BPM model to simulate FSI. He models both
-elastic dam break and flow over an elastic obstacle.
-
-Recently {cite our paper ETVF} has been proposed as an another extension to
-TVF to model both fluid and structures part. In the current work we couple
-purely Eulerian SPH based schemes to model the FSI problems. We take advantage
-of the accuracy of the ETVF scheme proposed in modelling the fluids. ETVF
-scheme deals with tensile instability in both fluid and solid inherently.
+Xu has introduced the particle shifting and adjusted the particles and applied
+it to fluid problems. TVF is a new variant which unifies the formulation and
+applied it to fluid problems. This TVF has been generalized and applied to free
+surface problems as well as elastic solid problems.
 
@@
 
-\subsection{Solid mechanics equations}
+continuity equation
+\begin{equation}
+  \label{eq:ce}
+  \frac{d \rho}{d t} = - \rho \; \frac{\partial u_i}{\partial x_i},
+\end{equation}
+and by the momentum equation
+\begin{equation}
+  \label{eq:me}
+  \frac{d u_i}{d t} = \frac{1}{\rho} \; \frac{\partial \sigma_{ij}}{\partial x_j}
+  + g_i,
+\end{equation}
+with $\frac{{d} }{d t}$, $\rho$, $t$, $u_i$, $x_i$, $\sigma_{ij}$ and $g_{i}$
+denoting material derivative, density, time, velocity vector, position vector,
+stress tensor and gravity, respectively.
 
-The discretized equations of the fluid medium are
+The stress tensor is split into isotropic and deviatoric parts,
+\begin{equation}
+  \label{eq:stress_tensor_decomposition}
+  \sigma_{ij} = - p \; \delta_{ij} + \sigma'_{ij},
+\end{equation}
+where $p$ and $\delta_{ij}$ denote pressure and Kronecker delta function, while
+$\sigma'_{ij}$ is the deviatoric stress.
 
+The rate of change of deviatoric stress $\frac{d \sigma'_{ij}}{dt}$ can be
+computed from the strain rate $\dot{\epsilon}_{ij}$ and rotation tensor
+$\dot{\Omega}_{ij}$ according to Jaumann's formulation for Hooke's stress law
+as
+\begin{equation}
+  \label{eq:jaumann-stress-rate}
+  \frac{d \sigma'_{ij}}{dt} = 2G (\dot{\epsilon}_{ij} - \frac{1}{3}
+  \dot{\epsilon}_{kk} \delta_{ij}) + \sigma^{'}_{ik}  \Omega_{jk} +
+  \Omega_{ik} \sigma^{'}_{kj}.
+\end{equation}
+Here $G$ is the shear modulus, while $\dot{\epsilon}_{ij}$ is
+\begin{equation}
+  \label{eq:strain-tensor}
+  \dot{\epsilon}_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} +
+  \frac{\partial u_j}{\partial x_i} \bigg),
+\end{equation}
+and $\Omega_{ij}$ is
+\begin{equation}
+  \label{eq:rotational-tensor}
+  \Omega_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} -
+  \frac{\partial u_j}{\partial x_i} \bigg).
+\end{equation}
+
+For a weakly-compressible or incompressible fluid the deviatoric stress
+vanishes and a viscous force is added to the stress tensor:
+\begin{equation}
+  \label{eq:fluid-stress-decomposition}
+  \sigma_{ij} = - p \delta_{ij} + 2 \eta \frac{\partial u_i}{\partial x_j}
+\end{equation}
+where $\eta$ is the kinematic viscosity of the fluid.
+
+In both fluid and solid modelling the pressure is computed using an
+isothermal equation of state, given as,
+\begin{equation}
+  \label{eq:pressure-equation}
+  p = K \bigg(\frac{\rho}{\rho_{0}} - 1 \bigg),
+\end{equation}
+where $K = \rho_{0} c_0^2$ is the bulk modulus. Here, the constants $c_0$ and
+$\rho_0$ are the reference speed of sound and density, respectively. For solids,
+$c_0$ is computed as $\sqrt{\frac{E}{3 (1 - 2 \nu)\rho_{0}}}$, $\nu$ is the
+Poisson ratio.
+
+\section{Numerical method}
+
+Write about Material derivative
+
+\begin{equation}
+  \label{eq:modified-material-derivative}
+  \frac{\tilde{d} }{d t} = \frac{\partial }{\partial t} +
+  \tilde{u}_j \frac{\partial }{\partial x_j}.
+\end{equation}
+
+\begin{equation}
+  \label{eq:ce-tvf}
+  \frac{\tilde{d} \rho}{d t} =
+  - \rho \frac{\partial \tilde{u}_j}{\partial x_j} +
+  \frac{\partial (\rho (\tilde{u}_j - u_j))}{\partial x_j}.
+\end{equation}
+
+\begin{equation}
+  \label{eq:mom-tvf}
+  \frac{\tilde{d} u_i}{d t} =
+  \frac{\partial}{\partial x_j} (u_i (\tilde{u}_j - u_j))
+  - u_i \frac{\partial}{\partial x_j} (\tilde{u}_j - u_j)
+  + g_i
+  +\frac{1}{\rho} \frac{\partial \sigma_{ij}}{\partial x_j}.
+\end{equation}
+
+\begin{equation}
+  \label{eq:edac-p-evolve}
+  \frac{\tilde{d} p}{d t} =
+  (p -\rho c_s^2)
+    \text{div}(\ten{u})
+  - p \; \text{div}(\tilde{\ten{u}})
+    + \text{div}(p (\tilde{\ten{u}} - \ten{u}))
+    + \nu_{edac}  \nabla^2 p.
+\end{equation}
+%
+The value of $\nu_{edac}$ is,
+\begin{equation}
+  \label{eq:nu-edac}
+  \nu_{edac} = \frac{\alpha_{\textrm{edac}} h c_s}{8},
+\end{equation}
+
+\subsection{SPH discretization}
+
+In the current work, both fluid and solid modelling uses the same continuity
+and pressure evolution equation. The SPH discretization of the continuity
+equation~\eqref{eq:ce-tvf} and the pressure evolution
+equation~\eqref{eq:edac-p-evolve} respectively are,
 \begin{equation}
@@
 
-\begin{equation}
-  \label{eq:sph-momentum-solid}
+\begin{multline}
+  \label{eq:sph-discretization-edac}
+  \frac{\tilde{d}p_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; \bigg(
+  (p_{a} - \rho_{a} c_{s}^2) \; \ten{u}_{ab} \; + \;
+  p_{a} \; \tilde{\ten{u}}_{ab} \; - \;
+  (p \; (\tilde{\ten{u}} - \ten{u}))_{ab} \; + \; \\
+  4 \; \nu_{edac}
+  \frac{p_a - p_b}{(\rho_a + \rho_b) (r^2_{ab} + 0.01 h_{ab}^{2})} \ten{r}_{ab}
+  \bigg) \; \cdot \nabla_{a} W_{ab}.
+\end{multline}
+%
+Similarly, the discretized momentum equation for fluids is written as,
+\begin{multline}
+  \label{eq:sph-momentum-fluid}
   \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
   \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
-  \bigg(\frac{\teng{\sigma}^{'}_{a}}{\rho_a^2} +
-  \frac{\teng{\sigma}^{'}_{b}}{\rho_b^2} + \Pi_{ab} \ten{I} \bigg) \bigg]  \cdot \nabla_{a} W_{ab} +
+  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2} + \Pi_{ab}
+  \ten{I} \bigg) \bigg]
+  \cdot \nabla_{a} W_{ab} \\
+  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
+  \nabla_{a} W_{ab} + \sum_{b} m_b \frac{4 \eta \nabla W_{ab}\cdot
+    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab} +
   \ten{g}_{a},
-\end{equation}
-
-$\Pi_{ab}$ is the artificial
+\end{multline}
+where $\ten{A}_a = \rho_a \ten{u}_a \otimes (\ten{\tilde{u}}_a - \ten{u}_a)$,
+$\ten{I}$ is the identity matrix, $\eta$ is the kinematic viscosity of the
+fluid and \citet{morris1997modeling} formulation is used to discretize the
+viscosity term. $\Pi_{ab}$ is the artificial
 viscosity~\cite{monaghan-review:2005} to maintain the stability of the
@@
 
-The Jaumann's formulation for Hooke's stress provides us with the rate of
-change of deviatoric stress,
+%
+For solid mechanics the momentum equation is written as,
 \begin{equation}
-  \label{eq:jaumann-stress-rate}
-  \frac{d \sigma'_{ij}}{dt} = 2G (\dot{\epsilon}_{ij} - \frac{1}{3}
-  \dot{\epsilon}_{ij} \delta_{ij}) + \sigma^{'}_{ik}  \Omega_{jk} +
-  \Omega_{ik} \sigma^{'}_{kj}
+  \label{eq:sph-momentum-solid}
+  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
+  \bigg(\frac{\teng{\sigma}^{'}_{a}}{\rho_a^2} +
+  \frac{\teng{\sigma}^{'}_{b}}{\rho_b^2} + \Pi_{ab} \ten{I} \bigg) \bigg]  \cdot \nabla_{a} W_{ab} +
+  \ten{g}_{a},
 \end{equation}
-where $G$ is the shear modulus, $\dot{\epsilon}_{ij}$ is the strain rate tensor,
-\begin{equation}
-  \label{eq:strain-tensor}
-  \dot{\epsilon}_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} +
-  \frac{\partial u_j}{\partial x_i} \bigg)
-\end{equation}
-and $\Omega_{ij}$ is the rotational tensor,
-\begin{equation}
-  \label{eq:rotational-tensor}
-  \Omega_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} -
-  \frac{\partial u_j}{\partial x_i} \bigg)
-\end{equation}
+we have not considered the correction stress term $\ten{A}$ in momentum
+equation of solid mechanics as it has a negligible effect.
 
+In addition to these three equations, the Jaumann stress rate equation is also
+solved. In the current work we use the momentum velocity $\ten{u}$ rather than
+$\tilde{\ten{u}}$ as in the GTVF~\cite{zhang_hu_adams17} in the computation of
+gradient of velocity. The SPH discretization of the gradient of velocity is
+given as,
 \begin{equation}
@@
 \end{equation}
+where $\otimes$ is the outer product.
 
+The SPH discretization of the modified Jaumann stress rate
+\cref{eq:modified-jaumann-stress-rate} is given as,
+\begin{multline}
+  \label{eq:sph-modified-jaumann-stress}
+  \frac{\tilde{d}\teng{\sigma}^{'}_{a}}{dt} = 2G (\dot{\teng{\epsilon}}_{a} -
+  \frac{1}{3} \dot{\teng{\epsilon}}_{a} \ten{I}) + \teng{\sigma}^{'}_{a}
+  \teng{\Omega}_{a}^{T} +
+  \teng{\Omega}_{a} \teng{\sigma}^{'}_{a} + \\
+  + \sum_{b} \; \frac{m_b}{\rho_{b}} \; (\teng{\sigma}^{'} \otimes (\tilde{\ten{u}} -
+  \ten{u}))_{ab} \; \cdot \nabla_{a} W_{ab}
+  + \teng{\sigma}^{'}_{a} \sum_{b} \; \frac{m_b}{\rho_{b}} \;
+  (\tilde{\ten{u}} - \ten{u})_{ab} \; \cdot \nabla_{a} W_{ab}.
+\end{multline}
+
+\subsection{Transport velocity computation of the mediums}
+
+The particles in the current scheme are moved with the transport velocity,
 \begin{equation}
-  \label{eq:pressure-equation}
-  p = K \bigg(\frac{\rho}{\rho_{0}} - 1 \bigg),
+  \label{eq:transport_velocity_position_derivative}
+  \frac{d\ten{r}_a}{dt} = \ten{\tilde{u}}_a.
 \end{equation}
-where $K = \rho_{0} c_0^2$ is the bulk modulus. Here, the constants $c_0$ and
-$\rho_0$ are the reference speed of sound and density, respectively.
+%
+The transport velocity is updated using,
+\begin{equation}
+  \label{eq:transport_velocity}
+  \ten{\tilde{u}}_a(t + \Delta t) =\ten{u}_a(t) + \Delta t \; \frac{\tilde{d} \ten{u}_a}{dt} +
+  \bigg(\frac{d \ten{u}_{a}}{dt}\bigg)_{\text{c}} \Delta t
+\end{equation}
 
-\subsection{Boundary conditions}
+Where $\big(\frac{d \ten{u}_a}{dt}\big)_{\text{c}}$ is the homogenization
+acceleration which ensures that the particle positions are homogeneous. In the
+current work we have explored two kinds of homogenization accelerations, one
+is a displacement based technique due to \citet{sun2017deltaplus}, and the
+other is the iterative particle shifting technique due to
+\citet{huang_kernel_2019}. These are discussed in the following.
 
-\subsection{Time integration}
+\subsubsection{Transport velocity computation of fluid medium}
+\label{sec:fluid_pst}
+
+In \citet{sun2017deltaplus}, the particle shifting technique was implemented as
+a particle displacement ($\delta \ten{r}$). This was modified in
+\citet{sun_consistent_2019} to be computed as a change to the velocity. In the
+present work we modify this to be treated as an acceleration to the particle
+in order to unify the treatment of different PST methods.
+
+Firstly, the velocity deviation based equation is given as,
+\begin{equation}
+  \label{eq:sun2019_pst}
+  \delta \ten{u}_a = - \text{Ma} \; (2h) c_0 \sum_b \bigg[
+  1 + R \bigg( \frac{W_{ab}}{W(\Delta x)} \bigg)^n  \bigg] \nabla_a W_{ab} V_b,
+\end{equation}
+%
+it is modified to force based as,
+\begin{equation}
+  \label{eq:sun2019_pst}
+  \bigg(\frac{d \ten{u}_a}{dt}\bigg)_{\text{c}} = - \frac{\text{Ma} \;
+    (2h) c_0}{\Delta t} \sum_b \bigg[1 + R \bigg( \frac{W_{ab}}{W(\Delta x)} \bigg)^n
+  \bigg] \nabla_a W_{ab} V_b,
+\end{equation}
+where $R$ is an adjustment factor to handle the tensile instability, and
+$\text{Ma}$ is the mach number of the flow. $V_b$ is the volume of the
+$b$\textsuperscript{th} particle. The acceleration is changed to account for
+particles that are on the free surface. We use $R = 0.2$ and $n = 4$ as
+suggested by \citet{sun_consistent_2019}.
+
+\subsubsection{Transport velocity computation of solid medium}
+\label{sec:elastic_solid_pst}
+
+In \citet{sun2017deltaplus}, the particle shifting technique was implemented as
+a particle displacement ($\delta \ten{r}$). This was modified in
+\citet{sun_consistent_2019} to be computed as a change to the velocity. In the
+present work we modify this to be treated as an acceleration to the particle
+in order to unify the treatment of different PST methods.
+
+Firstly, the velocity deviation based equation is given as,
+\begin{equation}
+  \label{eq:sun2019_pst}
+  \delta \ten{u}_a = - \text{Ma} \; (2h) c_0 \sum_b \bigg[
+  1 + R \bigg( \frac{W_{ab}}{W(\Delta x)} \bigg)^n  \bigg] \nabla_a W_{ab} V_b,
+\end{equation}
+%
+it is modified to force based as,
+\begin{equation}
+  \label{eq:sun2019_pst}
+  \bigg(\frac{d \ten{u}_a}{dt}\bigg)_{\text{c}} = - \frac{\text{Ma} \;
+    (2h) c_0}{\Delta t} \sum_b \bigg[1 + R \bigg( \frac{W_{ab}}{W(\Delta x)} \bigg)^n
+  \bigg] \nabla_a W_{ab} V_b,
+\end{equation}
+where $R$ is an adjustment factor to handle the tensile instability, and
+$\text{Ma}$ is the mach number of the flow. $V_b$ is the volume of the
+$b$\textsuperscript{th} particle. The acceleration is changed to account for
+particles that are on the free surface. We use $R = 0.2$ and $n = 4$ as
+suggested by \citet{sun_consistent_2019}.
+
+\section{Fluid structure interaction}
 
@@
 
-\subsection{Total energy of the structure}
-\label{sec:total-energy-struct}
+% \subsection{Total energy of the structure}
+% \label{sec:total-energy-struct}
 
-\citet{khayyer2018enhanced} had an extra section where he discusses about the
-energy conservation properties of the proposed FSI scheme. He discusses
-different energies in structure, kinetic energy and strain energy.
+% \citet{khayyer2018enhanced} had an extra section where he discusses about the
+% energy conservation properties of the proposed FSI scheme. He discusses
+% different energies in structure, kinetic energy and strain energy.
+
+\section{Summary equations of the full model to be solved}
+
+\subsection{Summary equations fluid model}
+
+\begin{equation}
+  \label{eq:sph-discretization-continuity}
+  \frac{\tilde{d}\rho_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; (
+  \rho_{a} \; \tilde{\ten{u}}_{ab} \; + \;
+  (\rho \; (\tilde{\ten{u}} \; - \;
+  \ten{u}))_{ab}) \; \cdot \nabla_{a} W_{ab},
+\end{equation}
+
+\begin{multline}
+  \label{eq:sph-discretization-edac}
+  \frac{\tilde{d}p_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; \bigg(
+  (p_{a} - \rho_{a} c_{s}^2) \; \ten{u}_{ab} \; + \;
+  p_{a} \; \tilde{\ten{u}}_{ab} \; - \;
+  (p \; (\tilde{\ten{u}} - \ten{u}))_{ab} \; + \; \\
+  4 \; \nu_{edac}
+  \frac{p_a - p_b}{(\rho_a + \rho_b) (r^2_{ab} + 0.01 h_{ab}^{2})} \ten{r}_{ab}
+  \bigg) \; \cdot \nabla_{a} W_{ab}.
+\end{multline}
+%
+
+\begin{multline}
+  \label{eq:sph-momentum-fluid}
+  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
+  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2} + \Pi_{ab}
+  \ten{I} \bigg) \bigg]
+  \cdot \nabla_{a} W_{ab} \\
+  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
+  \nabla_{a} W_{ab} + \sum_{b} m_b \frac{4 \eta \nabla W_{ab}\cdot
+    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab} +
+  \ten{g}_{a},
+\end{multline}
+
+\begin{equation}
+  \label{eq:transport_velocity}
+  \ten{\tilde{u}}_a(t + \Delta t) =\ten{u}_a(t) + \Delta t \; \frac{\tilde{d} \ten{u}_a}{dt} +
+  \bigg(\frac{d \ten{u}_{a}}{dt}\bigg)_{\text{c}} \Delta t
+\end{equation}
+
+\begin{equation}
+  \label{eq:gtvf_pst}
+  \bigg(\frac{d \ten{u}_a}{dt}\bigg)_{\text{c}} = p_a^0 \;
+  \sum_b m_b \frac{1}{\rho_a^2} \nabla_a \widetilde{W}_{ab} ,
+\end{equation}
+
+\subsection{Summary equations solid model}
+
+\begin{equation}
+  \label{eq:sph-discretization-continuity}
+  \frac{\tilde{d}\rho_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; (
+  \rho_{a} \; \tilde{\ten{u}}_{ab} \; + \;
+  (\rho \; (\tilde{\ten{u}} \; - \;
+  \ten{u}))_{ab}) \; \cdot \nabla_{a} W_{ab},
+\end{equation}
+
+\begin{equation}
+  \label{eq:sph-momentum-solid}
+  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
+  \bigg(\frac{\teng{\sigma}^{'}_{a}}{\rho_a^2} +
+  \frac{\teng{\sigma}^{'}_{b}}{\rho_b^2} + \Pi_{ab} \ten{I} \bigg) \bigg]  \cdot \nabla_{a} W_{ab} +
+  \ten{g}_{a},
+\end{equation}
+
+\begin{equation}
+  \label{eq:sph-modified-jaumann-stress}
+  \frac{\tilde{d}\teng{\sigma}^{'}_{a}}{dt} = 2G (\dot{\teng{\epsilon}}_{a} -
+  \frac{1}{3} \dot{\teng{\epsilon}}_{a} \ten{I}) + \teng{\sigma}^{'}_{a}
+  \teng{\Omega}_{a}^{T} +
+  \teng{\Omega}_{a} \teng{\sigma}^{'}_{a}
+\end{equation}
+
+\begin{equation}
+  \label{eq:strain-tensor}
+  \dot{\epsilon}_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} +
+  \frac{\partial u_j}{\partial x_i} \bigg),
+\end{equation}
+and $\Omega_{ij}$ is the rotation tensor,
+\begin{equation}
+  \label{eq:rotational-tensor}
+  \Omega_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} -
+  \frac{\partial u_j}{\partial x_i} \bigg).
+\end{equation}
+
+\begin{equation}
+  \label{eq:sph-vel-grad}
+  \nabla \ten{u}_a =
+  - \sum_{b} \frac{m_b}{\rho_{b}} (\ten{u}_{a} - \ten{u}_{b}) \otimes (\nabla_{a} W_{ab}),
+\end{equation}
+
+\begin{equation}
+  \label{eq:transport_velocity}
+  \ten{\tilde{u}}_a(t + \Delta t) =\ten{u}_a(t) + \Delta t \; \frac{\tilde{d} \ten{u}_a}{dt} +
+  \bigg(\frac{d \ten{u}_{a}}{dt}\bigg)_{\text{c}} \Delta t
+\end{equation}
+
+\begin{equation}
+  \label{eq:sun2019_pst}
+  \bigg(\frac{d \ten{u}_a}{dt}\bigg)_{\text{c}} = - \frac{\text{Ma} \;
+    (2h) c_0}{\Delta t} \sum_b \bigg[1 + R \bigg( \frac{W_{ab}}{W(\Delta x)} \bigg)^n
+  \bigg] \nabla_a W_{ab} V_b,
+\end{equation}
 
@@
 structures, marine structures and ocean engineering papers.
-
-The papers we have followed for the benchmarks are
-\citet{sun2021accurate}, \citet{yang2016numerical}, \citet{Sun2019study},
-\citet{He2017coupled}, \citet{khayyer2018enhanced}, \citet{sun2015numerical},
-\citet{wang2020scale}, \citet{peng2021coupling}, \citet{zhang2021deltasph},
-\citet{zhan2019stabilized}, \citet{khayyer2021multi},
-\citet{long2021coupling}, \citet{ng2020coupled},
 
@@
 
-This has two simulations, one taken from \cite{ng2020coupled} and \cite{khayyer2021coupled}.
-\begin{table}[!ht]
-  \centering
-  \begin{tabular}[!ht]{ll}
-    % \toprule
-    Quantity & Values \\
-    % \midrule
-    $D$, Diameter & 2m \\
-    $\rho_0$, reference density & 1000kg/m\textsuperscript{3} \\
-    $c_s$ & 10m/s \\
-    $D/\Delta x_{\max}$, lowest resolution & 4 \\
-    $D/\Delta x_{\min} $, highest resolution & 160, 250, 500\\
-    $C_r$ & 1.08 \\
-    Reynolds number & 40, 550, 1000, 3000, and 9500 \\
-    Time of simulation & 6 \\
-    % \bottomrule
-  \end{tabular}
-  \caption{Parameters used for the flow past a circular cylinder problem.}%
-  \label{tab:fpc-params}
-\end{table}
-%
+In the first example, a hydrostatic water column on an elastic plate is
+considered. The initial setup of the system with water pressure is shown in
+figure, where an initial column of fluid under hydrostatic state is rested on an
+elastic plate under gravity. The water column is $2$ m in height and $0.5$ m in
+width, while the elastic plate is of $0.05$ m in thickness and $0.5$ m in
+length, respectively. The elastic plate considered here is made of Aluminium,
+whose material properties are: Young's modulus $E = 67.5$ GPa, Poisson's ratio
+$\nu = 0.4$. According to the analytical solution \cite{sfsfd}, the deflection
+magnitude at mid-span after the system's equilibrium state is
+$d = -6.85 \times 10^{-5}$ m.
+
 %
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{images/hydrostatic_water_column_on_an_elastic_plate/hydrostatic_water_column_on_an_elastic_plate}
-  \caption{Hydrostatic tank}
+  \includegraphics[width=0.4\textwidth]{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/good_vs_bad}
+  \caption{Hydrostatic water column on an elastic plate}
 \label{fig:hs-water-on-plate}
@@
 
-\todoin{Comment on the Poisson ratio range of the current scheme}
-\todoin{Who did it previously}
-\todoin{How to derive the analytical solution in short}
-\todoin{Write about the different resolutions}
-\todoin{Any other artificial parameters regarding the scheme, alpha, beta}
+The simulation is ran for a total time of 0.4 s. For convergence study, three
+different particle resolutions, respectively
+$h_e / delta_x = 10, h_e / delta_x = 10, h_e / delta_x = 10 $are adopted,
+whose respective total number of particles are 1122232 and 1122323. The time
+step of the fluid and solid phase are computed separately, but we use
+substepping to update the fluid and solid phases as per section
+\ref{section:substepping}.
 
-\todoin{In this problem we check the accuracy and stability-preserving property of the
-proposed scheme in handling the fluid structure interaction. This problem has
-been studied in Li et al. (2015), Fourey et al. (2017), Khayyer et
-al. (2018a), Hu et al. (2019), (2021), (2021) papers. This benchmark has an
-analytical solution derived in Li et al. (2015).}
-
-The first benchmark test to validate the fluid structure interaction model
-corresponds to an elastic plate under a hydrostatic water tank. An elastic
-plate of length 1m and width of 5cm is placed under a block of water column of
-height 2m is allowed to settle under gravity. The elastic plate is fixed on
-both the ends. The material properties of the water are as follows, the
-density is 1000 $kg/m^3$, viscosity of $1e-6$. And the material properties of
-the elastic plate are as follows, density 2700$kg/m^3$, Young's modulus
-$67.5 \times 10^7$ Pa and a Poisson ratio of 0.34. Three different particle
-spacing are considered. Initially the fluid is set up with a hydrostatic
-pressure distribution as in equation,
-%
-%
-\begin{equation}
-  f_a^F = -m_i \sum_{a} m_a \bigg(\frac{p_a}{\rho_{a}^2} +
-  \frac{p_i}{\rho_{i}^2} + \Pi_{ai} \bigg) \nabla_{a} W(x_{ai}).
-\end{equation}
-%
-%
-Once the plate reaches an equilibrium state, the
-deflection at the midpoint is compared with the analytical solution,
-%
-%
-\begin{equation}
-  f_a^F = -m_i \sum_{a} m_a \bigg(\frac{p_a}{\rho_{a}^2} +
-  \frac{p_i}{\rho_{i}^2} + \Pi_{ai} \bigg) \nabla_{a} W(x_{ai}).
-\end{equation}
-%
 %
@@
   \centering
-  \includegraphics[width=1\textwidth]{figures/khayyer_2021_hydrostatic_water_column_on_composite_elastic_plate/y_amplitude}
-  \caption{Hydrostatic tank}
-\label{fig:y-disp-hs-water-on-plate}
+  \includegraphics[width=0.4\textwidth]{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/good_vs_bad}
+  \caption{Hydrostatic water column on an elastic plate}
+\label{fig:hs-water-on-plate}
 \end{figure}
@@
 %
-\Cref{fig:y-disp-hs-water-on-plate} depicts the time histories of the plate's
-center point deflection with three different particle spacing. From the
-presented \Cref{fig:y-disp-hs-water-on-plate} and table \todoin{citetable} we
-can see as the particle spacing is reduced the numerical solution by the
-current model approaches the analytical model, which proves the convergence
-properties of the current scheme. \todoin{compare with other numerical schemes}
+
+% This has two simulations, one taken from \cite{ng2020coupled} and \cite{khayyer2021coupled}.
+% \begin{table}[!ht]
+%   \centering
+%   \begin{tabular}[!ht]{ll}
+%     % \toprule
+%     Quantity & Values \\
+%     % \midrule
+%     $D$, Diameter & 2m \\
+%     $\rho_0$, reference density & 1000kg/m\textsuperscript{3} \\
+%     $c_s$ & 10m/s \\
+%     $D/\Delta x_{\max}$, lowest resolution & 4 \\
+%     $D/\Delta x_{\min} $, highest resolution & 160, 250, 500\\
+%     $C_r$ & 1.08 \\
+%     Reynolds number & 40, 550, 1000, 3000, and 9500 \\
+%     Time of simulation & 6 \\
+%     % \bottomrule
+%   \end{tabular}
+%   \caption{Parameters used for the flow past a circular cylinder problem.}%
+%   \label{tab:fpc-params}
+% \end{table}
+% %
 %
-%
-%
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=1\textwidth]{figures/khayyer_2021_hydrostatic_water_column_on_composite_elastic_plate/y_amplitude}
-  \caption{Hydrostatic tank}
-\label{fig:p-hs-tank-elastic-plate}
-\end{figure}
-%
-%
-%
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=1\textwidth]{figures/khayyer_2021_hydrostatic_water_column_on_composite_elastic_plate/y_amplitude}
-  \caption{Hydrostatic tank}
-\label{fig:sigma-hs-tank-elastic-plate}
-\end{figure}
-
-\Cref{fig:p-hs-tank-elastic-plate} shows the pressure distribution in the
-fluid domain at different time histories. \Cref{fig:sigma-hs-water-on-plate}
-shows the plots of $\sigma_{00}$ distribution of the elastic plate at
-different time steps.
 
@@
 %%% mode: latex
-%%% TeX-master: "paper"
-%%% fill-column: 78
+%%% TeX-master: t
 %%% End:

### 2021-12-14 automate.py

@@ -2,6 +2,9 @@
 import os
 import matplotlib.pyplot as plt
 
+# https://stackoverflow.com/questions/22408237/named-colors-in-matplotlib
+from matplotlib import colors as mcolors
+
 from itertools import product
 import json
 from automan.api import PySPHProblem as Problem
@@ -12,7 +15,31 @@ import numpy as np
 import matplotlib
 from pysph.solver.utils import load, get_files
 
-matplotlib.use('pdf')
+matplotlib.use('agg')
+from cycler import cycler
+from matplotlib import rc, patches, colors
+from matplotlib.collections import PatchCollection
+
+rc('font', **{'family': 'Helvetica', 'size': 12})
+rc('legend', fontsize='xx-small')
+rc('axes', grid=True, linewidth=1.2)
+rc('axes.grid', which='both', axis='both')
+# rc('axes.formatter', limits=(1, 2), use_mathtext=True, min_exponent=1)
+rc('grid', linewidth=0.5, linestyle='--')
+rc('xtick', direction='in', top=True)
+rc('ytick', direction='in', right=True)
+rc('savefig', format='pdf', bbox='tight', pad_inches=0.05,
+   transparent=False, dpi=300)
+rc('lines', linewidth=1.5)
+rc('axes', prop_cycle=(
+    cycler('color', ['tab:blue', 'tab:green', 'tab:red',
+                     'tab:orange', 'm', 'tab:purple',
+                     'tab:pink', 'tab:gray']) +
+    cycler('linestyle', ['-.', '--', '-', ':',
+                         (0, (3, 1, 1, 1)), (0, (3, 1, 1, 1, 1, 1)),
+                         (0, (3, 2, 1, 1)), (0, (3, 2, 2, 1, 1, 1)),
+                         ])
+))
 
 # n_core = free_cores()
 # n_thread = 2 * free_cores()
@@ -365,12 +392,6 @@ class Ng2020HydrostaticWaterColumnOnElasticPlate(Problem):
                 tf=3.,
                 d0=1e-2 * 0.25,
                 ), 'N=20'),
-            # 'rogers': (dict(
-            #     scheme='ctvf',
-            #     pfreq=500,
-            #     tf=1.,
-            #     rogers_eqns=None
-            #     ), 'Rogers Scheme'),
         }
 
         self.cases = [
@@ -383,9 +404,31 @@ class Ng2020HydrostaticWaterColumnOnElasticPlate(Problem):
 
     def run(self):
[…]

### 2021-12-14 code/fluids.py

@@ -1,7 +1,5 @@
 """
-Run it by
-
-python lid_driven_cavity.py --openmp --scheme etvf --integrator pec --internal-flow --pst sun2019 --re 100 --tf 25 --nx 50 --no-edac -d lid_driven_cavity_scheme_etvf_integrator_pec_pst_sun2019_re_100_nx_50_no_edac_output --detailed-output --pfreq 100
+Pertains to etvf fluids
 
 """
 import numpy
@@ -231,149 +229,6 @@ class FluidContinuityEquationETVFCorrectionSolid(Equation):
         vijdotdwij = (DWIJ[0] * tmp0 + DWIJ[1] * tmp1 + DWIJ[2] * tmp2)
 
         d_arho[d_idx] += s_m[s_idx] / s_rho[s_idx] * vijdotdwij
-
-
-class FluidEDACEquationWCSPH(Equation):
-    def __init__(self, dest, sources, nu):
-        self.nu = nu
-        super(FluidEDACEquationWCSPH, self).__init__(dest, sources)
-
-    def initialize(self, d_ap, d_idx):
-        d_ap[d_idx] = 0.0
-
-    def loop(self, d_idx, s_idx, d_p, d_rho, d_cs, d_u, d_v, d_w, d_uhat,
-             d_vhat, d_what, s_p, s_m, s_rho, d_ap, DWIJ, XIJ, s_uhat, s_vhat,
-             s_what, s_u, s_v, s_w, R2IJ, VIJ, EPS):
-        vhatij = declare('matrix(3)')
-        vhatij[0] = d_uhat[d_idx] - s_uhat[s_idx]
-        vhatij[1] = d_vhat[d_idx] - s_vhat[s_idx]
-        vhatij[2] = d_what[d_idx] - s_what[s_idx]
-
-        cs2 = d_cs[d_idx] * d_cs[d_idx]
-
-        rhoj1 = 1.0 / s_rho[s_idx]
-        Vj = s_m[s_idx] * rhoj1
-        rhoi = d_rho[d_idx]
-        pi = d_p[d_idx]
-        rhoj = s_rho[s_idx]
-        pj = s_p[s_idx]
-
-        vij_dot_dwij = -(VIJ[0] * DWIJ[0] + VIJ[1] * DWIJ[1] +
-                         VIJ[2] * DWIJ[2])
-
[…]

### 2021-12-14 code/fsi_wcsph.py

@@ -607,7 +607,7 @@ class FSIWCSPHFluidsScheme(Scheme):
 
         # common properties
         self.solver = None
-        self.kernel_factor = 2
+        self.kernel_factor = 3
 
         self.attributes_changed()
 

### 2021-12-14 code/ng_2020_elastic_dam_break.py

@@ -317,7 +317,7 @@ class ElasticGate(Application):
         gate_support.rho_fsi[:] = self.fluid_density
 
         # set the pressure of the fluid
-        fluid.p[:] = - self.fluid_density * self.gy * (max(fluid.y) - fluid.y[:])
+        # fluid.p[:] = - self.fluid_density * self.gy * (max(fluid.y) - fluid.y[:])
 
         gate.add_output_arrays(['tip_displacemet_index'])
 
@@ -404,7 +404,7 @@ class ElasticGate(Application):
             mach_no_fluid=self.mach_no_fluid,
             mach_no_structure=self.mach_no_gate,
             gy=self.gy,
-            alpha_fluid=0.1,
+            alpha_fluid=0.05,
             alpha_solid=1.,
             beta_solid=0,
             dt_fluid=self.dt_fluid,

### 2021-12-14 code/sun_2019_dam_breaking_flow_impacting_an_elastic_plate.py

@@ -233,7 +233,7 @@ class Sun2019DamBreakingFLowImpactingAnElasticPlate(Application):
         self.gate_nu = 0.0
         self.c0_gate = get_speed_of_sound(self.gate_E, self.gate_nu,
                                           self.gate_rho0)
-        self.u_max_gate = self.u_max_fluid
+        self.u_max_gate = 20.
         self.mach_no_gate = self.u_max_gate / self.c0_gate
         self.alpha_solid = 1.
         self.beta_solid = 0.
@@ -256,11 +256,11 @@ class Sun2019DamBreakingFLowImpactingAnElasticPlate(Application):
         # Create fluid
         # ===================================
         xf, yf = get_2d_block(dx=self.fluid_spacing, length=self.fluid_length,
-                              height=self.fluid_length)
+                              height=self.fluid_height)
 
         xt, yt = create_tank_2d_from_block_2d(
-            xf, yf, self.tank_length, self.tank_height, self.tank_spacing,
-            self.tank_layers)
+            xf, yf, self.tank_length - abs(min(xf)) - 0.006, self.tank_height,
+            self.tank_spacing, self.tank_layers)
 
         m_fluid = self.fluid_density * self.fluid_spacing**2.
 
@@ -345,6 +345,8 @@ class Sun2019DamBreakingFLowImpactingAnElasticPlate(Application):
         # ===========================
         # Adjust the geometry
         # ===========================
+        gate_support.x[:] += self.fluid_spacing/2.
+        gate.x[:] += self.fluid_spacing/2.
         remove_overlap_particles(tank, gate_support, self.fluid_spacing/2.)
 
         self.scheme.setup_properties([fluid, tank,

### 2021-12-14 code/zhang_2021_high_speed_water_entry_of_an_elastic_wedge.py

@@ -187,7 +187,8 @@ class WaterEntryOfElasticWedge(Application):
         # properties related to the elastic wedge
         # ================================================
         # elastic wedge is made of rubber
-        self.wedge_size = 0.60925
+        # self.wedge_size = 0.60925
+        self.wedge_size = 0.60
         self.wedge_width = 0.04
         self.wedge_spacing = self.fluid_spacing
         self.wedge_rho0 = 2700
@@ -195,9 +196,10 @@ class WaterEntryOfElasticWedge(Application):
         self.wedge_nu = 0.34
         self.c0_wedge = get_speed_of_sound(self.wedge_E, self.wedge_nu,
                                            self.wedge_rho0)
+        # print(self.c0_wedge)
         # self.c0 = 5960
-        # print("speed of sound is")
-        # print(self.c0)
+        print("speed of sound is")
+        print(self.c0_wedge)
         self.pb_wedge = self.wedge_rho0 * self.c0_wedge**2
 
         self.edac_alpha = 0.5
@@ -206,7 +208,7 @@ class WaterEntryOfElasticWedge(Application):
 
         # attributes for Sun PST technique
         # dummy value, will be updated in consume user options
-        self.u_max_wedge = 1.
+        self.u_max_wedge = 30.
         self.mach_no_wedge = self.u_max_wedge / self.c0_wedge
 
         # for pre step
@@ -327,7 +329,7 @@ class WaterEntryOfElasticWedge(Application):
                                  'A_index',
                                  'B_index',
                                  'C_index'])
-        wedge.add_output_arrays(['is_boundary'])
+        wedge.add_output_arrays(['is_boundary', 'p_fsi'])
         return [fluid, tank, wedge]
 
     def create_scheme(self):
@@ -466,20 +468,34 @@ class WaterEntryOfElasticWedge(Application):
         arrays = data['arrays']
         pa = arrays['wedge']
         # Displacement of the middle of the wedge (Index B)
-        index = np.where(pa.B_index == 1)[0][0]
-        y_0 = pa.y[index]
+        index_B = np.where(pa.B_index == 1)[0][0]
+        y_0 = pa.y[index_B]
+
+        # for pressure computation
+        index_C = np.where(pa.C_index == 1)[0][0]
[…]

### 2021-12-23 manuscript/paper.tex
Improved elastic wedge entry

@@
 
-%
-%
 \begin{figure}[!htpb]
   \centering
-  \includegraphics[width=0.4\textwidth]{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/good_vs_bad}
+  \includegraphics[width=0.4\textwidth]{{{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/schematic_t_0.0}}}
   \caption{Hydrostatic water column on an elastic plate}
@@
 \end{figure}
-%
+
 %
@@
 The simulation is ran for a total time of 0.4 s. For convergence study, three
-different particle resolutions, respectively
-$h_e / delta_x = 10, h_e / delta_x = 10, h_e / delta_x = 10 $are adopted,
-whose respective total number of particles are 1122232 and 1122323. The time
-step of the fluid and solid phase are computed separately, but we use
+different particle resolutions, respectively $d0 = 0.55 \times 10^{-2}$ m,
+$0.35 \times 10^{-2}$ m, $0.25 \times 10^{-2}$ m, are adopted, which generates
+10, 20 and 30 particles in along the width direction on the structure
+respectively. The test case is ran for a period of 0.3 seconds with 1232233
+particles for the highest resolution. The time step of the fluid and solid phase
+are computed separately as per equation \eqref{eq:time_step}, but we use
 substepping to update the fluid and solid phases as per section
@@
 %
+\begin{figure}[!htpb]
+  \centering
+%
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=0.7\textwidth]{{{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/snap_t_0.3}}}
+  \end{subfigure}
+%
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=0.3\textwidth]{{{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/colorbar_t_0.0}}}
+  \end{subfigure}
+  \caption{Pressure and stress distribution in an hydrostatic tank example}
+\label{fig:ng2020hsplate:t_0.3}
+\end{figure}
+%
+
 %
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/good_vs_bad}
-  \caption{Hydrostatic water column on an elastic plate}
-\label{fig:hs-water-on-plate}
+%
+  \begin{subfigure}{0.8\textwidth}
+    \centering
+    \includegraphics[width=1\textwidth]{{{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/y_amplitude}}}
+  \end{subfigure}
+  \caption{The mid-span deflection of the structure with time}
+\label{fig:ng2020hsplate:deflection}
 \end{figure}
 %
+
+\FloatBarrier%
+
+% %
+%   \begin{subfigure}{0.24\textwidth}
+%     \centering
+%     \includegraphics[width=0.7\textwidth]{{{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/snap_t_0.2}}}
+%     \subcaption{t = 4e-03 sec}\label{fig:rings:sun2019-nu-0.3975-2}
+%   \end{subfigure}
+% %
+%   \begin{subfigure}{0.24\textwidth}
+%     \centering
+%     \includegraphics[width=0.7\textwidth]{{{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/snap_t_0.2}}}
+%     \subcaption{t = 7.3e-03 sec}\label{fig:rings:sun2019-nu-0.3975-3}
+%   \end{subfigure}
+% %
+%   \begin{subfigure}{0.24\textwidth}
+%     \centering
+%     \includegraphics[width=0.7\textwidth]{{{figures/ng_2020_hydrostatic_water_column_on_elastic_plate/colorbar_t_0.0}}}
+%     % \subcaption{t = 1.45e-02 sec}\label{fig:rings:sun2019-nu-0.3975-4}
+%   \end{subfigure}
+% % %
+% %   \begin{subfigure}{0.3\textwidth}
+% %     \centering
+% %     \includegraphics[width=1.0\textwidth]{figures/rings/etvf_sun2019_poisson_ratio_0.3975/time5}
+% %     \subcaption{t = 1.5e-02 sec}\label{fig:rings:sun2019-nu-0.3975-5}
+% %   \end{subfigure}
+
+\subsection{Water impact onto a forefront elastic plate}
+\label{sec:water-impact-forefront}
+
+In this example the elastic plate is placed at the end. Which gets impacted
+due to the moving fluid. Further information can be found at section 3.2 of
+\cite{liu2013numerical}, \citet{sun2019fully}, {A $\delta$ SPH-SPIM coupled
+  method for fluid-structure interaction problems}.
+
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.8\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/schematic_t_0.0}}}
+  \caption{Dam breaking on to an elastic obstacle}
+\label{fig:dambreak-onto-a-plate}
+\end{figure}
+
 %
 
-% This has two simulations, one taken from \cite{ng2020coupled} and \cite{khayyer2021coupled}.
-% \begin{table}[!ht]
-%   \centering
-%   \begin{tabular}[!ht]{ll}
-%     % \toprule
-%     Quantity & Values \\
-%     % \midrule
-%     $D$, Diameter & 2m \\
-%     $\rho_0$, reference density & 1000kg/m\textsuperscript{3} \\
-%     $c_s$ & 10m/s \\
-%     $D/\Delta x_{\max}$, lowest resolution & 4 \\
-%     $D/\Delta x_{\min} $, highest resolution & 160, 250, 500\\
-%     $C_r$ & 1.08 \\
-%     Reynolds number & 40, 550, 1000, 3000, and 9500 \\
-%     Time of simulation & 6 \\
-%     % \bottomrule
-%   \end{tabular}
-%   \caption{Parameters used for the flow past a circular cylinder problem.}%
-%   \label{tab:fpc-params}
-% \end{table}
-% %
+\begin{figure}[!htpb]
+  \centering
+%
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/snap_t_0.0}}}
+  \end{subfigure}
+%
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/snap_t_0.2}}}
+  \end{subfigure}
+
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/snap_t_0.4}}}
+  \end{subfigure}
+%
+  \begin{subfigure}{0.49\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/snap_t_0.5}}}
+  \end{subfigure}
+
+  \begin{subfigure}{0.4\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/snap_t_0.6}}}
+  \end{subfigure}
+%
+  \begin{subfigure}{0.4\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/snap_t_0.7}}}
+  \end{subfigure}
+%
+  \begin{subfigure}{0.09\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/colorbar_t_0.0}}}
+  \end{subfigure}
+
+  \caption{Pressure and stress distribution in dam breaking onto a elastic
+    obstacle case}
+  \label{fig:sun2019dambreakobstable}
+\end{figure}
 %
 
+\begin{figure}[!htpb]
+  \centering
+%
+  \begin{subfigure}{0.8\textwidth}
+    \centering
+    \includegraphics[width=1\textwidth]{{{figures/sun_2019_dam_breaking_flow_impacting_an_elastic_plate/x_amplitude}}}
+  \end{subfigure}
+  \caption{The mid-span deflection of the structure with time}
+\label{fig:ng2020hsplate:deflection}
+\end{figure}
+%
 \FloatBarrier%
@@
 experimental results.
-
-\subsection{Water impact onto a forefront elastic plate}
-\label{sec:water-impact-forefront}
-
-In this example the elastic plate is placed at the end. Which gets impacted
-due to the moving fluid. Further information can be found at section 3.2 of
-\cite{liu2013numerical}, \citet{sun2019fully}, {A $\delta$ SPH-SPIM coupled
-  method for fluid-structure interaction problems}.
 
@@
 
+% This has two simulations, one taken from \cite{ng2020coupled} and \cite{khayyer2021coupled}.
+% \begin{table}[!ht]
+%   \centering
+%   \begin{tabular}[!ht]{ll}
+%     % \toprule
+%     Quantity & Values \\
+%     % \midrule
+%     $D$, Diameter & 2m \\
+%     $\rho_0$, reference density & 1000kg/m\textsuperscript{3} \\
+%     $c_s$ & 10m/s \\
+%     $D/\Delta x_{\max}$, lowest resolution & 4 \\
+%     $D/\Delta x_{\min} $, highest resolution & 160, 250, 500\\
+%     $C_r$ & 1.08 \\
+%     Reynolds number & 40, 550, 1000, 3000, and 9500 \\
+%     Time of simulation & 6 \\
+%     % \bottomrule
+%   \end{tabular}
+%   \caption{Parameters used for the flow past a circular cylinder problem.}%
+%   \label{tab:fpc-params}
+% \end{table}
+% %
+%
+
 \end{document}

### 2021-12-23 automate.py

@@ -245,6 +245,7 @@ class DamBreak2D(Problem):
         # Base case info
         self.case_info = {
             'wcsph': (dict(
+                scheme='wcsph',
                 pst='sun2019',
                 no_edac=None,
                 no_cont_vc_bc=None,
@@ -255,6 +256,7 @@ class DamBreak2D(Problem):
             ), 'WCSPH'),
 
             'wcsph_1': (dict(
+                scheme='wcsph',
                 pst='sun2019',
                 edac=None,
                 no_cont_vc_bc=None,
@@ -265,6 +267,19 @@ class DamBreak2D(Problem):
             ), 'WCSPH'),
 
             'wcsph_2': (dict(
+                scheme='wcsph',
+                pst='sun2019',
+                edac=None,
+                no_clamp_p=None,
+                cont_vc_bc=None,
+                dx=0.05,
+                tf=1.,
+                pfreq=200,
+                alpha=0.05
+            ), 'WCSPH'),
+
+            'etvf': (dict(
+                scheme='etvf',
                 pst='sun2019',
                 edac=None,
                 no_clamp_p=None,
@@ -411,21 +426,27 @@ class Ng2020HydrostaticWaterColumnOnElasticPlate(Problem):
         self.plot_prop(conditions=conditions, size=0.1,
                        show_fluid=True, fmin=0, fmax=18000, show_structure=True,
                        smin=-3*1e6, smax=3*1e6, fcmap='rainbow', show_fcmap=False,
-                       scmap='Greens', show_fsmap=False, times=[0],
-                       fname_prefix="schematic")
+                       scmap='winter', show_fsmap=False, times=[0],
+                       fname_prefix="schematic", only_colorbar=False)
+
+        self.plot_prop(conditions=conditions, size=0.1,
+                       show_fluid=True, fmin=0, fmax=18000, show_structure=False,
+                       smin=-3*1e6, smax=3*1e6, fcmap='rainbow', show_fcmap=True,
+                       scmap='winter', show_fsmap=False, times=[0],
+                       fname_prefix="colorbar", only_colorbar=True)
 
         # snapshots at different timesteps
         self.plot_prop(conditions=conditions, size=0.2,
                        show_fluid=True, fmin=0, fmax=18000, show_structure=True,
                        smin=-3*1e6, smax=3*1e6, fcmap='rainbow', show_fcmap=False,
[…]

### 2021-12-23 code/fsi_coupling.py

@@ -7,6 +7,7 @@ python lid_driven_cavity.py --openmp --scheme etvf --integrator pec --internal-f
 import numpy
 import numpy as np
 
+from pysph.sph.integrator import Integrator
 from pysph.sph.equation import Equation, Group, MultiStageEquations
 from pysph.sph.integrator_step import IntegratorStep
 from pysph.sph.scheme import Scheme
@@ -15,567 +16,12 @@ from pysph.tools.sph_evaluator import SPHEvaluator
 from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline,
                                 WendlandQuinticC4, Gaussian, SuperGaussian)
 
-from pysph.sph.wc.edac import (SolidWallPressureBC)
-from pysph.sph.wc.edac import ClampWallPressure
-
-from pysph.sph.integrator import PECIntegrator
 from boundary_particles import (add_boundary_identification_properties)
 
 from boundary_particles import (ComputeNormals, SmoothNormals,
                                 IdentifyBoundaryParticleCosAngleEDAC)
 
-from common import EDACIntegrator
 from pysph.examples.solid_mech.impact import add_properties
-from pysph.sph.wc.linalg import mat_vec_mult
-from pysph.sph.basic_equations import (MonaghanArtificialViscosity,
-                                       VelocityGradient3D, VelocityGradient2D)
-from pysph.sph.solid_mech.basic import (IsothermalEOS,
-                                        HookesDeviatoricStressRate)
-from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
-                                        get_shear_modulus)
-
-from pysph.sph.wc.transport_velocity import (MomentumEquationArtificialViscosity)
-from pysph.sph.integrator import Integrator
-
-from pysph.sph.wc.basic import TaitEOS
-
-
-class SetMassFracRhoFracPressureFrac(Equation):
-    """
-    This equation is applied to structure and structure solids
-    """
-    def initialize(self, d_m_frac, d_rho_frac, d_p_frac, d_m, d_m_fsi, d_rho,
[…]

### 2021-12-23 code/fsi_wcsph.py

@@ -655,7 +655,8 @@ class FSIWCSPHFluidsScheme(Scheme):
 
     def consume_user_options(self, options):
         vars = ['alpha_fluid', 'alpha_solid', 'beta_solid',
-                'edac_alpha', 'wall_pst', 'damping', 'damping_coeff']
+                'edac_alpha', 'wall_pst', 'damping', 'damping_coeff',
+                'solid_velocity_bc']
         data = dict((var, self._smart_getattr(options, var)) for var in vars)
         self.configure(**data)
 
@@ -728,11 +729,12 @@ class FSIWCSPHFluidsScheme(Scheme):
             ElasticSolidContinuityEquationUhat,
             ElasticSolidContinuityEquationETVFCorrection,
             VelocityGradient2D,
+            VelocityGradient2DUhat,
 
             ElasticSolidContinuityEquationUhatSolid,
             ElasticSolidContinuityEquationETVFCorrectionSolid,
             VelocityGradient2DSolid,
-
+            VelocityGradient2DSolidUhat,
             HookesDeviatoricStressRate,
 
             SetHIJForInsideParticles,
@@ -820,6 +822,7 @@ class FSIWCSPHFluidsScheme(Scheme):
                 g1.append(
                     ElasticSolidContinuityEquationETVFCorrection(
                         dest=structure, sources=self.structures))
+
                 g1.append(
                     VelocityGradient2D(
                         dest=structure, sources=self.structures))
@@ -834,7 +837,8 @@ class FSIWCSPHFluidsScheme(Scheme):
                             dest=structure, sources=self.structure_solids))
 
                     g1.append(
-                        VelocityGradient2DSolid(dest=structure, sources=self.structure_solids))
+                        VelocityGradient2DSolid(dest=structure,
+                                                sources=self.structure_solids))
 
             stage1.append(Group(equations=g1))
 

### 2021-12-23 code/solid_mech.py

@@ -41,6 +41,29 @@ from math import sqrt, acos
 from math import pi as M_PI
 
 
+class VelocityGradient2DUhat(Equation):
+    def initialize(self, d_idx, d_v00, d_v01, d_v10, d_v11):
+        d_v00[d_idx] = 0.0
+        d_v01[d_idx] = 0.0
+        d_v10[d_idx] = 0.0
+        d_v11[d_idx] = 0.0
+
+    def loop(self, d_uhat, d_vhat, d_what, d_idx, s_idx, s_m, s_rho, d_v00,
+             d_v01, d_v10, d_v11, s_uhat, s_vhat, s_what, DWIJ):
+        vij = declare('matrix(3)')
+        vij[0] = d_uhat[d_idx] - s_uhat[s_idx]
+        vij[1] = d_vhat[d_idx] - s_vhat[s_idx]
+        vij[2] = d_what[d_idx] - s_what[s_idx]
+
+        tmp = s_m[s_idx] / s_rho[s_idx]
+
+        d_v00[d_idx] += tmp * -vij[0] * DWIJ[0]
+        d_v01[d_idx] += tmp * -vij[0] * DWIJ[1]
+
+        d_v10[d_idx] += tmp * -vij[1] * DWIJ[0]
+        d_v11[d_idx] += tmp * -vij[1] * DWIJ[1]
+
+
 # ===========================
 # Equations for ULSPH by Gray
 # ===========================
@@ -646,18 +669,29 @@ class ElasticSolidContinuityEquationETVFCorrectionSolid(Equation):
 
 
 class VelocityGradient2DSolid(Equation):
-    def initialize(self, d_idx, d_v00, d_v01, d_v10, d_v11):
-        d_v00[d_idx] = 0.0
-        d_v01[d_idx] = 0.0
-        d_v10[d_idx] = 0.0
-        d_v11[d_idx] = 0.0
-
     def loop(self, d_idx, s_idx, s_m, s_rho, d_v00, d_v01, d_v10, d_v11, d_u,
              d_v, d_w, s_ub, s_vb, s_wb, DWIJ):
         vij = declare('matrix(3)')
         vij[0] = d_u[d_idx] - s_ub[s_idx]
         vij[1] = d_v[d_idx] - s_vb[s_idx]
         vij[2] = d_w[d_idx] - s_wb[s_idx]
+
[…]

### 2021-12-23 code/sun_2019_dam_breaking_flow_impacting_an_elastic_plate.py

@@ -28,6 +28,7 @@ https://ars.els-cdn.com/content/image/1-s2.0-S0889974618308673-gr7_lrg.jpg
 
 """
 
+
 import numpy as np
 
 from pysph.base.kernels import CubicSpline
@@ -233,7 +234,11 @@ class Sun2019DamBreakingFLowImpactingAnElasticPlate(Application):
         self.gate_nu = 0.0
         self.c0_gate = get_speed_of_sound(self.gate_E, self.gate_nu,
                                           self.gate_rho0)
-        self.u_max_gate = 20.
+        if self.options.d0 == 1e-3:
+            self.u_max_gate = 20.
+        elif self.options.d0 == 5e-4:
+            self.u_max_gate = 40.
+
         self.mach_no_gate = self.u_max_gate / self.c0_gate
         self.alpha_solid = 1.
         self.beta_solid = 0.
@@ -419,7 +424,9 @@ class Sun2019DamBreakingFLowImpactingAnElasticPlate(Application):
         dt = self.dt_fluid
         tf = 1.
 
-        self.scheme.configure_solver(dt=dt, tf=tf, pfreq=2000)
+        times = [0.0, 0.2, 0.4, 0.5, 0.6, 0.7]
+        self.scheme.configure_solver(dt=dt, tf=tf, pfreq=2000,
+                                     output_at_times=times)
 
         self.scheme.configure(
             dim=2,

### 2021-12-23 code/zhang_2021_high_speed_water_entry_of_an_elastic_wedge.py

@@ -14,6 +14,14 @@ An enhanced ISPH-SPH coupled method for simulation of incompressible
 fluid-elastic structure interactions
 
 https://doi.org/10.1016/j.cpc.2018.05.012
+
+# Wedge geometry description
+A non-intrusive partitioned approach to couple smoothed particle hydrodynamics
+and finite element methods for transient fluid-structure interaction problems
+with large interface motion
+
+https://doi.org/10.1007/s00466-015-1131-8
+
 """
 
 import numpy as np
@@ -55,8 +63,27 @@ def find_displacement_index(pa):
     pa.A_index[index] = 1
 
 
-def get_hydrostatic_tank_with_fluid(fluid_length=1., fluid_height=2., tank_height=2.3,
-                                    tank_layers=2, fluid_spacing=0.1):
+def find_velocity_indices(pa):
+    min_x = min(pa.x)
+    max_x = max(pa.x)
+    pa.add_property('velocity_indices', type='int',
+                    data=np.zeros(len(pa.x)))
+
+    index = (pa.x == min_x)
+    pa.velocity_indices[index] = 1
+
+    index = (pa.x == max_x)
+    pa.velocity_indices[index] = 1
+
+    min_y = min(pa.y)
+    x_min_y = pa.x[pa.y == min_y]
+    index = pa.x == x_min_y
+    pa.velocity_indices[index] = 1
+
+
+def get_hydrostatic_tank_with_fluid(fluid_length=1., fluid_height=2.,
+                                    tank_height=2.3, tank_layers=2,
+                                    fluid_spacing=0.1):
     import matplotlib.pyplot as plt
 
     xf, yf = get_2d_block(dx=fluid_spacing,
@@ -126,7 +153,7 @@ def get_wedge(wedge_size, wedge_width, slope, spacing):
 class WaterEntryOfElasticWedge(Application):
     def add_user_options(self, group):
         group.add_argument("--d0", action="store", type=float, dest="d0",
-                           default=5e-3,
+                           default=5 * 1e-3,
                            help="Spacing between the particles")
 
     def consume_user_options(self):
@@ -294,7 +321,7 @@ class WaterEntryOfElasticWedge(Application):
         # ===================================
         xp += self.fluid_length
         wedge = get_particle_array(
-            x=xp, y=yp, v=-30, m=m, h=self.h_fluid, rho=self.wedge_rho0,
+            x=xp, y=yp, m=m, h=self.h_fluid, rho=self.wedge_rho0,
[…]

### 2022-12-08 manuscript/paper.tex
Add 3 cases for hs tank

@@
 \begin{abstract}
+In the current work we have proposed a single
+unified meshless particle based numerical scheme to model fluid structure
+interaction problems. A corrected transport velocity formulation is utilised to
+model both fluid and solid phases. Both the phases follow the same set of
+governing equations. The corrected transport velocity formulation has proved
+that it has better approximation in fluids due to the corrected terms as well
+the particle distribution. We also take the advantage of the ctvf scheme in
+eliminating the tensile instability of the structures. The coupling is
+seamlessly done as both the phases are simulated in one configuration and no
+reference frame or initial frame is used to model the dynamics of any phase.
+Three numerical problems are simulated to show the current scheme validation. A
+clamped beam acted upon by a uniformly distributed load, hydrostatic tank on an
+elastic plate, and dam breaking flow hitting a plate.
 \end{abstract}
@@
 %% keywords here, in the form: keyword \sep keyword
-{XXX}, {XXX}, {XXX}
+{Smoothed particle hydrodynamics}, {Fluid-structure interaction}, {Transport velocity formulation}
 
@@
 
+\begin{itemize}
+\item Fluid structure interaction in real life. Refer to papers where they deal
+  with FSI problems, this includes FEM coupling, MPS coupling and many other
+  paper, or may be looking at one review paper and select 5 paper to write about this.
+\item In many different ways FSI is modeled, this includes mesh based and mesh
+  less. Explain in a good detail what meshless methods are out there which
+  handles these problems. This includes SPH too.
+\item Explain different ways SPH is applied in FSI area. Detail some papers
+  where how differently fluid as well as structures is modelled. This includes
+  ISPH, WCSPH, TVF, delta+ SPH and for structures TLSPH, ULSPH, some other DEM
+  methods. Also mention the latest multiphase flow, where air is considered,
+  then mention the adaptive formulation, where the author captures the cavity.
+  And what different coupling approaches are handled so far.
+\item Mention the open source software which provide SPH formulation (This is
+  optional for now).
+\item Explain what we are going to do in the current work. We couple the
+  transport velocity formulation approach extended to free surface to model
+  both the phases.
+\item Explain the examples.
+\end{itemize}
+
 Xu has introduced the particle shifting and adjusted the particles and applied
@@
 surface problems as well as elastic solid problems.
+
+FSI is a common engineering problem that is seen in daily life. Few examples
+include the deformation of the wind turbine blade due to the fluid flow, the
+flow traversal due to the deflected blade, blood flow in heart value, coastal
+engineering, and vortex-induced vibration
+\cite{williamson2004vortex,bearman2011circular}. An accurate study FSI
+phenomena can allow us to understand systems where FSI is prevalent. However,
+studying the FSI phenomena through experiments or analytical techniques is
+complex. The complexity arises due to the nonlinear behavior of the
+fluid-structure coupling. Due to the difficulty in studying the FSI phenomena by
+experiments and analytical methods, we resort to numerical study due to its
+flexibility. Mesh-based and meshless methods are used to study the FSI phenomena
+numerically.
+
+Mesh-based schemes such as FEM \cite{lozovskiy2015unconditionally} and FVM
+\cite{jasak2007updated} have been in the market for the last few decades
+and are successful in modeling the FSI phenomena. But, mesh-based procedures are
+not favorable when dealing with free surface flow problems and problems with
+large deformation of solids due to large mesh distortion
+\cite{moresi2003lagrangian}.
+
+% Current research
+% has been carried out to address such issues, and methods like Immersed Boundary
+% Method \cite{mittal2005immersed} and level set method
+% \cite{olsson2005conservative} are proposed to address such issues.
+
+Therefore, meshless methods are used to solve free surface and large deformation
+problems, which is advantageous in these areas. Among many meshless methods, we
+often find Smoothed particle hydrodynamics (SPH) and Material point method (MPM)
+to model the fluid phase, and the solids phase is modeled with DEM, RKPM, or SPH
+itself \cite{hu2010material,li2022material}. These meshless techniques have
+been coupled for the past two decades to model the fluid-structure interaction.
+A few schemes with SPH and MPM are SPH-DEM, SPH-TLSPH, SPH-RKPM, SPH-PD,
+MPM-DEM, MPM-RKPM \cite{khayyer2022systematic}. For more, see the review by
+\cite{khayyer2022systematic}.%  In the current work, we use SPH alone to model
+% fluid and solid phases.
+
+In the SPH methods, fluids are modelled primarily using two different
+approaches, one by assuming it to be weakly compressible and another by
+considering it as incompressible.
+% Though both techniques successfully model fluid dynamics, they have their
+% drawbacks.
+Weakly compressible SPH suffers from particle pairing and irregular particle
+distribution problems affecting the function approximation.
+\cite{xu2009accuracy} proposed a particle shifting technique, where particle
+positions are adjusted after each timestep to distribute the particles
+homogeneously. The particle properties are adjusted at the new position using
+Taylor series approximation. Later, \cite{adami2013transport} proposed a
+complete scheme where the particle transport is incorporated in Navier-Stokes
+equations, and a new set of equations is solved and applied to internal fluid
+flow problems. \cite{zhang_hu_adams17} extended the TVF formulation to GTVF
+and solved free surface problems. \cite{adepu2021corrected}proposed a
+corrected TVF scheme (CTVF) where the missing terms in TVF are incorporated to
+solve the free surface flow problems.
+
+If we consider papers where SPH alone is used to model the FSI phenomena, we
+have WCSPH-Total Lagrangian SPH (TLSPH) \cite{zhan2019stabilized},
+WCSPH-Updated Lagrangian SPH (ULSPH) \cite{antoci2007numerical},
+ISPH-TLSPH\cite{salehizadeh2022coupled}. Where the coupling is handled
+using \cite{Adami2013} conditions and adapted accordingly.
+% So, in all these
+% schemes we have fluid being modeled in updated frame and solid being simulated
+% in a reference frame.
+Modeling the FSI using a transport velocity formulation is at a great advantage
+as it can solve the tensile instability issue in solid dynamics and inharmonious
+particle distribution in fluids. We model both fluid and solid phase in CTVF and
+couple them in the current work.
+
+\section{Fluid }
 

### 2022-12-08 automate.py

@@ -457,11 +457,14 @@ class Ng2020HydrostaticWaterColumnOnElasticPlate(Problem):
         rand_case = (list(data.keys())[0])
         t_analytical = data[rand_case]['t_analytical']
         y_analytical = data[rand_case]['y_analytical']
+        t_ng_2020 = data[rand_case]['t_ng_2020']
+        y_ng_2020 = data[rand_case]['y_ng_2020']
 
         # ==================================
         # Plot x amplitude
         # ==================================
         plt.plot(t_analytical, y_analytical, "-", label='Analytical')
+        plt.plot(t_ng_2020, y_ng_2020, "-", label='SPH-VCPM (Ng et al. 2020)')
         for name in self.case_info:
             t_ctvf = data[name]['t_ctvf']
             y_ctvf = data[name]['y_ctvf']
@@ -760,20 +763,20 @@ class Sun2019DamBreakingFlowImpactingAnElasticPlate(Problem):
 
         # Base case info
         self.case_info = {
-            'd0_1e_3': (dict(
-                scheme='wcsph_fluids',
-                pfreq=300,
-                tf=0.7,
-                d0=1e-3,
-                ), 'd0 1e-3'),
+            # 'd0_1e_3': (dict(
+            #     scheme='wcsph_fluids',
+            #     pfreq=300,
+            #     tf=0.7,
+            #     d0=1e-3,
+            #     ), 'd0 1e-3'),
 
-            'd0_1e_3_ipst': (dict(
-                scheme='wcsph_fluids',
-                solid_pst="ipst",
-                pfreq=300,
-                tf=0.7,
-                d0=1e-3,
-                ), 'd0 1e-3 IPST'),
+            # 'd0_1e_3_ipst': (dict(
+            #     scheme='wcsph_fluids',
+            #     solid_pst="ipst",
+            #     pfreq=300,
+            #     tf=0.7,
+            #     d0=1e-3,
+            #     ), 'd0 1e-3 IPST'),
 
             'd0_5e_4': (dict(
                 scheme='wcsph_fluids',
@@ -845,16 +848,17 @@ class Sun2019DamBreakingFlowImpactingAnElasticPlate(Problem):
         # Plot x amplitude
         # ==================================
         plt.clf()
[…]

### 2022-12-08 code/ng_2020_hydrostatic_water_column_on_elastic_plate.py

@@ -444,16 +444,30 @@ class ElasticGate(Application):
             t_ctvf.append(_t)
             y_ctvf.append((gate.y[index] - y_0) * 1)
 
-        t_analytical = np.linspace(0., 1., 1000)
+        t_analytical = np.linspace(0., max(t_ctvf), 1000)
         y_analytical = -6.849 * 1e-5 * np.ones_like(t_analytical)
 
+        # Numerical data
+        path = os.path.abspath(__file__)
+        directory = os.path.dirname(path)
+
+        # load the data
+        data_y_disp_ng_2020 = np.loadtxt(
+            os.path.join(directory, 'ng_2020_hydrostatic_water_column_on_elastic_plate_y_displacement_ng_2020_sph_vcpm.csv'),
+            delimiter=',')
+
+        t_ng_2020, y_ng_2020 = data_y_disp_ng_2020[:, 0] * 1e-4, data_y_disp_ng_2020[:, 1] * 1e-4
+        t_ng_2020 = np.concatenate([t_ng_2020, np.array([max(t_ctvf)])])
+        y_ng_2020 = np.concatenate([y_ng_2020, np.array([y_ng_2020[-1]])])
         res = os.path.join(self.output_dir, "results.npz")
         np.savez(res, t_analytical=t_analytical, y_analytical=y_analytical,
-                 y_ctvf=y_ctvf, t_ctvf=t_ctvf)
+                 y_ctvf=y_ctvf, t_ctvf=t_ctvf,
+                 t_ng_2020=t_ng_2020, y_ng_2020=y_ng_2020)
 
         plt.clf()
         plt.plot(t_analytical, y_analytical, label='Analytical')
         plt.plot(t_ctvf, y_ctvf, "-", label='Simulated')
+        plt.plot(t_ng_2020, y_ng_2020, "-", label='SPH-VCPM')
 
         plt.xlabel('t')
         plt.ylabel('y-amplitude')
